### 2018-05-18 ms.tex
Update on Overleaf.

\documentclass[modern]{aastex62}
\usepackage{amsmath}
\graphicspath{{./}{figures/}}

% typography
\setlength{\parindent}{1.\baselineskip}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\package}[1]{\textsl{#1}}
\newcommand{\gaia}{\textsl{Gaia}}
\newcommand{\pans}{\textsl{Pan-STARRS}}
\newcommand{\DR}[1]{\acronym{DR#1}}
\newcommand{\todo}[1]{{\color{red} TODO: #1}}

% astronomy stuffs
\newcommand{\msun}{\textrm{M}_\odot}
\newcommand{\kpc}{\textrm{kpc}}
\newcommand{\kms}{\ensuremath{\textrm{km}~\textrm{s}^{-1}}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\masyr}{\ensuremath{\textrm{mas}~\textrm{yr}^{-1}}}
\newcommand{\feh}{\ensuremath{[\textrm{Fe} / \textrm{H}]}}
%\newcommand{\kms}{\mbox{km s$^{-1}~$}} 
\newcommand{\kmse}{\mbox{km s$^{-1}$}} 
\newcommand{\vlsr}{$V_{\rm LSR}~$}
\newcommand{\vlsre}{$V_{\rm LSR}$}
\newcommand{\hi}{H{\footnotesize I} }
\newcommand{\hie}{H{\footnotesize I}}
\newcommand{\lms}{$L_{\rm MS}~$}
\newcommand{\lmse}{$L_{\rm MS}$}
\newcommand{\bms}{$B_{\rm MS}~$}
\newcommand{\bmse}{$B_{\rm MS}$}

\newcommand{\clustername}{\textsl{NAME}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
% \received{January 1, 2018}
% \revised{January 7, 2018}
% \accepted{\today}

\submitjournal{ApJ}
\shorttitle{Sample article}
\shortauthors{People et al.}

\begin{document}

\title{A young cluster in the Galactic halo: \\
Recent star formation associated with the Magellanic stream}

\author{Author McAuthorface}
\affil{Some affiliation}

\author[0000-0003-0872-7098]{Adrian~M.~Price-Whelan}
\affiliation{Department of Astrophysical Sciences,
             Princeton University, Princeton, NJ 08544, USA}
\email{adrn@astro.princeton.edu}
\correspondingauthor{Adrian M. Price-Whelan}

\author[0000-0002-1793-3689]{David L. Nidever}
\affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717-3840, USA}
\affiliation{National Optical Astronomy Observatory, 950 North Cherry Ave, Tucson, AZ 85719}

\author[0000-0003-1680-1884]{Yumi Choi}
\affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717-3840, USA}
\affiliation{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson AZ, 85721}

\begin{abstract}

We report the discovery of a young ($\lesssim 100~\textrm{Myr}$), metal-poor ($[\textrm{Fe}/\textrm{H}] \sim -1$) star cluster in the halo of the Milky Way. 
The cluster --- \clustername\ --- is likely associated with the leading arm of the gas stream emanating from the Magellanic cloud system and is located $\approx 60^\circ$ from the LMC center, on the other side of the Milky Way disk relative to the LMC.
By assuming the cluster is co-located with HI gas in the stream, we, for the first time, directly measure the distance to the Magellanic stream, $d \approx 25~\textrm{kpc}$. 
At this location relative to the LMC, this distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way.
The estimated age of \clustername\ is consistent with the time of last passage through the Galactic midplane. 
We therefore conclude that this star-formation event was triggered by the last disk passage, which occurred at a Galactocentric radius $R \approx XX~\kpc$.

\end{abstract}

\keywords{Galaxy: halo}

\section{Introduction} \label{sec:intro}

The stellar halo of the Milky Way is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the Milky Way's formation: massive dwarf galaxies (cite deason, etc.).
The 
(Built up from destroyed satellites that lost their gas on infall)

However, the Milky Way continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy that can be traced $>360^\circ$ in angle, and the presence of the Magellanic cloud system.
While Sagittarius was likely stripped of its neutral gas long ago (cite), the LMC/SMC system contains $\approx XX~\msun$ of HI gas (cite), which form leading and trailing gas streams that cover $\approx 200^\circ$ on the sky.
(Gas is great, can run models to try to reproduce. But lacks distance information)
(Many people search for stars associated with the stream, but must be diffuse)

\section{Data and cluster discovery} \label{sec:data}

We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) cross-matched to the \pans\ data release 1 photometry ($griz$ magnitudes; \citealt{Chambers:2016}) to search for distant, comoving multiplets of blue stars.\footnote{We use the cross-match provided by the \gaia\ science archive at \url{https://gea.esac.esa.int/archive/}.}
In detail, we initially query all stars from the \gaia--\pans\ cross-match that have $(g - i) < 1$, parallax $\varpi < 1~{\rm mas}$, and Galactic latitude $|b| > 10^\circ$.

Figure \ref{fig_skypm} shows the spatial and proper motion distribution in the region of interest with the objects in
a small proper motion selection shown as black and red dots.  The color magnitude diagram (CMD) of the same objects
is shown in Figure \ref{fig_cmd} and clearly reveals a sequence of objects that follow the shape of a young main-sequence.
The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at
a distance of 25 kpc.  Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever2008}.
The component of the LA II can be seen on the left-hand side of the figure and a similar \hie stream can be seen near the
position of the cluster.

\section{Results} \label{sec:results}

We have used the new Gaia data to detect a young, metal-poor cluster in the halo of the Milky Way at a distance of 25 kpc and
a Milky Way z-height of 12 kpc.  The detection of such a young cluster so far from the star-forming disks of any nearby
galaxy is highly unusual.  However, the proximity of the new cluster to the Leading Arm of the Magellanic Stream suggests
that the cluster originated from this metal-poor gas \citep{Fox2018}.  Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu2014,MoniBidin2017}, however, this is the first time
that an entire star cluster has been detected so far from the Clouds.

We evaluate the hypothesis that the cluster formed in the Leading Arm.  The mean proper motion values in the Magellanic Stream
coordinate system \citep{Nidever2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the
mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.  The simulations
of \citet{Besla2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.  The Magellanic Stream
simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the
effects of ram pressure from the hot MW halo which could cause the gas to drop in its orbit to smaller Galactocentric
distances (NEED TO DOUBLE-CHECK THIS).  In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the
position of the position of the cluster with a velocity of \vlsr=70 \kmse.

\begin{figure}
\centering
\includegraphics[width=12cm]{sky_pm.png}
\caption{Figure 1}  
\label{fig_skypm}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=8cm]{cmd.png}
\caption{The Gaia DR2 color magnitude diagram of the region showing the pronounced
young stellar main sequence.}
\label{fig_cmd}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=8cm]{isochrone.png}
\caption{PS1 color magnitude diagrams with young, metal-poor (\feh=-1.0) isochrones overplotted at
a distance of 25 kpc.}
\label{fig_isochrone}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=8cm]{gass_vlsrmlon.pdf}
\caption{GASS position-velocity diagram.}
\label{fig_gass}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=8cm]{gass_mlatmlon.pdf}
\caption{GASS \hi column density in the region of LA II. The red cross marks the position
of the young cluster.}
\label{fig_gass}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=8cm]{orbits.png}
\caption{Integrated orbits (over 60 Myr) of the star cluster using the Gaia DR2 proper motions, the
\hi~velocity and a distance of 25 kpc.  The orbits intersect the MW midplane about 
60 Myr ago which is close to the age of the cluster.}
\label{fig_gass}
\end{figure}

\section{Discussion} \label{sec:discussion}

- Streams or clusters in the halo from star-formation from Sgr or dwarf gas

- Sgr young globular clusters: same thing as this? Indication of when Sgr lost its gas?

\section{Conclusion} \label{sec:conclusion}

\acknowledgments

We thank some people...

This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by
the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral Agreement.

\vspace{5mm}
\facilities{TODO}

\software{
    \package{Astropy} \citep{astropy},
    \package{dustmaps}\footnote{\url{https://github.com/gregreen/dustmaps}},
    \package{gala} \citep{gala},
    \package{IPython} \citep{ipython},
    \package{matplotlib} \citep{mpl},
    \package{numpy} \citep{numpy},
    \package{scipy} \citep{scipy}
}

\bibliographystyle{aasjournal}
\bibliography{ms}

\end{document}

### 2018-05-18 ms.tex
Intro outline

@@
 The stellar halo of the Milky Way is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
-This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the Milky Way's formation: massive dwarf galaxies (cite deason, etc.).
-The 
-(Built up from destroyed satellites that lost their gas on infall)
+This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the Milky Way's formation: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
+These systems likely came in with significant gas reservoirs, but were quenched and stripped of their gas, leading to the typically old stellar halo population in place today.
+(Gas stripped now too hot/diffuse to form stars)
 
-However, the Milky Way continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy that can be traced $>360^\circ$ in angle, and the presence of the Magellanic cloud system.
-While Sagittarius was likely stripped of its neutral gas long ago (cite), the LMC/SMC system contains $\approx XX~\msun$ of HI gas (cite), which form leading and trailing gas streams that cover $\approx 200^\circ$ on the sky.
-(Gas is great, can run models to try to reproduce. But lacks distance information)
+However, the Milky Way continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy (cite), and the presence of the Large and Small Magellanic Clouds (LMC, SMC).
+While Sagittarius was likely stripped of its neutral gas long ago (cite), the LMC--SMC system contains $\approx XX~\msun$ of HI gas (cite), which form leading and trailing gas streams that cover $\approx 200^\circ$ on the sky (cite nidever).
+By modeling the LMC--SMC interaction and infall, ... sims to reproduce gas velocity vs. longitude \citep{Besla:2010}
+(But lacks distance constraints)
 (Many people search for stars associated with the stream, but must be diffuse)
+
+(Gas near the LMC/SMC is forming stars \citep{Casetti-Dinescu2014,MoniBidin2017}, and cite Deason/Belokurov bridge paper)
 
@@
 mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.  The simulations
-of \citet{Besla2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.  The Magellanic Stream
+of \citet{Besla:2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.  The Magellanic Stream
 simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the

### 2018-05-18 ms.tex
Add Vasily / Sergey

@@
 
+\author{Sergey E. Koposov}
+\affiliation{McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, 5000 Forbes Avenue, Pittsburgh, PA 15213, USA}
+\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
+
+\author{Vasily Belokurov}
+\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, NY 10010, USA}
+
 \begin{abstract}
@@
 We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) cross-matched to the \pans\ data release 1 photometry ($griz$ magnitudes; \citealt{Chambers:2016}) to search for distant, comoving multiplets of blue stars.\footnote{We use the cross-match provided by the \gaia\ science archive at \url{https://gea.esac.esa.int/archive/}.}
-In detail, we initially query all stars from the \gaia--\pans\ cross-match that have $(g - i) < 1$, parallax $\varpi < 1~{\rm mas}$, and Galactic latitude $|b| > 10^\circ$.
+We initially query all stars from the \gaia--\pans\ cross-match that have $(g - i) < 1$, parallax $\varpi < 1~\textrm{mas}$, and Galactic latitude $|b| > 10^\circ$.
 

### 2018-05-21 ms.tex
Title
Update on Overleaf.

@@
 
-\title{A young cluster in the Galactic halo: \\
-Recent star formation associated with the Magellanic stream}
+\title{A young star cluster in the Galactic halo: \\
+Recent star formation associated with the Leading Arm of the Magellanic stream}
 
@@
 
-The stellar halo of the Milky Way is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
-This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the Milky Way's formation: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
+The stellar halo of the Milky Way (MW) is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
+This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the MW's formation: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
 These systems likely came in with significant gas reservoirs, but were quenched and stripped of their gas, leading to the typically old stellar halo population in place today.
@@
 
-However, the Milky Way continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy (cite), and the presence of the Large and Small Magellanic Clouds (LMC, SMC).
+However, the MW continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy (cite), and the presence of the Large and Small Magellanic Clouds (LMC, SMC).
 While Sagittarius was likely stripped of its neutral gas long ago (cite), the LMC--SMC system contains $\approx XX~\msun$ of HI gas (cite), which form leading and trailing gas streams that cover $\approx 200^\circ$ on the sky (cite nidever).
@@
 is shown in Figure \ref{fig_cmd} and clearly reveals a sequence of objects that follow the shape of a young main-sequence.
-The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at
-a distance of 25 kpc.
+The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at fa distance of 25 kpc.
 Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever2008}.
@@
 position of the cluster.
+% Yumi:
+% Need a sentence or two for dust extinction correction somewhere in the above two paragraphs?
 
@@
 
-We have used the new Gaia data to detect a young, metal-poor cluster in the halo of the Milky Way at a distance of 25 kpc and
-a Milky Way z-height of 12 kpc.  The detection of such a young cluster so far from the star-forming disks of any nearby
+We have used the new Gaia data to detect a young, metal-poor cluster in the halo of the Milky Way at a distance of 25 kpc and a MW z-height of 12 kpc.
+The detection of such a young cluster so far from the star-forming disks of any nearby
 galaxy is highly unusual.  However, the proximity of the new cluster to the Leading Arm of the Magellanic Stream suggests
 that the cluster originated from this metal-poor gas \citep{Fox2018}.
-Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu2014,MoniBidin2017}, however, this is the first time
-that an entire star cluster has been detected so far from the Clouds.
+Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu2014,MoniBidin2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
 
-We evaluate the hypothesis that the cluster formed in the Leading Arm.  The mean proper motion values in the Magellanic Stream
-coordinate system \citep{Nidever2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the
-mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.  The simulations
-of \citet{Besla:2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.  The Magellanic Stream
-simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the
-effects of ram pressure from the hot MW halo which could cause the gas to drop in its orbit to smaller Galactocentric
-distances (NEED TO DOUBLE-CHECK THIS).  In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the
-position of the position of the cluster with a velocity of \vlsr=70 \kmse.
+We evaluate the hypothesis that the cluster formed in the Leading Arm.
+The mean proper motion values in the Magellanic Stream coordinate system \citep{Nidever2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.
+The simulations of \citet{Besla:2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.
+The Magellanic Stream simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the effects of ram pressure from the hot MW halo which could cause the gas to drop in its orbit to smaller Galactocentric distances (NEED TO DOUBLE-CHECK THIS).
+In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the position of the position of the cluster with a velocity of \vlsr=70 \kmse.
 

### 2018-07-17 ms.tex
Update on Overleaf.
Intro

@@
 \newcommand{\clustername}{\textsl{NAME}}
+\newcommand{\lmcsmc}{LMC--SMC}
 
@@
 
-\title{A young star cluster in the Galactic halo: \\
-Recent star formation associated with the Leading Arm of the Magellanic stream}
+% \title{A young star cluster in the Galactic halo: \\
+% Recent star formation associated with the Leading Arm of the Magellanic stream}
+\title{Star formation in the leading arm of the Magellanic stream triggered by passage through the Galactic midplane}
 
@@
 
+\author{Edward Schlafly}
+
+\author{Douglas Finkbeiner}
+% \affiliation{McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, 5000 Forbes Avenue, Pittsburgh, PA 15213, USA}
+% \affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
+
 \author{Sergey E. Koposov}
@@
 
-We report the discovery of a young ($\lesssim 100~\textrm{Myr}$), metal-poor ($[\textrm{Fe}/\textrm{H}] \sim -1$) star cluster in the halo of the Milky Way.
-The cluster --- \clustername\ --- is likely associated with the leading arm of the gas stream emanating from the Magellanic cloud system and is located $\approx 60^\circ$ from the LMC center, on the other side of the Milky Way disk relative to the LMC.
-By assuming the cluster is co-located with HI gas in the stream, we, for the first time, directly measure the distance to the Magellanic stream, $d \approx 25~\textrm{kpc}$.
-At this location relative to the LMC, this distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way.
+We report the discovery of a young ($\lesssim 100~\textrm{Myr}$), metal-poor ($[\textrm{Fe}/\textrm{H}] \sim -1$) stellar association in the halo of the Milky Way ($(R, z) \sim (24, 16) kpc$).
+The association --- \clustername\ --- is likely associated with the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
+By assuming that the cluster is co-located with HI gas in the stream, we directly measure the distance to the Magellanic stream, $d \approx 25~\textrm{kpc}$.
+At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way.
+\todo{that don't account for ram pressure and gas interaction with MW disk}
 The estimated age of \clustername\ is consistent with the time of last passage through the Galactic midplane.
@@
 
-The stellar halo of the Milky Way (MW) is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
-This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the MW's formation: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
-These systems likely came in with significant gas reservoirs, but were quenched and stripped of their gas, leading to the typically old stellar halo population in place today.
-(Gas stripped now too hot/diffuse to form stars)
+The stellar halo of the Milky Way is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
+This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the formation of the Galaxy: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
+These systems likely came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
 
-However, the MW continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy (cite), and the presence of the Large and Small Magellanic Clouds (LMC, SMC).
-While Sagittarius was likely stripped of its neutral gas long ago (cite), the LMC--SMC system contains $\approx XX~\msun$ of HI gas (cite), which form leading and trailing gas streams that cover $\approx 200^\circ$ on the sky (cite nidever).
-By modeling the LMC--SMC interaction and infall, ... sims to reproduce gas velocity vs. longitude \citep{Besla:2010}
+The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, and the presence of the Large and Small Magellanic Clouds (LMC, SMC) within the virial radius of the Galaxy.
+While Sagittarius was likely stripped of its neutral gas long ago \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system contains $\approx 5\times 10^8~\msun$ of HI gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Putman:1998, Bruns:2005, Nidever:2010}.
+Streams formed from tidally stripped material --- such as the Sagittarius or Palomar 5 \citep{Odenkirchen:2001} stellar streams, or gas streams such as the Magellanic stream (MS) --- encode information about the orbital history and future trajectory of their progenitor system \citep[e.g.,][]{Johnston:1999}.
+For this reason, streams of debris are of interest for constraining the dark matter distribution around the Galaxy, as well as for providing a fossil record of the Milky Way's accretion history \citep{Johnston:1998, Bullock:2005}.
+
+(Summarize magellanic stream stuffs)
+
+Several groups have attempted to use the MS to constrain both the infall history of the \lmcsmc\ and the dark matter halo of the Milky Way (see recent review by \citealt{DOnghia:2016}).
+Early models for the formation of the MS invoke ram pressure and tidal stripping to explain the sky distribution and extent of the MS, and typically require that the \lmcsmc\ system complete several orbits around the Galaxy in order to strip enough material \citep[e.g.,][]{Murai:1980, Gardiner:1994, Mastropietro:2005}.
+However, later measurements of the proper motion of the LMC (\citealt{Kallivayalil:2006}, later confirmed by \gaia\ \citealt{van-der-Marel:2016}) and improved models for the infall dynamics \citep{Besla:2007} suggest that the \lmcsmc\ system could be on its first passage through the Galaxy \citep{Besla:2010, Besla:2012}.
+In addition, the orbit of the LMC implied by the new proper motion measurement appears to be offset by $\approx 10^\circ$ from the MS \citep{Besla:2010}.
+Put together, these recent revelations have led to new models for the formation of the MS that largely rely on past interactions between the LMC and SMC to preprocess the gas distribution before infall and eventual stripping by the tidal field of the Milky Way \citep{Besla:2012, Diaz:2012}
+
+(More recently, proper motions (confirmed by Gaia) show that orbit of LMC differs from path of MS)
+(Difficulty reproducing offset by invoking tidal stripping + ram pressure, interaction history important)
+(But, questions remain because leading stream)
+
+One critical difficulty in using the MS to constrain models of the \lmcsmc\ interaction and infall is the lack of distance information along the stream.
+No significant over-density of stars have been found associated with the trailing portion of the MS \citep{Guhathakurta:1998}, thus leaving distance and tangential velocity information largely unknown.
+The leading arm, however, ...
+A small number of young OB stars have been found in the vicinity of the leading arm gas, with radial velocities consistent with having formed from the leading MS \citep{Casetti-Dinescu:2014, Zhang:2017}.
+However, given their sparsity and concentration near the Galactic plane, it is difficult to unambiguously associate them with the MS: these could instead be runaway OB stars from the Milky Way disk.
+
+Recent work has found
+
+(Young OB stars tentatively associated with leading (Casetti-D))
+
+However, the connection between the Magellanic clouds and the Magellanic Stream (MS)
+
+For example, by modeling the \todo{XX} \citep{Besla:2010}, it is now understood that the \lmcsmc\ is likely on its first approach through the Galaxy, which has major implications for understanding the properties of the system itself and its effect on Galactic structure such as the bar, spiral arms, and outer disk \citep[e.g.,][]{Gomez:xxxx, Laporte:20xx}.
+
 (But lacks distance constraints)
@@
 
-(Gas near the LMC/SMC is forming stars \citep{Casetti-Dinescu2014,MoniBidin2017}, and cite Deason/Belokurov bridge paper)
+Gas associated with the LMC--SMC system has continued to form stars:
+
+(Gas near the LMC/SMC is forming stars \citep{Casetti-Dinescu:2014, MoniBidin:2017}, and cite Deason/Belokurov bridge paper)
+
+For the Magellanic Clouds, observations of tidally stripped gas or stars should help constrain the LMC--SMC interaction history and infall, and will help inform the expected response of the Milky Way to this massive accretion event \citep[e.g.,][]{Gomez:xxxx, Laporte:20xx}.
+
+Leading arm features - ??? Disrupted satellites of the LMC?? Fox 2015 paper
 
@@
 The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at fa distance of 25 kpc.
-Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever2008}.
+Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths:2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever:2008}.
 The component of the LA II can be seen on the left-hand side of the figure and a similar \hie stream can be seen near the
@@
 % Need a sentence or two for dust extinction correction somewhere in the above two paragraphs?
+
+Isochrone: \citep{Fox:2018}
 
@@
 galaxy is highly unusual.  However, the proximity of the new cluster to the Leading Arm of the Magellanic Stream suggests
-that the cluster originated from this metal-poor gas \citep{Fox2018}.
-Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu2014,MoniBidin2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
+that the cluster originated from this metal-poor gas \citep{Fox:2018}.
+Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, MoniBidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
 
 We evaluate the hypothesis that the cluster formed in the Leading Arm.
-The mean proper motion values in the Magellanic Stream coordinate system \citep{Nidever2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.
+The mean proper motion values in the Magellanic Stream coordinate system \citep{Nidever:2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.
 The simulations of \citet{Besla:2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.

### 2018-07-18 ms.tex
Introduction complete draft

@@
 \newcommand{\todo}[1]{{\color{red} TODO: #1}}
+
+\newcommand{\articlename}{\textsl{Letter}}
+\newcommand{\sectionname}{Section}
 
@@
 
-\submitjournal{ApJ}
-\shorttitle{Sample article}
-\shortauthors{People et al.}
+\submitjournal{ApJL}
+\shorttitle{A recent star formation event in the Magellanic stream}
+\shortauthors{Price-Whelan et al.}
 
@@
 % Recent star formation associated with the Leading Arm of the Magellanic stream}
-\title{Star formation in the leading arm of the Magellanic stream triggered by passage through the Galactic midplane}
-
-\author{Author McAuthorface}
-\affil{Some affiliation}
+\title{A star formation event in the leading arm of the Magellanic stream triggered by passage through the outer Galactic disk}
 
@@
 
-The stellar halo of the Milky Way is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
+The halo of the Milky Way is characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
 This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the formation of the Galaxy: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
 These systems likely came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
+The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, and the presence of the Large and Small Magellanic Clouds (LMC, SMC) within the virial radius of the Galaxy.
+While Sagittarius was likely stripped of its neutral gas long ago \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of HI gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Putman:1998, Bruns:2005, Nidever:2010}.
 
-The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, and the presence of the Large and Small Magellanic Clouds (LMC, SMC) within the virial radius of the Galaxy.
-While Sagittarius was likely stripped of its neutral gas long ago \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system contains $\approx 5\times 10^8~\msun$ of HI gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Putman:1998, Bruns:2005, Nidever:2010}.
-Streams formed from tidally stripped material --- such as the Sagittarius or Palomar 5 \citep{Odenkirchen:2001} stellar streams, or gas streams such as the Magellanic stream (MS) --- encode information about the orbital history and future trajectory of their progenitor system \citep[e.g.,][]{Johnston:1999}.
+The Magellanic stream (MS) is a large stream of (predominantly) hydrogen gas emanating from the \lmcsmc\ system that contains a significant fraction of the total gas mass associated with the \lmcsmc\ \citep{Bruns:2005}.
+The stream was discovered in early surveys of 21 cm emission and has since been studied in great detail by large-area radio sky surveys, and in H$\alpha$ emission \citep{Weiner:1996, Barger:2017}.
+With increased resolution, surveys have found small-scale structure and gas fragmentation \citep[e.g.,][]{Nidever:2008, For:2014} and a large-scale bifurcation, with semi-distinct ``strands'' that lead back to the LMC and broader system, respectively \citep[e.g.,][]{Morras:1983, Putman:2003}.
+As surveys push deeper to lower column densities, extensions of the stream have been found both in the trailing region \citep{Nidever:2010}, but also in the leading arm, which has been found to connect to regions of low-column-density gas ($N\sim 10^{18}$--$10^{19}~\textrm{cm}^{-2}$) on the other side of the Galactic disk \citep{Putman:1998, Nidever:2008}.
+The leading arm (LA) has been decomposed into three or four distinct ``features'' named LA1--4 \citep{Bruns:2005, Nidever:2008, Venzmer:2012} with total HI mass $\sim 4 \times10^7~\msun$ \citep{Venzmer:2012}.
+
+The origin and formation of the LA features in the MS is still uncertain.
+Initial studies of the LA argue that the features closest to the \lmcsmc\ can be traced back to the SMC, thus implying that the gas in the LA was stripped from the SMC \citep{Putman:1998}.
+In more recent work, it has instead been argued that outer features of the LMC appear to lead directly into the LA-1 feature \citep{Nidever:2008}, implying an LMC origin for the leading arm.
+Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the leading arm \citep{Nidever:2008}.
+However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions with gas in the outer Milky Way disk may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.
+
+Streams formed from tidally stripped material --- such as the Sagittarius or Palomar 5 \citep{Odenkirchen:2001} stellar streams, or gas streams such as the MS --- encode information about the orbital history and future trajectory of their progenitor system \citep[e.g.,][]{Johnston:1999}.
 For this reason, streams of debris are of interest for constraining the dark matter distribution around the Galaxy, as well as for providing a fossil record of the Milky Way's accretion history \citep{Johnston:1998, Bullock:2005}.
-
-(Summarize magellanic stream stuffs)
-
 Several groups have attempted to use the MS to constrain both the infall history of the \lmcsmc\ and the dark matter halo of the Milky Way (see recent review by \citealt{DOnghia:2016}).
 Early models for the formation of the MS invoke ram pressure and tidal stripping to explain the sky distribution and extent of the MS, and typically require that the \lmcsmc\ system complete several orbits around the Galaxy in order to strip enough material \citep[e.g.,][]{Murai:1980, Gardiner:1994, Mastropietro:2005}.
-However, later measurements of the proper motion of the LMC (\citealt{Kallivayalil:2006}, later confirmed by \gaia\ \citealt{van-der-Marel:2016}) and improved models for the infall dynamics \citep{Besla:2007} suggest that the \lmcsmc\ system could be on its first passage through the Galaxy \citep{Besla:2010, Besla:2012}.
-In addition, the orbit of the LMC implied by the new proper motion measurement appears to be offset by $\approx 10^\circ$ from the MS \citep{Besla:2010}.
-Put together, these recent revelations have led to new models for the formation of the MS that largely rely on past interactions between the LMC and SMC to preprocess the gas distribution before infall and eventual stripping by the tidal field of the Milky Way \citep{Besla:2012, Diaz:2012}
-
-(More recently, proper motions (confirmed by Gaia) show that orbit of LMC differs from path of MS)
-(Difficulty reproducing offset by invoking tidal stripping + ram pressure, interaction history important)
-(But, questions remain because leading stream)
+However, later measurements of the proper motion of the LMC (\citealt{Kallivayalil:2006}, later confirmed by \gaia\ \citealt{van-der-Marel:2016}) and improved models for the infall dynamics \citep{Besla:2007} suggest instead that the \lmcsmc\ system could be on its first passage through the Galaxy \citep{Besla:2010, Besla:2012}.
+In addition, the orbit of the LMC implied by the new proper motion measurement appears to be offset by $\approx 10^\circ$ from the trailing MS \citep{Besla:2010}.
+Put together, these recent revelations have led to new models for the formation of the MS that largely rely on past interactions between the LMC and SMC to preprocess the gas distribution before infall and eventual stripping by the tidal field of the Milky Way \citep{Besla:2012, Diaz:2012}.
 
@@
 No significant over-density of stars have been found associated with the trailing portion of the MS \citep{Guhathakurta:1998}, thus leaving distance and tangential velocity information largely unknown.
-The leading arm, however, ...
-A small number of young OB stars have been found in the vicinity of the leading arm gas, with radial velocities consistent with having formed from the leading MS \citep{Casetti-Dinescu:2014, Zhang:2017}.
+Recently, a small number of young OB stars have been found in the vicinity of the leading arm gas, with radial velocities consistent with having formed from the leading MS \citep{Casetti-Dinescu:2014, Zhang:2017}.
 However, given their sparsity and concentration near the Galactic plane, it is difficult to unambiguously associate them with the MS: these could instead be runaway OB stars from the Milky Way disk.
 
-Recent work has found
+In this \articlename, we report the discovery of a clustered association of young stars at the far edge of the LA-2 feature ($L_{\textrm{MS}} \sim 65^\circ$) that is unambiguously located far into the Galactic halo ($d_\odot \sim 30~\textrm{kpc}$) and therefore likely formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
+This provides a clear distance measurement to the leading arm of the MS to be compared with models of \lmcsmc\ interaction and infall into the Milky Way.
 
-(Young OB stars tentatively associated with leading (Casetti-D))
-
-However, the connection between the Magellanic clouds and the Magellanic Stream (MS)
-
-For example, by modeling the \todo{XX} \citep{Besla:2010}, it is now understood that the \lmcsmc\ is likely on its first approach through the Galaxy, which has major implications for understanding the properties of the system itself and its effect on Galactic structure such as the bar, spiral arms, and outer disk \citep[e.g.,][]{Gomez:xxxx, Laporte:20xx}.
-
-(But lacks distance constraints)
-(Many people search for stars associated with the stream, but must be diffuse)
-
-Gas associated with the LMC--SMC system has continued to form stars:
-
-(Gas near the LMC/SMC is forming stars \citep{Casetti-Dinescu:2014, MoniBidin:2017}, and cite Deason/Belokurov bridge paper)
-
-For the Magellanic Clouds, observations of tidally stripped gas or stars should help constrain the LMC--SMC interaction history and infall, and will help inform the expected response of the Milky Way to this massive accretion event \citep[e.g.,][]{Gomez:xxxx, Laporte:20xx}.
-
-Leading arm features - ??? Disrupted satellites of the LMC?? Fox 2015 paper
+In \sectionname~\ref{sec:data}, we present the initial discovery with \gaia\ \DR{2} and follow-up observations with DECam to obtain deeper photometry of the region around the association.
+In \sectionname~\ref{sec:results}, we derive estimates for the total stellar mass of, age of, and distance to the association, and present a plausible formation scenario.
+In \sectionname~\ref{sec:discussion}, we discuss implications for future searches for stars associated with the MS, and discrepancies with existing models of the LA.
+We conclude in \sectionname~\ref{sec:conclusion}.
 
@@
 
+- TODO: where would interaction point between LMC gas and MW disk gas be today? ~150–200 Myr ago is almost 1 complete disk rotation. see Bekki:2008
+
 \section{Conclusion} \label{sec:conclusion}

### 2018-07-18 ms.tex
edits

@@
 
-We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) cross-matched to the \pans\ data release 1 photometry ($griz$ magnitudes; \citealt{Chambers:2016}) to search for distant, comoving multiplets of blue stars.\footnote{We use the cross-match provided by the \gaia\ science archive at \url{https://gea.esac.esa.int/archive/}.}
-We initially query all stars from the \gaia--\pans\ cross-match that have $(g - i) < 1$, parallax $\varpi < 1~\textrm{mas}$, and Galactic latitude $|b| > 10^\circ$.
+We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) to search for distant, comoving multiplets of blue stars.
+We initially select all stars from \gaia\ with $\textrm{parallax} < 1$, $-0.5 < \bprp < 0$, $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see \sectionname~\ref{sec:queries} for database query).
+We further exclude stars within a $15^\circ$ radius from the LMC, and a $8^\circ$ radius from the SMC --- this leaves just 27,895 stars.
+We then cross-match this catalog to itself with both sky positions and proper motions: we search for pairs of stars that have separations $s < 0.5^\circ$ and proper motion differences $|\Delta \mu| < 0.5~\masyr$.
+We then combine mutually-connected comoving pairs into small groups of stars that are colocated on the sky and comoving in proper motions; We filter out groups that have $<4$ members.
+We cross-match the mean sky positions of the groups to locations of local group galaxies \todo{citation} \citep{Mcconaghie} and Milky Way globular clusters \todo{citation} \citep{Harris} and filter out all groups that lie within 1 degree of these known objects.
+After these filters, just one group of blue, comoving stars remains at $(\textrm{RA}, \textrm{Dec}) \sim (179, -29)^\circ$.
+
+We then query all objects from the \gaia\ \DR{2} catalog within a polygon centered on the nominal position of the group (see above), with a width of $12^\circ$ and a height of $8^\circ$ in the Magellanic stream coordinate system \citep{Nidever:2008} (see \sectionname~\ref{sec:queries} for the database query).
+We cross-match the resulting catalog with \acronym{GALEX} \todo{citation} using a positional crossmatch requiring source separation $<2~\textrm{arcsec}$, and with \acronym{PS1} \todo{citation}\citep{Chambers:XX} using the cross-match provided by the \gaia\ science archive.
+
+\todo{Left off here}
 
@@
 
-\vspace{5mm}
-\facilities{TODO}
+\appendix
+
+\section{Queries}
+\label{sec:queries}
+
+Initial query to select very blue stars away from the Galactic plane:
+\begin{verbatim}
+SELECT * FROM gaiadr2.gaia_source
+WHERE parallax < 1
+AND (bp_rp > -0.5) AND (bp_rp < 0)
+AND phot_g_mean_mag < 20
+AND ABS(b) > 20
+\end{verbatim}
+
+Query to retrieve \gaia\ data around the blue, comoving group found and discussed in \sectionname~\ref{sec:data}:
+\begin{verbatim}
+SELECT *
+FROM gaiadr2.gaia_source
+WHERE (parallax < 0.5 OR parallax IS NULL) AND
+    CONTAINS(POINT('ICRS', ra, dec),
+             POLYGON('ICRS',
+                     182.1954909980203, -35.51467868323814,
+                     172.7240896740689, -33.70157733692543,
+                     176.3745742549848, -22.277118488646703,
+                     184.81885184435987, -24.236022801996057)) = 1 AND
+    (pmra > -10) AND (pmra < 10) AND
+    (pmdec > -10) AND (pmdec < 10)
+\end{verbatim}
 

### 2018-07-18 ms.tex
Appendix

@@
 We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) to search for distant, comoving multiplets of blue stars.
-We initially select all stars from \gaia\ with $\textrm{parallax} < 1$, $-0.5 < \bprp < 0$, $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see \sectionname~\ref{sec:queries} for database query).
+We initially select all stars from \gaia\ with $\textrm{parallax} < 1$, $-0.5 < \bprp < 0$, $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see Appendix~\ref{sec:queries} for database query).
 We further exclude stars within a $15^\circ$ radius from the LMC, and a $8^\circ$ radius from the SMC --- this leaves just 27,895 stars.
@@
 
-We then query all objects from the \gaia\ \DR{2} catalog within a polygon centered on the nominal position of the group (see above), with a width of $12^\circ$ and a height of $8^\circ$ in the Magellanic stream coordinate system \citep{Nidever:2008} (see \sectionname~\ref{sec:queries} for the database query).
+We then query all objects from the \gaia\ \DR{2} catalog within a polygon centered on the nominal position of the group (see above), with a width of $12^\circ$ and a height of $8^\circ$ in the Magellanic stream coordinate system \citep{Nidever:2008} (see Appendix~\ref{sec:queries} for the database query).
 We cross-match the resulting catalog with \acronym{GALEX} \todo{citation} using a positional crossmatch requiring source separation $<2~\textrm{arcsec}$, and with \acronym{PS1} \todo{citation}\citep{Chambers:XX} using the cross-match provided by the \gaia\ science archive.

### 2018-07-20 ms.tex
dust map
figure 1

@@
+% TODO
+% - Sand, Seth, et al. Virgo: blue stars with nothing else
+% - Mixture model in proper-motion space, Gaia only
+
+% Proposal
+% - IMACS?
+% - Blue stars - bandpasses have bad Teff resolution
+% - Better Teff, logg -> better age
+% - Big FOV, blue throughput, southern, >4m
+
 \documentclass[modern]{aastex62}
@@
 \newcommand{\lmcsmc}{LMC--SMC}
+\newcommand{\bprp}{\ensuremath{\textrm{BP} - \textrm{RP}}}
 
@@
 We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) to search for distant, comoving multiplets of blue stars.
-We initially select all stars from \gaia\ with $\textrm{parallax} < 1$, $-0.5 < \bprp < 0$, $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see Appendix~\ref{sec:queries} for database query).
-We further exclude stars within a $15^\circ$ radius from the LMC, and a $8^\circ$ radius from the SMC --- this leaves just 27,895 stars.
+We initially select all stars from \gaia\ with parallax $\varpi < 1$, color $-0.5 < (\bprp) < 0$, $G$-band magnitude $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see Appendix~\ref{sec:queries} for database query).
+We further exclude stars within a $15^\circ$ radius from the LMC, and a $8^\circ$ radius from the SMC --- 27,895 stars remain after these cuts.
 We then cross-match this catalog to itself with both sky positions and proper motions: we search for pairs of stars that have separations $s < 0.5^\circ$ and proper motion differences $|\Delta \mu| < 0.5~\masyr$.
-We then combine mutually-connected comoving pairs into small groups of stars that are colocated on the sky and comoving in proper motions; We filter out groups that have $<4$ members.
+We then combine mutually-connected comoving pairs into small groups of stars that are colocated on the sky and comoving in proper motions, and remove groups that have $<4$ members.
 We cross-match the mean sky positions of the groups to locations of local group galaxies \todo{citation} \citep{Mcconaghie} and Milky Way globular clusters \todo{citation} \citep{Harris} and filter out all groups that lie within 1 degree of these known objects.
@@
 We cross-match the resulting catalog with \acronym{GALEX} \todo{citation} using a positional crossmatch requiring source separation $<2~\textrm{arcsec}$, and with \acronym{PS1} \todo{citation}\citep{Chambers:XX} using the cross-match provided by the \gaia\ science archive.
+\figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram (left) and the \acronym{GALEX} NUV minus \acronym{PS1} $g$-band vs.
+\gaia\ \bprp\ color-color diagram (right) from the cross-matched photometry.
+All magnitudes are corrected for dust extinction using the SFD \citep{Schlegel:1998} dust map.
+The green polygon in the left panel of \figurename~\ref{fig:cmds} highlights the over-density of blue stars that were identified as comoving from the proper motion search described above.
+The red line in right panel of \figurename~\ref{fig:cmds} is an isochrone (from MIST; \citealt{TODO}) for a $50~\textrm{Myr}$, $\feh = -1$ stellar population.
+
+% Notebook: Figure-CMDs
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/gaia-galex-cmd.pdf}
+\caption{Color-magnitude and color-color diagrams with \gaia\ ($G$, BP, RP), \acronym{GALEX} (NUV), and \acronym{PS1} ($g$) magnitudes.
+Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
+Green polygon in left panel highlights the over-density of blue, comoving stars identified by the search described in \sectionname~\ref{sec:data}.
+Red line in right panel shows the zero-age main sequence of a $50~\textrm{Myr}$, $\feh = -1$ stellar population from the MIST isochrone library \citep{TODO}.
+}
+\label{fig:cmds}
+\end{figure}
 

### 2018-07-21 ms.tex
updates

@@
 \newcommand{\gaia}{\textsl{Gaia}}
-\newcommand{\pans}{\textsl{Pan-STARRS}}
+\newcommand{\pans}{\acronym{PS1}}
+\newcommand{\decam}{DECam}
 \newcommand{\DR}[1]{\acronym{DR#1}}
@@
 
-\section{Data and cluster discovery} \label{sec:data}
+\section{Data} \label{sec:data}
+
+\subsection{Cluster discovery with \gaia}
+\label{sec:discovery}
 
@@
 We then query all objects from the \gaia\ \DR{2} catalog within a polygon centered on the nominal position of the group (see above), with a width of $12^\circ$ and a height of $8^\circ$ in the Magellanic stream coordinate system \citep{Nidever:2008} (see Appendix~\ref{sec:queries} for the database query).
-We cross-match the resulting catalog with \acronym{GALEX} \todo{citation} using a positional crossmatch requiring source separation $<2~\textrm{arcsec}$, and with \acronym{PS1} \todo{citation}\citep{Chambers:XX} using the cross-match provided by the \gaia\ science archive.
-\figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram (left) and the \acronym{GALEX} NUV minus \acronym{PS1} $g$-band vs.
+We cross-match the resulting catalog with \acronym{GALEX} \todo{citation} using a positional crossmatch requiring source separation $<2~\textrm{arcsec}$, and with \pans\ \todo{citation}\citep{Chambers:XX} using the cross-match provided by the \gaia\ science archive.
+\figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram (left) and the \acronym{GALEX} NUV minus \pans\ $g$-band vs.
 \gaia\ \bprp\ color-color diagram (right) from the cross-matched photometry.
@@
 \includegraphics[width=\textwidth]{figures/gaia-galex-cmd.pdf}
-\caption{Color-magnitude and color-color diagrams with \gaia\ ($G$, BP, RP), \acronym{GALEX} (NUV), and \acronym{PS1} ($g$) magnitudes.
+\caption{Color-magnitude and color-color diagrams with \gaia\ ($G$, BP, RP), \acronym{GALEX} (NUV), and \pans\ ($g$) magnitudes.
 Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
-Green polygon in left panel highlights the over-density of blue, comoving stars identified by the search described in \sectionname~\ref{sec:data}.
+Green polygon in left panel highlights the over-density of blue, comoving stars identified by the search described in \sectionname~\ref{sec:discovery}.
 Red line in right panel shows the zero-age main sequence of a $50~\textrm{Myr}$, $\feh = -1$ stellar population from the MIST isochrone library \citep{TODO}.
@@
 
-\todo{Left off here}
+\subsection{Follow-up with \decam}
+\label{sec:decam}
 
-Figure \ref{fig_skypm} shows the spatial and proper motion distribution in the region of interest with the objects in
-a small proper motion selection shown as black and red dots.  The color magnitude diagram (CMD) of the same objects
-is shown in Figure \ref{fig_cmd} and clearly reveals a sequence of objects that follow the shape of a young main-sequence.
-The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at fa distance of 25 kpc.
+\todo{Nidever}
+
+% Figure \ref{fig_skypm} shows the spatial and proper motion distribution in the region of interest with the objects in
+% a small proper motion selection shown as black and red dots.  The color magnitude diagram (CMD) of the same objects
+% is shown in Figure \ref{fig_cmd} and clearly reveals a sequence of objects that follow the shape of a young main-sequence.
+% The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at fa distance of 25 kpc.
 Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths:2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever:2008}.
-The component of the LA II can be seen on the left-hand side of the figure and a similar \hie stream can be seen near the
-position of the cluster.
+% The component of the LA II can be seen on the left-hand side of the figure and a similar \hie stream can be seen near the
+% position of the cluster.
 % Yumi:
@@
 
-Isochrone: \citep{Fox:2018}
+\section{Results} \label{sec:results}
 
-\section{Results} \label{sec:results}
+\section{Proper motion cleaned}
+\label{sec:pmclean}
+
+\todo{APW}
+
+\section{Stellar population characteristics}
+\label{sec:popchars}
+
+\todo{APW}
+
+\section{Relation to HI gas}
+\label{sec:higas}
+
+\todo{Nidever}
 

### 2018-08-01 ms.tex
Proper motion modeling

@@
 \newcommand{\todo}[1]{{\color{red} TODO: #1}}
+\newcommand{\bs}[1]{\boldsymbol{#1}}
 
@@
 
-% astronomy stuffs
+% Stats / probability
+\newcommand{\given}{\,|\,}
+\newcommand{\norm}{\mathcal{N}}
+
+% Maths
+\newcommand{\dd}{\mathrm{d}}
+\newcommand{\transpose}[1]{{#1}^{\mathsf{T}}}
+\newcommand{\inverse}[1]{{#1}^{-1}}
+\newcommand{\argmin}{\operatornamewithlimits{argmin}}
+\newcommand{\mean}[1]{\left< #1 \right>}
+\newcommand{\mat}[1]{\mathbf{#1}}
+
+% Units
 \newcommand{\msun}{\textrm{M}_\odot}
@@
 \newcommand{\kms}{\ensuremath{\textrm{km}~\textrm{s}^{-1}}}
-\newcommand{\bs}[1]{\boldsymbol{#1}}
 \newcommand{\masyr}{\ensuremath{\textrm{mas}~\textrm{yr}^{-1}}}
+
+% Astronomy
 \newcommand{\feh}{\ensuremath{[\textrm{Fe} / \textrm{H}]}}
-%\newcommand{\kms}{\mbox{km s$^{-1}~$}}
-\newcommand{\kmse}{\mbox{km s$^{-1}$}}
 \newcommand{\vlsr}{$V_{\rm LSR}~$}
@@
 
+% Shortcuts for this paper
 \newcommand{\clustername}{\textsl{NAME}}
@@
 \newcommand{\bprp}{\ensuremath{\textrm{BP} - \textrm{RP}}}
+\newcommand{\truepm}{\ensuremath{\tilde{\bs{\mu}}}}
 
@@
 
-We report the discovery of a young ($\lesssim 100~\textrm{Myr}$), metal-poor ($[\textrm{Fe}/\textrm{H}] \sim -1$) stellar association in the halo of the Milky Way ($(R, z) \sim (24, 16) kpc$).
+We report the discovery of a young ($\lesssim 100~\textrm{Myr}$), metal-poor ($[\textrm{Fe}/\textrm{H}] \sim -1$) stellar association in the halo of the Milky Way ($(R, z) \sim (24, 16)~\textrm{kpc}$).
 The association --- \clustername\ --- is likely associated with the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
@@
 
-We then query all objects from the \gaia\ \DR{2} catalog within a polygon centered on the nominal position of the group (see above), with a width of $12^\circ$ and a height of $8^\circ$ in the Magellanic stream coordinate system \citep{Nidever:2008} (see Appendix~\ref{sec:queries} for the database query).
+We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of the group (see above), with a width of $12^\circ$ and a height of $12^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
 We cross-match the resulting catalog with \acronym{GALEX} \todo{citation} using a positional crossmatch requiring source separation $<2~\textrm{arcsec}$, and with \pans\ \todo{citation}\citep{Chambers:XX} using the cross-match provided by the \gaia\ science archive.
@@
 The green polygon in the left panel of \figurename~\ref{fig:cmds} highlights the over-density of blue stars that were identified as comoving from the proper motion search described above.
-The red line in right panel of \figurename~\ref{fig:cmds} is an isochrone (from MIST; \citealt{TODO}) for a $50~\textrm{Myr}$, $\feh = -1$ stellar population.
+The lines in the right panel of \figurename~\ref{fig:cmds} show isochrones from the \acronym{MIST} (blue; \citealt{TODO}) and \acronym{PARSEC} (red; \citealt{TODO}) isochrone libraries for a 50 Myr stellar population with metallicity $\feh = -0.5$ (dashed) or $\feh = -1.5$ (solid).
 
@@
 Green polygon in left panel highlights the over-density of blue, comoving stars identified by the search described in \sectionname~\ref{sec:discovery}.
-Red line in right panel shows the zero-age main sequence of a $50~\textrm{Myr}$, $\feh = -1$ stellar population from the MIST isochrone library \citep{TODO}.
+Red and blue lines in right panel show the zero-age main sequence of a $50~\textrm{Myr}$ stellar population with the metallicity indicated from the \acronym{MIST} \citep{TODO} and \acronym{PARSEC} \citep{TODO} isochrone libraries.
 }
@@
 
-\section{Proper motion cleaned}
+\section{Determining kinematic membership}
 \label{sec:pmclean}
 
-\todo{APW}
+We identify probable members of the photometrically-identified young cluster using astrometric data from \gaia.
+We start by selecting all stars with $\bprp < 0.35$ to remove low-mass and old main sequence star contamination in the region.
+\figurename~\ref{fig:pm-members}, left (grey points), shows the sky positions of stars that pass this blue cut in the region around the young cluster.
+The larger solid-line (green) circle indicates the region we define as the cluster area, and the two smaller dashed-line (blue) circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
+The control fields are designed to, together, have the same total area as the cluster field.
+The top-left panel of the middle panels shows the proper motion distribution in the control fields, and top-right panel in the middle shows the proper motion distribution of the cluster field.
+The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.} is the identified comoving association of blue stars.
+
+To model membership of the cluster based on the observed proper motions, $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, we first construct a model for the error-deconvolved proper motion distribution in the control fields using ``extreme deconvolution'' \citep[XD;][]{TODO} with 3 Gaussian components.
+The bottom-left panel of the middle panels of \figurename~\ref{fig:pm-members} shows the three inferred Gaussian components (blue) from running XD, which takes into account the full error distributions for each proper motion measurement (i.e.
+including covariances), $\mat{C}_\mu$, provided by \gaia\ \DR{2}.
+We fix the parameters of the background model inferred from XD and model the cluster field proper motion distribution using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{m}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
+In detail, taking $f$ to be the fraction of blue stars in this region belonging to the young cluster, and \truepm\ to be the true proper motion for a single star,
+\begin{align}
+    p(\bs{\mu} \given \truepm, \mat{C}_\mu) &=
+        \norm(\bs{\mu} \given \truepm, \mat{C}_\mu)\\
+    p(\truepm \given f, \bs{m}, s) &=
+        f \, p_{\textrm{cl}}(\truepm \given \bs{m}, s)
+        + (1-f) \, p_{\textrm{XD}}(\truepm)\\
+    p_{\textrm{cl}}(\truepm \given \bs{m}, s) &=
+        \norm(\truepm \given \bs{m}, s^2 \, \mathbb{I})
+\end{align}
+where $\norm(\bs{x} \given \bs{m}, \mat{C})$ represents the multidimensional normal distribution with mean $\bs{m}$ and covariance matrix $\mat{C}$, and $\mathbb{I}$ is the identity matrix.
+Because all distributions are Gaussian, the per-star parameters (the true proper motions, \truepm) can be analytically marginalized out so that the per-star likelihood can be expressed as $p(\bs{\mu} \given f, \bs{m}, s, \mat{C}_\mu)$.
+We assume that the measurements for each star, $n$, are independent so that the full likelihood of all $N$ stars given the parameters $(f, \bs{m}, s)$ is
+\begin{align}
+    p(\{\bs{\mu}_n\}_N \given \given f, \bs{m}, s, \{\mat{C}_{\mu, n}\}_N) &=
+        \prod_n^N p(\bs{\mu}_n \given f, \bs{m}, s, \mat{C}_{\mu, n}) \quad .
+        \label{eq:likelihood}
+\end{align}
+
+We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee}][]{Goodman:XX, Foreman-Mackey:2013} to generate posterior samples over the parameters $(f, \bs{m}, s)$ using the likelihood defined above (Equation~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{m}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
+We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
+We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties, and to compute, for each star, posterior probabilities of belonging to the cluster mixture component.
+For the young cluster, we find $\bs{m} = (-0.55,  0.44) \pm (0.03, 0.02)~\masyr$, $\ln s = -3.5 \pm 1$, and $f = 0.24 \pm 0.02$.
+The bottom-left panel of the middle panels of \figurename~\ref{fig:pm-members} shows, in black (small black ellipse), the inferred median proper motion and proper-motion dispersion of the young cluster.
+The proper-motion dispersion is consistent with zero, but is unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.
+
+The bottom-right panel of the middle panels of \figurename~\ref{fig:pm-members} shows all stars in the cluster field, but each marker is colored by the probability of (kinematically) belonging to the young cluster.
+The right (large) panel of \figurename~\ref{fig:pm-members} shows the sky positions of all stars with $\textrm{probability} > 0.5$ of belonging to the cluster: The comoving, blue stars are also a clear spatial over-density in this region.
+\figurename~\ref{fig:pm-members-cmd} shows \gaia\ color-magnitude diagrams for
+
+% Notebook: Proper-motion-membership
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/pm-model.pdf}
+\caption{\todo{APW}
+}
+\label{fig:pm-members}
+\end{figure}
+
+% Notebook: Proper-motion-membership
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/pm-members-cmd.pdf}
+\caption{\todo{APW}
+}
+\label{fig:pm-members-cmd}
+\end{figure}
 
@@
 \todo{APW}
+
+Fit isochrone? Or ask Dan Weisz?
 
@@
 FROM gaiadr2.gaia_source
-WHERE (parallax < 0.5 OR parallax IS NULL) AND
-    CONTAINS(POINT('ICRS', ra, dec),
-             POLYGON('ICRS',
-                     182.1954909980203, -35.51467868323814,
-                     172.7240896740689, -33.70157733692543,
-                     176.3745742549848, -22.277118488646703,
-                     184.81885184435987, -24.236022801996057)) = 1 AND
-    (pmra > -10) AND (pmra < 10) AND
-    (pmdec > -10) AND (pmdec < 10)
+WHERE parallax < 1
+    AND ra > (179-6) AND ra < (179+6)
+    AND dec > (-29-6) AND dec < (-29+6)
 \end{verbatim}
@@
     \package{dustmaps}\footnote{\url{https://github.com/gregreen/dustmaps}},
+    \package{emcee} \citep{emcee},
     \package{gala} \citep{gala},

### 2018-08-01 ms.tex
Update on Overleaf.

@@
 
-We evaluate the hypothesis that the cluster formed in the Leading Arm.
+% We evaluate the hypothesis that the cluster formed in the Leading Arm.
 The mean proper motion values in the Magellanic Stream coordinate system \citep{Nidever:2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.

### 2018-08-01 ms.tex
stuff

--- 2018-08-01 ms.tex
@@
 
-We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee}][]{Goodman:XX, Foreman-Mackey:2013} to generate posterior samples over the parameters $(f, \bs{m}, s)$ using the likelihood defined above (Equation~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{m}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
+We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{Goodman:XX, Foreman-Mackey:2013} to generate posterior samples over the parameters $(f, \bs{m}, s)$ using the likelihood defined above (Equation~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{m}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
 We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
@@
 The bottom-right panel of the middle panels of \figurename~\ref{fig:pm-members} shows all stars in the cluster field, but each marker is colored by the probability of (kinematically) belonging to the young cluster.
-The right (large) panel of \figurename~\ref{fig:pm-members} shows the sky positions of all stars with $\textrm{probability} > 0.5$ of belonging to the cluster: The comoving, blue stars are also a clear spatial over-density in this region.
-\figurename~\ref{fig:pm-members-cmd} shows \gaia\ color-magnitude diagrams for
+The right (large) panel of \figurename~\ref{fig:pm-members} shows the sky positions of all stars with $\textrm{probability} > 0.5$ of belonging to the cluster: The comoving, blue stars show a clear spatial over-density in this region.
+
+\figurename~\ref{fig:pm-members-cmd} shows the \gaia\ color-magnitude diagrams for all stars in this sky region (grey background) and stars with $\text{probability} > 0.5$ of belonging to the young cluster (black markers) in the control field (left, \todo{XX} stars) and cluster field (right, \todo{XX} stars).
+The colored lines show $\[\textrm{Fe}/\textrm{H}\] = -1$ isochrones with ages indicated at a distance of \todo{XX} \kpc.
 
@@
 \centering
-\includegraphics[width=\textwidth]{figures/pm-members-cmd.pdf}
+\includegraphics[width=0.6\textwidth]{figures/pm-members-cmd.pdf}
 \caption{\todo{APW}

### 2018-08-01 ms.tex
Numbers

@@
 We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties, and to compute, for each star, posterior probabilities of belonging to the cluster mixture component.
-For the young cluster, we find $\bs{m} = (-0.55,  0.44) \pm (0.03, 0.02)~\masyr$, $\ln s = -3.5 \pm 1$, and $f = 0.24 \pm 0.02$.
+For the young cluster, we find $\bs{m} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
 The bottom-left panel of the middle panels of \figurename~\ref{fig:pm-members} shows, in black (small black ellipse), the inferred median proper motion and proper-motion dispersion of the young cluster.
@@
 
-\figurename~\ref{fig:pm-members-cmd} shows the \gaia\ color-magnitude diagrams for all stars in this sky region (grey background) and stars with $\text{probability} > 0.5$ of belonging to the young cluster (black markers) in the control field (left, \todo{XX} stars) and cluster field (right, \todo{XX} stars).
+\figurename~\ref{fig:pm-members-cmd} shows the \gaia\ color-magnitude diagrams for all stars in this sky region (grey background) and stars with $\text{probability} > 0.5$ of belonging to the young cluster (black markers) in the control field (left, 5 stars) and cluster field (right, 65 stars).
 The colored lines show $\[\textrm{Fe}/\textrm{H}\] = -1$ isochrones with ages indicated at a distance of \todo{XX} \kpc.

### 2018-08-02 ms.tex
affil and ackn

@@
 
-\author{Edward Schlafly}
+\author[0000-0002-3569-7421]{Edward F. Schlafly}
+\affiliation{Lawrence Berkeley National Laboratory, One Cyclotron Road, Berkeley, CA 94720, USA}
 
-\author{Douglas Finkbeiner}
-% \affiliation{McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, 5000 Forbes Avenue, Pittsburgh, PA 15213, USA}
-% \affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
+\author[0000-0003-2808-275X]{Douglas P. Finkbeiner}
+\affiliation{Institute for Theory and Computation, Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, MS-51, Cambridge, MA 02138, USA}
 
-\author{Sergey E. Koposov}
+\author[0000-0003-2644-135X]{Sergey E. Koposov}
 \affiliation{McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, 5000 Forbes Avenue, Pittsburgh, PA 15213, USA}
@@
 
-\author{Vasily Belokurov}
+\author[0000-0002-0038-9584]{Vasily Belokurov}
 \affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
@@
 
-Fit isochrone? Or ask Dan Weisz?
+\begin{itemize}
+\item Fit isochrone to DECam photometry
+\item Use luminosity function to estimate stellar mass
+\end{itemize}
 
@@
 
+We have identified a young, metal-poor stellar association --- named \clustername\ --- that likely formed from gas in the leading arm of the Magellanic gas stream.
+With an assumed metallicity of $\feh = -1$, the age of the association is \todo{XX} at a distance of \todo{XX}.
+If we fit for metallicity, age, and distance, we find weaker constraints on \todo{...}
+
 \acknowledgments
 
-We thank some people...
+It is a pleasure to thank
+Lauren Anderson (Flatiron),
+Ana Bonaca (Harvard),
+Elena D'Onghia (UW Madison),
+Raja Guhathakurta (UCSC),
+Cliff Johnson (Northwestern),
+Ekta Patel (Arizona)
+Josh Peek (STScI),
+and Erik Tollerud (STScI)
+for useful suggestions and discussion.
 
@@
 \software{
-    \package{Astropy} \citep{astropy},
+    \package{Astropy} \citep{astropy, astropy:2018},
     \package{dustmaps}\footnote{\url{https://github.com/gregreen/dustmaps}},

### 2018-08-02 ms.tex
Caption

@@
 \newcommand{\truepm}{\ensuremath{\tilde{\bs{\mu}}}}
+\newcommand{\isodist}{\ensuremath{25~\kpc}}
 
@@
 \author[0000-0002-1793-3689]{David L. Nidever}
-\affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717-3840, USA}
+\affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717, USA}
 \affiliation{National Optical Astronomy Observatory, 950 North Cherry Ave, Tucson, AZ 85719}
@@
 \figurename~\ref{fig:pm-members-cmd} shows the \gaia\ color-magnitude diagrams for all stars in this sky region (grey background) and stars with $\text{probability} > 0.5$ of belonging to the young cluster (black markers) in the control field (left, 5 stars) and cluster field (right, 65 stars).
-The colored lines show $\[\textrm{Fe}/\textrm{H}\] = -1$ isochrones with ages indicated at a distance of \todo{XX} \kpc.
+The colored lines show $\feh = -1$ isochrones with ages indicated at a distance of \todo{XX} \kpc.
+In the next section, we model the distribution of stars in the \decam\ color-magnitude diagram to determine the characteristics of the stellar population.
 
@@
 \includegraphics[width=0.6\textwidth]{figures/pm-members-cmd.pdf}
-\caption{\todo{APW}
+\caption{\gaia\ color-magnitude diagrams for stars in the sky region around \clustername: grey background in both panels shows the distribution for all stars, and black points show stars with $\textrm{probability} > 0.5$ of (kinematically) belonging to \clustername.
+Left panel is for stars in the control fields, right panel is for stars in the cluster field.
+Colored lines show $\feh = -1$ isochrones from the MIST \citep{TODO} isochrone library for the ages indicated at a distance of \isodist.
 }

### 2018-08-03 ms.tex
fix query

@@
 % Shortcuts for this paper
-\newcommand{\clustername}{\textsl{NAME}}
+\newcommand{\clustername}{\textsl{Price-Whelan 1}}
 \newcommand{\lmcsmc}{LMC--SMC}
@@
 
-We report the discovery of a young ($\lesssim 100~\textrm{Myr}$), metal-poor ($[\textrm{Fe}/\textrm{H}] \sim -1$) stellar association in the halo of the Milky Way ($(R, z) \sim (24, 16)~\textrm{kpc}$).
+We report the discovery of a young, $\lesssim 100~\textrm{Myr}$, metal-poor, $[\textrm{Fe}/\textrm{H}] \sim -1$, comoving stellar association in the halo of the Milky Way, $(R, z) \sim (24, 16)~\textrm{kpc}$.
 The association --- \clustername\ --- is likely associated with the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
@@
 We therefore conclude that this star-formation event was triggered by the last disk passage, which occurred at a Galactocentric radius $R \approx XX~\kpc$.
-
+\todo{Further follow-up needed...spectroscopy}
 \end{abstract}
@@
 
-We identify probable members of the photometrically-identified young cluster using astrometric data from \gaia.
-We start by selecting all stars with $\bprp < 0.35$ to remove low-mass and old main sequence star contamination in the region.
+We select probable members of the photometrically-identified young cluster using astrometric data from \gaia.
+We start by selecting all stars with $\bprp_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
 \figurename~\ref{fig:pm-members}, left (grey points), shows the sky positions of stars that pass this blue cut in the region around the young cluster.
@@
 FROM gaiadr2.gaia_source
-WHERE parallax < 1
-    AND ra > (179-6) AND ra < (179+6)
-    AND dec > (-29-6) AND dec < (-29+6)
+WHERE (parallax < 1 OR parallax IS NULL)
+    AND ra > 173.5 AND ra < 185.5
+    AND dec > -35.0 AND dec < -23.0
 \end{verbatim}

### 2018-08-05 ms.tex
Update on Overleaf.

@@
 \affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717, USA}
-\affiliation{National Optical Astronomy Observatory, 950 North Cherry Ave, Tucson, AZ 85719}
+\affiliation{National Optical Astronomy Observatory, 950 North Cherry Ave, Tucson, AZ 85719, USA}
 
 \author[0000-0003-1680-1884]{Yumi Choi}
-\affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717-3840, USA}
-\affiliation{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson AZ, 85721}
+\affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717, USA}
+\affiliation{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson AZ, 85721, USA}
 

### 2018-08-22 ms.tex
Update on Overleaf.

@@
 The association --- \clustername\ --- is likely associated with the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
-By assuming that the cluster is co-located with HI gas in the stream, we directly measure the distance to the Magellanic stream, $d \approx 25~\textrm{kpc}$.
-At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way.
-\todo{that don't account for ram pressure and gas interaction with MW disk}
+By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $d \approx 25~\textrm{kpc}$.
+At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way \todo{that don't account for ram pressure and gas interaction with MW disk}
 The estimated age of \clustername\ is consistent with the time of last passage through the Galactic midplane.
@@
 The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, and the presence of the Large and Small Magellanic Clouds (LMC, SMC) within the virial radius of the Galaxy.
-While Sagittarius was likely stripped of its neutral gas long ago \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of HI gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Putman:1998, Bruns:2005, Nidever:2010}.
+While Sagittarius was likely stripped of its neutral gas long ago \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Putman:1998, Bruns:2005, Nidever:2010}.
 

### 2018-09-13 ms.tex
Update on Overleaf.

@@
 These systems likely came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
-The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, and the presence of the Large and Small Magellanic Clouds (LMC, SMC) within the virial radius of the Galaxy.
-While Sagittarius was likely stripped of its neutral gas long ago \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Putman:1998, Bruns:2005, Nidever:2010}.
+The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC, SMC) and about 50 dwarf satellites within the virial radius of the Galaxy.
+While Sagittarius was likely stripped of its neutral gas long ago through repeated passage about the Milky Way \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
 
@@
 The stream was discovered in early surveys of 21 cm emission and has since been studied in great detail by large-area radio sky surveys, and in H$\alpha$ emission \citep{Weiner:1996, Barger:2017}.
-With increased resolution, surveys have found small-scale structure and gas fragmentation \citep[e.g.,][]{Nidever:2008, For:2014} and a large-scale bifurcation, with semi-distinct ``strands'' that lead back to the LMC and broader system, respectively \citep[e.g.,][]{Morras:1983, Putman:2003}.
+With increased resolution, surveys have found small-scale structure and gas fragmentation \citep[e.g.,][]{Nidever:2008, For:2014} and a large-scale bifurcation, with %semi-distinct ``strands'' that lead back to the LMC and broader system, respectively \citep[e.g.,][]{Morras:1983, Putman:2003}.
+kinematically \citep{Nidever:2008} and chemically \citep{Fox:2013} distinct ``strands'' that lead back to the LMC and the SMC, respectively.
 As surveys push deeper to lower column densities, extensions of the stream have been found both in the trailing region \citep{Nidever:2010}, but also in the leading arm, which has been found to connect to regions of low-column-density gas ($N\sim 10^{18}$--$10^{19}~\textrm{cm}^{-2}$) on the other side of the Galactic disk \citep{Putman:1998, Nidever:2008}.
@@
 The origin and formation of the LA features in the MS is still uncertain.
-Initial studies of the LA argue that the features closest to the \lmcsmc\ can be traced back to the SMC, thus implying that the gas in the LA was stripped from the SMC \citep{Putman:1998}.
-In more recent work, it has instead been argued that outer features of the LMC appear to lead directly into the LA-1 feature \citep{Nidever:2008}, implying an LMC origin for the leading arm.
-Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the leading arm \citep{Nidever:2008}.
+Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC, thus implying that the gas in the LA was stripped from the SMC \citep{Putman:1998}. 
+In later work, it has instead been argued that outer features of the LMC appear to lead directly into the LA-1 feature \citep{Nidever:2008}, implying an LMC origin for the leading arm.
+Recent chemical abundance measurements along several sightlines passing through the LA again suggested the SMC origin \citep{Fox:2018,Richter:2018}. 
+Hydrodynamical simulations of the MCs on the first infall to the Milky Way, however, showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas creates filamentary gas structures both in the LA and the Magellanic Stream \citep{Pardy:2018}.
+Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the leading arm \citep{Nidever:2008, Besla:2012}.
 However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions with gas in the outer Milky Way disk may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.
@@
 We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of the group (see above), with a width of $12^\circ$ and a height of $12^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
-We cross-match the resulting catalog with \acronym{GALEX} \todo{citation} using a positional crossmatch requiring source separation $<2~\textrm{arcsec}$, and with \pans\ \todo{citation}\citep{Chambers:XX} using the cross-match provided by the \gaia\ science archive.
+We cross-match the resulting catalog with \acronym{GALEX} \citep{Martin:2005} using a positional cross-match requiring source separation $<2~\textrm{arcsec}$, and with \pans\ \citep{Chambers:2016} using the cross-match provided by the \gaia\ science archive.
 \figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram (left) and the \acronym{GALEX} NUV minus \pans\ $g$-band vs.
 \gaia\ \bprp\ color-color diagram (right) from the cross-matched photometry.
-All magnitudes are corrected for dust extinction using the SFD \citep{Schlegel:1998} dust map.
+All magnitudes are corrected for dust extinction using the SFD \citep{Schlegel:1998} dust map {\bf (Yumi: Did you use Schlafly's value though?)}.
 The green polygon in the left panel of \figurename~\ref{fig:cmds} highlights the over-density of blue stars that were identified as comoving from the proper motion search described above.
-The lines in the right panel of \figurename~\ref{fig:cmds} show isochrones from the \acronym{MIST} (blue; \citealt{TODO}) and \acronym{PARSEC} (red; \citealt{TODO}) isochrone libraries for a 50 Myr stellar population with metallicity $\feh = -0.5$ (dashed) or $\feh = -1.5$ (solid).
+The lines in the right panel of \figurename~\ref{fig:cmds} show isochrones from the \acronym{MIST} \citep[blue;][]{Choi:2016} and \acronym{PARSEC} \citep[red;][]{Bressan:2012, Marigo:2017} isochrone libraries for a 50 Myr stellar population with metallicity $\feh = -0.5$ (dashed) or $\feh = -1.5$ (solid).
 

### 2018-10-05 ms.tex
Update on Overleaf.

@@
 Recent chemical abundance measurements along several sightlines passing through the LA again suggested the SMC origin \citep{Fox:2018,Richter:2018}. 
-Hydrodynamical simulations of the MCs on the first infall to the Milky Way, however, showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas creates filamentary gas structures both in the LA and the Magellanic Stream \citep{Pardy:2018}.
+Recent hydrodynamical simulations of the MCs on the first infall to the Milky Way, however, showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas creates filamentary gas structures both in the LA and the Magellanic Stream \citep{Pardy:2018}.
 Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the leading arm \citep{Nidever:2008, Besla:2012}.

### 2018-10-31 ms.tex
Update on Overleaf.
whitespace
todos
abstract and intro

@@
 % - Sand, Seth, et al. Virgo: blue stars with nothing else
-% - Mixture model in proper-motion space, Gaia only
-
-% Proposal
-% - IMACS?
-% - Blue stars - bandpasses have bad Teff resolution
-% - Better Teff, logg -> better age
-% - Big FOV, blue throughput, southern, >4m
+% - Thank DFM
+% - Thank Dylan and Nick @ SCC
+% - Thank Flatiron
 
@@
 
-\author[0000-0002-1793-3689]{David L. Nidever}
+\author[0000-0002-1793-3689]{David~L.~Nidever}
 \affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717, USA}
@@
 
-\author[0000-0003-1680-1884]{Yumi Choi}
+\author[0000-0003-1680-1884]{Yumi~Choi}
 \affiliation{Department of Physics, Montana State University, P.O. Box 173840, Bozeman, MT 59717, USA}
@@
 
-\author[0000-0002-3569-7421]{Edward F. Schlafly}
+\author[0000-0002-8537-5711]{Timothy~Morton} % TODO: check orcID
+\affiliation{Department of Astrophysical Sciences,
+             Princeton University, Princeton, NJ 08544, USA}
+
+\author[0000-0002-3569-7421]{Edward~F.~Schlafly}
 \affiliation{Lawrence Berkeley National Laboratory, One Cyclotron Road, Berkeley, CA 94720, USA}
 
-\author[0000-0003-2808-275X]{Douglas P. Finkbeiner}
+\author[0000-0003-2808-275X]{Douglas~P.~Finkbeiner}
 \affiliation{Institute for Theory and Computation, Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, MS-51, Cambridge, MA 02138, USA}
@@
 
-We report the discovery of a young, $\lesssim 100~\textrm{Myr}$, metal-poor, $[\textrm{Fe}/\textrm{H}] \sim -1$, comoving stellar association in the halo of the Milky Way, $(R, z) \sim (24, 16)~\textrm{kpc}$.
-The association --- \clustername\ --- is likely associated with the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
-By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $d \approx 25~\textrm{kpc}$.
-At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way \todo{that don't account for ram pressure and gas interaction with MW disk}
+We report the discovery of a young, $\sim 150~\textrm{Myr}$, metal-poor, $[\textrm{Fe}/\textrm{H}] \sim -1.2$, stellar association in the halo of the Milky Way, $(R, z) \sim (24, 16)~\textrm{kpc}$.
+% TODO: check with new dist.
+The association --- \clustername\ --- is spatially near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
+By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $d \approx 30~\textrm{kpc}$.
+At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with MW disk.
 The estimated age of \clustername\ is consistent with the time of last passage through the Galactic midplane.
-We therefore conclude that this star-formation event was triggered by the last disk passage, which occurred at a Galactocentric radius $R \approx XX~\kpc$.
-\todo{Further follow-up needed...spectroscopy}
+We therefore speculate that this star-formation event was triggered by the last disk midplane passage of the Magellanic stream gas, which occurred at a Galactocentric radius $R \approx XX~\kpc$.
+However, most details of this idea remain a mystery: the Magellanic Stream is low column density, the Milky Way disk at this large radius has low surface density, and the relative velocity of the gas is large.
+Spectroscopic follow-up is needed to confirm its kinematic association with the Magellanic Stream \hi, but either way \todo{this is an interesting thing.}
 \end{abstract}
@@
 In later work, it has instead been argued that outer features of the LMC appear to lead directly into the LA-1 feature \citep{Nidever:2008}, implying an LMC origin for the leading arm.
-Recent chemical abundance measurements along several sightlines passing through the LA again suggested the SMC origin \citep{Fox:2018,Richter:2018}. 
+Recent chemical abundance measurements along several sightlines passing through the LA again suggested the SMC origin \citep{Fox:2018, Richter:2018}.
 Recent hydrodynamical simulations of the MCs on the first infall to the Milky Way, however, showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas creates filamentary gas structures both in the LA and the Magellanic Stream \citep{Pardy:2018}.
@@
 In this \articlename, we report the discovery of a clustered association of young stars at the far edge of the LA-2 feature ($L_{\textrm{MS}} \sim 65^\circ$) that is unambiguously located far into the Galactic halo ($d_\odot \sim 30~\textrm{kpc}$) and therefore likely formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
-This provides a clear distance measurement to the leading arm of the MS to be compared with models of \lmcsmc\ interaction and infall into the Milky Way.
+This provides a clear distance measurement to the leading arm of the MS to be compared with models of \lmcsmc\ interaction and infall into the Milky Way, and also provides an opportunity to study recent star formation in a regime unlike that of the Milky Way.
+\todo{or any other?}
 
@@
 \caption{\todo{APW}
-}
+Add proper motion vector?}
 \label{fig:pm-members}

### 2018-10-31 ms.tex
cleaning up and acks

@@
 % - Sand, Seth, et al. Virgo: blue stars with nothing else
-% - Thank DFM
-% - Thank Dylan and Nick @ SCC
-% - Thank Flatiron
 
@@
 We use astrometric data from the \gaia\ mission (\citealt{Prusti:2016}), data release 2 (\DR{2}; \citealt{Gaia-Collaboration:2018, Lindegren:2018}) to search for distant, comoving multiplets of blue stars.
-We initially select all stars from \gaia\ with parallax $\varpi < 1$, color $-0.5 < (\bprp) < 0$, $G$-band magnitude $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see Appendix~\ref{sec:queries} for database query).
+Our original intent was to search for small, distant, comoving groups of blue horizontal branch stars to identify new candidate satellites of the Milky Way.
+We therefore initially select all stars from \gaia\ with parallax $\varpi < 1$, color $-0.5 < (\bprp) < 0$, $G$-band magnitude $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see Appendix~\ref{sec:queries} for database query).
 We further exclude stars within a $15^\circ$ radius from the LMC, and a $8^\circ$ radius from the SMC --- 27,895 stars remain after these cuts.
@@
 
-We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of the group (see above), with a width of $12^\circ$ and a height of $12^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
+We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of this group, with a width of $12^\circ$ and a height of $12^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
 We cross-match the resulting catalog with \acronym{GALEX} \citep{Martin:2005} using a positional cross-match requiring source separation $<2~\textrm{arcsec}$, and with \pans\ \citep{Chambers:2016} using the cross-match provided by the \gaia\ science archive.
-\figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram (left) and the \acronym{GALEX} NUV minus \pans\ $g$-band vs.
-\gaia\ \bprp\ color-color diagram (right) from the cross-matched photometry.
-All magnitudes are corrected for dust extinction using the SFD \citep{Schlegel:1998} dust map {\bf (Yumi: Did you use Schlafly's value though?)}.
-The green polygon in the left panel of \figurename~\ref{fig:cmds} highlights the over-density of blue stars that were identified as comoving from the proper motion search described above.
+\figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram (left) and the \acronym{GALEX} NUV minus \pans\ $g$-band versus \gaia\ \bprp\ color-color diagram (right) from the cross-matched photometry.
+All magnitudes are corrected for dust extinction using the SFD \citep{Schlegel:1998, Sclafly:2011} dust map.
+The green polygon in the left panel of \figurename~\ref{fig:cmds} highlights the over-density of blue stars that were identified as comoving from the proper motion search described above: surprisingly, this appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
 The lines in the right panel of \figurename~\ref{fig:cmds} show isochrones from the \acronym{MIST} \citep[blue;][]{Choi:2016} and \acronym{PARSEC} \citep[red;][]{Bressan:2012, Marigo:2017} isochrone libraries for a 50 Myr stellar population with metallicity $\feh = -0.5$ (dashed) or $\feh = -1.5$ (solid).
+\todo{Remake this plot with just FeH=-1.}
 
@@
 
-\section{Determining kinematic membership}
+In the subsections below, we perform two independent analyses of the data available for \clustername.
+In \sectionname~\ref{sec:pmclean}, we use astrometric data from \gaia\ \DR{2} to identify members probabilistically, then demonstrate that the high-probability kinematic members appear as a clear young main sequence in the \gaia\ CMD.
+In \sectionname~\ref{sec:popchars}, we use photometric data from \decam\ to again identify members probabilistically, and simultaneously infer the cluster parameters (age, metallicity, distance, etc.).
+We perform these analyses separately because \gaia\ \DR{2} only includes the most massive members of the cluster, but the addition of lower main sequence members apparent in the \decam\ photometry provide a much better constraint on the cluster parameters.
+
+\subsection{Determining kinematic membership}
 \label{sec:pmclean}
 
-We select probable members of the photometrically-identified young cluster using astrometric data from \gaia.
+We select probable members of \clustername\ by constructing a probabilistic model of the cluster and background population using astrometric data from \gaia.
 We start by selecting all stars with $\bprp_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
@@
 
-To model membership of the cluster based on the observed proper motions, $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, we first construct a model for the error-deconvolved proper motion distribution in the control fields using ``extreme deconvolution'' \citep[XD;][]{TODO} with 3 Gaussian components.
-The bottom-left panel of the middle panels of \figurename~\ref{fig:pm-members} shows the three inferred Gaussian components (blue) from running XD, which takes into account the full error distributions for each proper motion measurement (i.e.
+To model membership of the cluster based on the observed proper motions, $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, we first construct a model for the error-deconvolved proper motion distribution in the control fields using ``extreme deconvolution'' \citep[XD;][]{TODO} with two Gaussian components.
+The bottom-left panel of the middle panels of \figurename~\ref{fig:pm-members} shows the $2\sigma$ contours of the two inferred Gaussian components (blue) from running XD, which takes into account the full error distributions for each proper motion measurement (i.e.
 including covariances), $\mat{C}_\mu$, provided by \gaia\ \DR{2}.
-We fix the parameters of the background model inferred from XD and model the cluster field proper motion distribution using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{m}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
+After running XD, we fix the parameters of the background model and model the cluster field proper motion distribution using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{m}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
 In detail, taking $f$ to be the fraction of blue stars in this region belonging to the young cluster, and \truepm\ to be the true proper motion for a single star,
@@
 The bottom-right panel of the middle panels of \figurename~\ref{fig:pm-members} shows all stars in the cluster field, but each marker is colored by the probability of (kinematically) belonging to the young cluster.
-The right (large) panel of \figurename~\ref{fig:pm-members} shows the sky positions of all stars with $\textrm{probability} > 0.5$ of belonging to the cluster: The comoving, blue stars show a clear spatial over-density in this region.
+The right (large) panel of \figurename~\ref{fig:pm-members} shows the sky positions of all stars with $\textrm{probability} > 0.5$ of belonging to the cluster: These comoving, blue stars show a clear spatial over-density in this region.
 
-\figurename~\ref{fig:pm-members-cmd} shows the \gaia\ color-magnitude diagrams for all stars in this sky region (grey background) and stars with $\text{probability} > 0.5$ of belonging to the young cluster (black markers) in the control field (left, 5 stars) and cluster field (right, 65 stars).
-The colored lines show $\feh = -1$ isochrones with ages indicated at a distance of \todo{XX} \kpc.
+To further validate the existence of this cluster, we visualize the \gaia\ color-magnitude diagrams of the high-probability members in both the control and cluster fields (see leftmost panel of \figurename~\ref{fig:pm-members}).
+\figurename~\ref{fig:pm-members-cmd} shows the CMDs for all stars in this sky region (grey background) in both panels, and stars with $\text{probability} > 0.5$ of belonging to the young cluster (black markers) in the control field (left, 5 stars) and cluster field (right, 65 stars).
+The colored lines show $\feh = -1$ isochrones with ages indicated at a distance of 30~\kpc.
 In the next section, we model the distribution of stars in the \decam\ color-magnitude diagram to determine the characteristics of the stellar population.
@@
 
-\section{Stellar population characteristics}
+\subsection{Stellar population characteristics}
 \label{sec:popchars}
 
-\todo{APW}
+% TODO:
+% - Stellar mass estimate
 
-\begin{itemize}
-\item Fit isochrone to DECam photometry
-\item Use luminosity function to estimate stellar mass
-\end{itemize}
-
-\section{Relation to HI gas}
+\subsection{Relation to HI gas}
 \label{sec:higas}
@@
 In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the position of the position of the cluster with a velocity of \vlsr=70 \kmse.
-
-\begin{figure}
-\centering
-\includegraphics[width=12cm]{sky_pm.png}
-\caption{Figure 1}
-\label{fig_skypm}
-\end{figure}
 
@@
 Elena D'Onghia (UW Madison),
+Dan Foreman-Mackey (Flatiron),
 Raja Guhathakurta (UCSC),
 Cliff Johnson (Northwestern),
-Ekta Patel (Arizona)
+Ekta Patel (Arizona),
 Josh Peek (STScI),
+Anil Seth (\todo{where?}),
 and Erik Tollerud (STScI)
@@
 the institutions participating in the {\it Gaia} Multilateral Agreement.
+
+\todo{Dylan Simon, Nick Carreiro and SCC at Flatiron}
+
+\todo{Flatiron Institute}
 

### 2018-10-31 ms.tex
methods

@@
 \newcommand{\isodist}{\ensuremath{25~\kpc}}
+\newcommand{\eep}{\ensuremath{\acronym{\textrm{EEP}}}}
 
@@
 \submitjournal{ApJL}
-\shorttitle{A recent star formation event in the Magellanic stream}
+\shorttitle{Recent star formation in the Magellanic Stream}
 \shortauthors{Price-Whelan et al.}
@@
 
-\section{Results} \label{sec:results}
+\section{Methods} \label{sec:methods}
 
@@
 In \sectionname~\ref{sec:pmclean}, we use astrometric data from \gaia\ \DR{2} to identify members probabilistically, then demonstrate that the high-probability kinematic members appear as a clear young main sequence in the \gaia\ CMD.
-In \sectionname~\ref{sec:popchars}, we use photometric data from \decam\ to again identify members probabilistically, and simultaneously infer the cluster parameters (age, metallicity, distance, etc.).
+In \sectionname~\ref{sec:popmodel}, we use photometric data from \decam\ to again identify members probabilistically, and simultaneously infer the cluster parameters (age, metallicity, distance, etc.).
 We perform these analyses separately because \gaia\ \DR{2} only includes the most massive members of the cluster, but the addition of lower main sequence members apparent in the \decam\ photometry provide a much better constraint on the cluster parameters.
@@
 Left panel is for stars in the control fields, right panel is for stars in the cluster field.
-Colored lines show $\feh = -1$ isochrones from the MIST \citep{TODO} isochrone library for the ages indicated at a distance of \isodist.
-}
+Colored lines show $\feh = -1$ isochrones from the \acronym{MIST} \citep{TODO} isochrone library for the ages indicated at a distance of \isodist.}
 \label{fig:pm-members-cmd}
@@
 
-\subsection{Stellar population characteristics}
+\subsection{Stellar population modeling}
+\label{sec:popmodel}
+
+The deeper photometry from \decam\ provides a clear view of the stellar population of \clustername\ down to stellar masses $M \sim 0.9~\msun$:
+\figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (single stellar population in right panel).
+We use the $g$- and $i$-band photometry for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
+To summarize our methodology, we generate posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture of a single stellar population and a background population.
+The results of this modeling are presented in \sectionname~\ref{sec:popchars}.
+
+In detail, we start by using the \texttt{isochrones} package \citep{Morton:XXXX} to generate posterior samplings over stellar parameters for each individual source given its photometry and an interim prior.
+We use the \acronym{MIST} \citep{Choi:2016} isochrone library, and \texttt{isochrones} automatically performs interpolation between the provided grid of stellar isochrones to evaluate predicted stellar parameters at a given location in the CMD.
+The stellar parameters for each source are its ``equal evolutionary point'' number $\eep$ (see \acronym{MIST} documentation; \citealt{WHO}), age $\tau$, metallicity $\feh$, extinction $A_V$, and distance $D$, which can be uniquely mapped to a point in the observed CMD;
+The likelihood of a given set of these parameters, $\boldsymbol{\theta} = (\eep, \tau, \feh, A_V, D)$, is then computed from the photometry and (assumed Gaussian) photometric uncertainties given the predicted photometry.
+
+To generate posterior samples, we must also specify prior probability distributions over the parameters $\boldsymbol{\theta}$.
+The priors for each parameter are summarized in \tablename~\ref{tbl:priors}.
+The bounds on $\eep$ limit the isochrone to evolutionary phases between the zero-age main sequence to the terminal-age main sequence.
+The prior and bounds on $A_V$ are set to prefer small and reasonable values of extinction for this moderately high Galactic latitude region.
+The prior on distance assumes a uniform space density of stars.
+
+As expected, we find that the photometry for individual sources in the lower main sequence are very poorly constrained in all parameters, and the prior tends to pull the posterior samplings to prefer closer, older stellar parameters.
+This is a weakness of our methodology for performing the hierarchical inference: each source is considered independently, even though there is clear structure in the CMD (i.e.
+\figurename~\ref{fig:decam-cmd}).
+A more correct way to do this would be to infer the stellar parameters of \emph{all} stars, the cluster hyperparameters, and the background simultaneously.
+However, for the 417 stars we are using (in the red box in \figurename~\ref{fig:decam-cmd}), this model would have $\sim$2,000 free parameters, if left unmarginalized.
+We are developing tools to perform star cluster parameter inference in this way (Morton et al., in prep.), but here we adopt a simple hack to allow us to instead perform individual posterior samplings and then combine into a hierarchical inference.
+
+The brightest stars in the cluster have very precise \decam\ photometry, and have precise astrometry from \gaia, and therefore have membership probabilities from the previous section (\sectionname~\ref{sec:pmclean}).
+Given their location in the CMD, these stars must be young, and so also have much better constrained stellar parameters.
+We therefore use the brightest, high-probability \emph{kinematic} member --- XXX --- as an ``anchor'' star:
+We model every other source (i.e.
+excluding XXX) in the \decam\ selection region by fitting the photometry of it and the anchor star simultaneously, assuming they have the same age, metallicity, distance, and extinction but different \eep\ values.
+Motivated by the possible signature of an (unresolved) binary sequence in the \decam\ CMD, we add one further piece of complexity to the model by allowing the photometry of each non-anchor source to be fit as an unresolved binary star system.
+This adds an additional parameter, the unresolved binary mass ratio $q$, to the list of inferred stellar parameters for each source.
+The details of this model are handled by the \texttt{isochrones} package.
+
+\begin{table}[ht]
+\begin{center}
+    \begin{tabular}{ c | c | c }
+        \toprule
+        Parameter & Prior & Bounds \\
+        \toprule
+        $\eep$ & uniform & $(202, 355)$ \\
+        $\tau$ & uniform & $(10~\textrm{Myr}, 15~\textrm{Gyr})$ \\
+        $\feh$ & uniform & $(-2, 0.5)$ \\
+        $A_V$ & $\propto A_V^{-1}$ & $(0.001, 1)~\textrm{mag}$ \\
+        $D$ & $\propto D^{2}$ & $(1, 100)~\kpc$ \\
+        \toprule
+    \end{tabular}
+\caption{Prior probability distributions for each of the stellar parameters defined in \sectionname~\ref{sec:popmodel}.
+\label{tbl:priors}}
+\end{center}
+\end{table}
+
+In the end, we generate posterior samplings over the parameters $(\boldsymbol{\theta}, q)$ for each of the 417 sources in the selected region of the \decam\ CMD using \texttt{PyMultinest} \citep{TODO}, and store the value of the prior evaluated at the location of each sample.
+We then use these samples and interim prior values to construct our hierarchical model.
+In the hierarchical model, we assume that the stellar parameters of each primary star in the CMD region are either drawn from the cluster, or a background (stellar halo) population.
+For the cluster, we assume the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\boldsymbol{\alpha} = (\mu_\tau, \mu_{\feh}, \mu_D, \mu_{A_V})$ as hyperparameters of the hierarchical inference.
+\todo{Double check that we let all 4 of these free}
+For the background model, we assume the same priors as specified in \tablename~\ref{tbl:priors}.
+The one other parameter of this hierarchical model is the global fraction of sources that are likely cluster members, $f$.
+The full XXX of this model for all $K=417$ source ... \todo{write this down}
+\begin{align}
+    p(\boldsymbol{\theta}_K, q_K, \boldsymbol{\alpha}, f \given \{g, i\}_K )
+        &\propto
+        \prod_k^K p(g_k, i_k \given \boldsymbol{\theta}_k, q_k) \,
+            p(\boldsymbol{\theta}_k, q_k \given \boldsymbol{\alpha}, f) \,
+            p(\boldsymbol{\alpha}) \, p(f)
+\end{align}
+(see \citealt{Hogg:2008, Foreman-Mackey:2013, Price-Whelan:2018} for other examples of this trick). \todo{double check references and add}
+\todo{Make a PGM for this model?}
+
+\todo{OK, so now finally we generate samples in alpha, f using emcee, and now we have inferred the cluster parameters - boo ya}
+
+% Notebook: Figure-DECam-CMD
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{figures/DECam-cmd.pdf}
+\caption{TODO}
+\label{fig:decam-cmd}
+\end{figure}
+
+\section{Results} \label{sec:results}
+
+\subsection{The stellar population of \clustername}
 \label{sec:popchars}
+
+\todo{APW}
 
@@
 
-\subsection{Relation to HI gas}
+\subsection{Relation to \hi gas}
 \label{sec:higas}
@@
 In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the position of the position of the cluster with a velocity of \vlsr=70 \kmse.
-
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{cmd.png}
-\caption{The Gaia DR2 color magnitude diagram of the region showing the pronounced
-young stellar main sequence.}
-\label{fig_cmd}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{isochrone.png}
-\caption{PS1 color magnitude diagrams with young, metal-poor (\feh=-1.0) isochrones overplotted at
-a distance of 25 kpc.}
-\label{fig_isochrone}
-\end{figure}
 
@@
 
+- Stars have the right metallicity to be SMC gas, I think
+
 - TODO: where would interaction point between LMC gas and MW disk gas be today? ~150–200 Myr ago is almost 1 complete disk rotation. see Bekki:2008
@@
 
-We have identified a young, metal-poor stellar association --- named \clustername\ --- that likely formed from gas in the leading arm of the Magellanic gas stream.
-With an assumed metallicity of $\feh = -1$, the age of the association is \todo{XX} at a distance of \todo{XX}.
-If we fit for metallicity, age, and distance, we find weaker constraints on \todo{...}
+We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername --- with an age $\tau \approx 150~\textrm{Myr}$, heliocentric distance $D \approx 30~\kpc$, and metallicity $\feh \approx -1.1$.
+At its present day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic gas stream and thus it plausibly formed from Magellanic stream gas.
+The age of the cluster is broadly consistent with the time it would have crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
+The discovery of \clustername\ provides a critical distance constraint to the Magellanic stream and will aid future Magellanic system and Milky Way modeling efforts.
+It also provides an opportunity to study star formation in a unique environment, unlike that of the Milky Way disk or any other cluster-forming region.
+The serendipitous discovery of this cluster is a reminder that the combined value of the \gaia\ data with deep, large-area imaging surveys will provide many more [...].
 
@@
     \package{numpy} \citep{numpy},
+    \package{schwimmbad} \citep{schwimmbad},
     \package{scipy} \citep{scipy}

### 2018-11-01 ms.tex
describe hierarchical inf

@@
 \newcommand{\sectionname}{Section}
+\newcommand{\equationname}{Equation}
 
@@
 \newcommand{\eep}{\ensuremath{\acronym{\textrm{EEP}}}}
+\newcommand{\Nisofit}{417}
 
@@
 
-We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{Goodman:XX, Foreman-Mackey:2013} to generate posterior samples over the parameters $(f, \bs{m}, s)$ using the likelihood defined above (Equation~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{m}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
+We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{Goodman:XX, Foreman-Mackey:2013} to generate posterior samples over the parameters $(f, \bs{m}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{m}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
 We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
@@
 The stellar parameters for each source are its ``equal evolutionary point'' number $\eep$ (see \acronym{MIST} documentation; \citealt{WHO}), age $\tau$, metallicity $\feh$, extinction $A_V$, and distance $D$, which can be uniquely mapped to a point in the observed CMD;
-The likelihood of a given set of these parameters, $\boldsymbol{\theta} = (\eep, \tau, \feh, A_V, D)$, is then computed from the photometry and (assumed Gaussian) photometric uncertainties given the predicted photometry.
+The likelihood of a given set of these parameters, $\bs{\theta} = (\eep, \tau, \feh, A_V, D)$, is then computed from the photometry and (assumed Gaussian) photometric uncertainties given the predicted photometry.
 
-To generate posterior samples, we must also specify prior probability distributions over the parameters $\boldsymbol{\theta}$.
+To generate posterior samples, we must also specify prior probability distributions over the parameters $\bs{\theta}$.
 The priors for each parameter are summarized in \tablename~\ref{tbl:priors}.
@@
 A more correct way to do this would be to infer the stellar parameters of \emph{all} stars, the cluster hyperparameters, and the background simultaneously.
-However, for the 417 stars we are using (in the red box in \figurename~\ref{fig:decam-cmd}), this model would have $\sim$2,000 free parameters, if left unmarginalized.
+However, for the \Nisofit\ stars we are using (in the red box in \figurename~\ref{fig:decam-cmd}), this model would have $\sim$2,000 free parameters, if left unmarginalized.
 We are developing tools to perform star cluster parameter inference in this way (Morton et al., in prep.), but here we adopt a simple hack to allow us to instead perform individual posterior samplings and then combine into a hierarchical inference.
@@
 
-In the end, we generate posterior samplings over the parameters $(\boldsymbol{\theta}, q)$ for each of the 417 sources in the selected region of the \decam\ CMD using \texttt{PyMultinest} \citep{TODO}, and store the value of the prior evaluated at the location of each sample.
-We then use these samples and interim prior values to construct our hierarchical model.
-In the hierarchical model, we assume that the stellar parameters of each primary star in the CMD region are either drawn from the cluster, or a background (stellar halo) population.
-For the cluster, we assume the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\boldsymbol{\alpha} = (\mu_\tau, \mu_{\feh}, \mu_D, \mu_{A_V})$ as hyperparameters of the hierarchical inference.
-\todo{Double check that we let all 4 of these free}
+Ultimately we generate posterior samplings over the parameters $(\bs{\theta}, q)$ for each of the \Nisofit\ sources in the selected region of the \decam\ CMD using \texttt{PyMultinest} \citep{TODO}, and store the value of the prior evaluated at the location of each sample.
+We then use these samples and interim prior values to construct our hierarchical model, as described below.
+In the hierarchical model, we assume that the stellar parameters of each primary star in the selected region are either drawn from the cluster, or a background (stellar halo) population.
+For the cluster, we assume the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\bs{\alpha} = (\mu_\tau, \mu_{\feh}, \mu_D, \mu_{A_V})$ as hyperparameters of the hierarchical inference.
 For the background model, we assume the same priors as specified in \tablename~\ref{tbl:priors}.
-The one other parameter of this hierarchical model is the global fraction of sources that are likely cluster members, $f$.
-The full XXX of this model for all $K=417$ source ... \todo{write this down}
-\begin{align}
-    p(\boldsymbol{\theta}_K, q_K, \boldsymbol{\alpha}, f \given \{g, i\}_K )
-        &\propto
-        \prod_k^K p(g_k, i_k \given \boldsymbol{\theta}_k, q_k) \,
-            p(\boldsymbol{\theta}_k, q_k \given \boldsymbol{\alpha}, f) \,
-            p(\boldsymbol{\alpha}) \, p(f)
-\end{align}
-(see \citealt{Hogg:2008, Foreman-Mackey:2013, Price-Whelan:2018} for other examples of this trick). \todo{double check references and add}
+The one additional parameter that must be included in this hierarchical model is the ``mixture weight'': the global fraction of sources that are likely cluster members, $f$.
+To compute the likelihood of the hierarchical model, we use the individual posterior samplings to marginalize over the per-source $k$ stellar parameters $\bs{\theta}_k$ to compute the marginal likelihood $p(\bs{m}_k \given \bs{\alpha}, f)$, where $\bs{m}_k = (g, i)_k$ is the vector of photometric data;
+This likelihood for a single source $k$ given a set of hyperparameters $(\bs{\alpha}, f)$ is
+\begin{equation}
+    p(\bs{m}_k \given \bs{\alpha}, f) = \int \dd \bs{\theta}_k \,
+        p(\bs{m}_k \given \bs{\theta}_k) \,
+        p(\bs{\theta}_k \given \bs{\alpha}, f) \quad .
+\end{equation}
+We employ the ``importance sampling trick'' (see, e.g., Appendix of \citealt{Price-Whelan:2018} or \citealt{Hogg:2008, Foreman-Mackey:2013} for other examples) to re-write an approximate form for this marginal likelihood as
+\begin{equation}
+    p(\bs{m}_k \given \bs{\alpha}, f) \approx \frac{\mathcal{Z}_k}{J} \,
+        \sum_j^J \frac{p(\bs{\theta}_{kj} \given \bs{\alpha}, f)}{p(\bs{\theta}_{kj} \given \bs{\alpha}_0, f)}
+        \label{eq:marglike}
+\end{equation}
+where the index $j$ specifies the index of one of $J$ posterior samples generated from the independent samplings (described above), $\mathcal{Z}_k$ is a constant, and the denominator, $p(\bs{\theta}_{kj} \given \bs{\alpha}_0, f)$, are the values of the interim prior used to do the independent samplings.
+In this work, $K=\Nisofit$ and we adopt $J=2048$.
+
+\todo{we ignore the $q$!}
+With the marginal likelihood (\equationname~\ref{eq:marglike}), we then need to specify prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, and we can then generate posterior samples for the hyperparameters;
+We use uniform priors for all of these, as summarized in \tablename~\ref{tbl:hyperpriors}.
+We then use \texttt{emcee} \citep{Goodman:XX, Foreman-Mackey:2013} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
+\begin{equation}
+    p(\bs{\alpha}, f \given \{\bs{m}_k\}) \propto
+        p(\bs{\alpha}) \, p(f) \,
+        \prod_k^K p(\bs{m}_k \given \bs{\alpha}, f) \quad .
+\end{equation}
+Here we use 64 walkers and run for an initial 128 steps to burn-in the sampler before running for a final 1024 steps.
+
+\begin{table}[ht]
+\begin{center}
+    \begin{tabular}{ c | c | c }
+        \toprule
+        Parameter & Prior & Bounds \\
+        \toprule
+        $\mu_\tau$ & uniform & $(1~\textrm{Myr}, 1~\textrm{Gyr})$ \\
+        $\mu_{\feh}$ & uniform & $(-2, 0)$ \\
+        $\mu_{A_V}$ & uniform & $(0, 1)~\textrm{mag}$ \\
+        $\mu_D$ & uniform & $(1, 100)~\kpc$ \\
+        $f$ & uniform & (0, 1) \\
+        \toprule
+    \end{tabular}
+\caption{Prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$.
+\label{tbl:hyperpriors}}
+\end{center}
+\end{table}
+
 \todo{Make a PGM for this model?}
@@
 At its present day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic gas stream and thus it plausibly formed from Magellanic stream gas.
-The age of the cluster is broadly consistent with the time it would have crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
+The age of the cluster is broadly consistent with the time it would have most recently crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
 The discovery of \clustername\ provides a critical distance constraint to the Magellanic stream and will aid future Magellanic system and Milky Way modeling efforts.

### 2018-11-01 ms.tex
new figures

@@
 
+% Notebook: Figure-DECam-CMD
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{figures/DECam-cmd.pdf}
+\caption{TODO}
+\label{fig:decam-cmd}
+\end{figure}
+
 \section{Methods} \label{sec:methods}
@@
 Here we use 64 walkers and run for an initial 128 steps to burn-in the sampler before running for a final 1024 steps.
+\figurename~\ref{fig:hierarch-corner} shows a corner plot showing all 1D and 2D marginal posterior probability distributions estimated from the samples.
 
@@
 
-\todo{OK, so now finally we generate samples in alpha, f using emcee, and now we have inferred the cluster parameters - boo ya}
+We also use the posterior samples from the hierarchical inference to compute the posterior probabilities that each source is a member of the cluster.
+\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
+Over-plotted (blue, solid lines) are \acronym{MIST} isochrones computed from 128 randomly chosen posterior samples, shifted to the distance of the given sample and extincted given the $A_V$ value of the sample.
+Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain an abundance of binary star systems.
 
-% Notebook: Figure-DECam-CMD
+% Notebook: Figure-hierarch-results
 \begin{figure}
 \centering
-\includegraphics[width=0.6\textwidth]{figures/DECam-cmd.pdf}
+\includegraphics[width=0.9\textwidth]{figures/hierarch-corner.pdf}
 \caption{TODO}
-\label{fig:decam-cmd}
+\label{fig:hierarch-corner}
+\end{figure}
+
+% Notebook: Figure-hierarch-results
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{figures/hierarch-results.pdf}
+\caption{TODO}
+\label{fig:hierarch-iso}
 \end{figure}

### 2018-11-01 ms.tex
Way too long for a letter
use x to avoid variable overloading

@@
 
-\submitjournal{ApJL}
+\submitjournal{ApJ}
 \shorttitle{Recent star formation in the Magellanic Stream}
@@
 including covariances), $\mat{C}_\mu$, provided by \gaia\ \DR{2}.
-After running XD, we fix the parameters of the background model and model the cluster field proper motion distribution using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{m}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
+After running XD, we fix the parameters of the background model and model the cluster field proper motion distribution using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{x}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
 In detail, taking $f$ to be the fraction of blue stars in this region belonging to the young cluster, and \truepm\ to be the true proper motion for a single star,
@@
         \norm(\bs{\mu} \given \truepm, \mat{C}_\mu)\\
-    p(\truepm \given f, \bs{m}, s) &=
-        f \, p_{\textrm{cl}}(\truepm \given \bs{m}, s)
+    p(\truepm \given f, \bs{x}, s) &=
+        f \, p_{\textrm{cl}}(\truepm \given \bs{x}, s)
         + (1-f) \, p_{\textrm{XD}}(\truepm)\\
-    p_{\textrm{cl}}(\truepm \given \bs{m}, s) &=
-        \norm(\truepm \given \bs{m}, s^2 \, \mathbb{I})
+    p_{\textrm{cl}}(\truepm \given \bs{x}, s) &=
+        \norm(\truepm \given \bs{x}, s^2 \, \mathbb{I})
 \end{align}
-where $\norm(\bs{x} \given \bs{m}, \mat{C})$ represents the multidimensional normal distribution with mean $\bs{m}$ and covariance matrix $\mat{C}$, and $\mathbb{I}$ is the identity matrix.
-Because all distributions are Gaussian, the per-star parameters (the true proper motions, \truepm) can be analytically marginalized out so that the per-star likelihood can be expressed as $p(\bs{\mu} \given f, \bs{m}, s, \mat{C}_\mu)$.
-We assume that the measurements for each star, $n$, are independent so that the full likelihood of all $N$ stars given the parameters $(f, \bs{m}, s)$ is
+where $\norm(\bs{y} \given \bs{x}, \mat{C})$ represents the multidimensional normal distribution with mean $\bs{x}$ and covariance matrix $\mat{C}$, and $\mathbb{I}$ is the identity matrix.
+Because all distributions are Gaussian, the per-star parameters (the true proper motions, \truepm) can be analytically marginalized out so that the per-star likelihood can be expressed as $p(\bs{\mu} \given f, \bs{x}, s, \mat{C}_\mu)$.
+We assume that the measurements for each star, $n$, are independent so that the full likelihood of all $N$ stars given the parameters $(f, \bs{x}, s)$ is
 \begin{align}
-    p(\{\bs{\mu}_n\}_N \given \given f, \bs{m}, s, \{\mat{C}_{\mu, n}\}_N) &=
-        \prod_n^N p(\bs{\mu}_n \given f, \bs{m}, s, \mat{C}_{\mu, n}) \quad .
+    p(\{\bs{\mu}_n\}_N \given \given f, \bs{x}, s, \{\mat{C}_{\mu, n}\}_N) &=
+        \prod_n^N p(\bs{\mu}_n \given f, \bs{x}, s, \mat{C}_{\mu, n}) \quad .
         \label{eq:likelihood}
@@
 
-We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{Goodman:XX, Foreman-Mackey:2013} to generate posterior samples over the parameters $(f, \bs{m}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{m}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
+We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{Goodman:XX, Foreman-Mackey:2013} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
 We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.

### 2018-11-01 ms.tex
move figure

@@
 
-\todo{Make a PGM for this model?}
-
-We also use the posterior samples from the hierarchical inference to compute the posterior probabilities that each source is a member of the cluster.
-\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
-Over-plotted (blue, solid lines) are \acronym{MIST} isochrones computed from 128 randomly chosen posterior samples, shifted to the distance of the given sample and extincted given the $A_V$ value of the sample.
-Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain an abundance of binary star systems.
+% TODO: Make a PGM for this model?
 
@@
 
+\section{Results} \label{sec:results}
+
+\subsection{The stellar population of \clustername}
+\label{sec:popchars}
+
+We also use the posterior samples from the hierarchical inference to compute the posterior probabilities that each source is a member of the cluster.
+\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
+From the stellar population modeling described above (\sectionname~\ref{sec:popmodel}), we find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx 130~\textrm{Myr}$, distance $D \approx 29~\kpc$, and metallicity $\feh \approx -1.1$.
+Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with these parameters, shifted to the median distance and extincted given the median $A_V$ value.
+Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain an abundance of binary star systems.
+
 % Notebook: Figure-hierarch-results
@@
 
-\section{Results} \label{sec:results}
-
-\subsection{The stellar population of \clustername}
-\label{sec:popchars}
-
-\todo{APW}
-
 % TODO:
@@
 
-\subsection{Relation to \hi gas}
+\subsection{Relation to the Magellanic stream}
 \label{sec:higas}

### 2018-11-02 ms.tex
use star instead of mu

@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/DECam-cmd.pdf}
+\includegraphics[width=0.8\textwidth]{figures/DECam-cmd.pdf}
 \caption{TODO}
@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/pm-members-cmd.pdf}
+\includegraphics[width=0.8\textwidth]{figures/pm-members-cmd.pdf}
 \caption{\gaia\ color-magnitude diagrams for stars in the sky region around \clustername: grey background in both panels shows the distribution for all stars, and black points show stars with $\textrm{probability} > 0.5$ of (kinematically) belonging to \clustername.
@@
 In the hierarchical model, we assume that the stellar parameters of each primary star in the selected region are either drawn from the cluster, or a background (stellar halo) population.
-For the cluster, we assume the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\bs{\alpha} = (\mu_\tau, \mu_{\feh}, \mu_D, \mu_{A_V})$ as hyperparameters of the hierarchical inference.
+For the cluster, we assume the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\bs{\alpha} = (\tau^*, \feh^*, D^*, A_V^*)$ as hyperparameters of the hierarchical inference.
 For the background model, we assume the same priors as specified in \tablename~\ref{tbl:priors}.
@@
         \toprule
-        $\mu_\tau$ & uniform & $(1~\textrm{Myr}, 1~\textrm{Gyr})$ \\
-        $\mu_{\feh}$ & uniform & $(-2, 0)$ \\
-        $\mu_{A_V}$ & uniform & $(0, 1)~\textrm{mag}$ \\
-        $\mu_D$ & uniform & $(1, 100)~\kpc$ \\
+        $\tau^*$ & uniform & $(1~\textrm{Myr}, 1~\textrm{Gyr})$ \\
+        $\feh^*$ & uniform & $(-2, 0)$ \\
+        $A_V^*$ & uniform & $(0, 1)~\textrm{mag}$ \\
+        $D^*$ & uniform & $(1, 100)~\kpc$ \\
         $f$ & uniform & (0, 1) \\

### 2018-11-02 ms.tex
Ack

@@
 Josh Peek (STScI),
-Anil Seth (\todo{where?}),
+Anil Seth (Utah),
 and Erik Tollerud (STScI)
@@
 
-\todo{Dylan Simon, Nick Carreiro and SCC at Flatiron}
-
-\todo{Flatiron Institute}
+We thank the Scientific Computing Core at the Flatiron Institute, and especially Dylan Simon and Nick Carriero, for technical support and access to the Flatiron Institute cluster computing resources, which enabled this work.
+We thank the Center for Computational Astrophysics and especially David Spergel for support, access to computational resources, and space to conduct this work.
 

### 2018-11-02 ms.tex
refs
mass and expansion

@@
 \centering
-\includegraphics[width=0.9\textwidth]{figures/hierarch-corner.pdf}
+\includegraphics[width=0.7\textwidth]{figures/hierarch-corner.pdf}
 \caption{TODO}
@@
 
-We also use the posterior samples from the hierarchical inference to compute the posterior probabilities that each source is a member of the cluster.
+We use the posterior samples from the hierarchical inference described in \sectionname~\ref{sec:popmodel} to compute the posterior probabilities that each source in the \decam\ CMD selection box (red box, \figurename~\ref{fig:decam-cmd}) is a member of the cluster.
 \figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
-From the stellar population modeling described above (\sectionname~\ref{sec:popmodel}), we find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx 130~\textrm{Myr}$, distance $D \approx 29~\kpc$, and metallicity $\feh \approx -1.1$.
-Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with these parameters, shifted to the median distance and extincted given the median $A_V$ value.
+Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
+We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx 130~\textrm{Myr}$, distance $D \approx 29~\kpc$, and metallicity $\feh \approx -1.1$.
 Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain an abundance of binary star systems.
+
+We use the isochrone corresponding to the median posterior sample to estimate the total stellar mass of the cluster.
+By assuming we are 100\% complete to stars with $(g-i) < 0.3)$, and by assuming a Kroupa initial mass function \citep{Kroupa:TODO}, we use the number of observed stars and the isochrone to compute the total mass;
+We find that $M_{\rm tot, *} \approx 1200~\msun$.
+The mass and age of \clustername\ are comparable to Milky Way disk open clusters, but with a much lower metallicity, and a much larger spatial extent.
+For example, the Pleiades has an age $\sim 135~\textrm{Myr}$ \citep{Gossage:2018}, but a physical size $\sim 5~\textrm{pc}$.
+At a distance of $29~\kpc$, \clustername\ spans $\sim 1.5^\circ$, corresponding to a physical size $\sim 760~\textrm{pc}$.
+If it formed unbound, but with a size comparable to the present size of the Pleiades, this corresponds to an expansion velocity $\sim 6~\kms$, which would be detectable with precise radial velocity measurements of stars on either side of \clustername.
 
@@
 \end{figure}
-
-% TODO:
-% - Stellar mass estimate
 
@@
     \package{Astropy} \citep{astropy, astropy:2018},
-    \package{dustmaps}\footnote{\url{https://github.com/gregreen/dustmaps}},
-    \package{emcee} \citep{emcee},
+    \package{dustmaps} \citep{dustmaps},
+    \package{emcee} \citep{emcee, emcee:ascl},
     \package{gala} \citep{gala},

### 2018-11-02 ms.tex
conc end

@@
 It also provides an opportunity to study star formation in a unique environment, unlike that of the Milky Way disk or any other cluster-forming region.
-The serendipitous discovery of this cluster is a reminder that the combined value of the \gaia\ data with deep, large-area imaging surveys will provide many more [...].
+The serendipitous discovery of this cluster is a reminder that the combined value of the \gaia\ data with deep, large-area imaging surveys provides a wealth of information about our Galaxy and stellar halo.
 

### 2018-11-02 ms.tex
macros

@@
 % - Sand, Seth, et al. Virgo: blue stars with nothing else
+% - Keywords after abstract
 
@@
 
+\newcommand{\clage}{\ensuremath{130~\textrm{Myr}}}
+\newcommand{\clfeh}{\ensuremath{-1.1}}
+\newcommand{\cldist}{\ensuremath{29~\textrm{kpc}}}
+
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
@@
 
-\submitjournal{ApJ}
-\shorttitle{Recent star formation in the Magellanic Stream}
+% \submitjournal{ApJ}
+\shorttitle{A recent star formation event in the Magellanic Stream}
 \shortauthors{Price-Whelan et al.}
@@
 % Recent star formation associated with the Leading Arm of the Magellanic stream}
-\title{A star formation event in the leading arm of the Magellanic stream triggered by passage through the outer Galactic disk}
+\title{\textbf{Discovery of a disrupting open cluster in the Galactic halo:\\
+       a recent star formation event in the leading arm of the Magellanic stream}}
 
@@
 
-We report the discovery of a young, $\sim 150~\textrm{Myr}$, metal-poor, $[\textrm{Fe}/\textrm{H}] \sim -1.2$, stellar association in the halo of the Milky Way, $(R, z) \sim (24, 16)~\textrm{kpc}$.
-% TODO: check with new dist.
+We report the discovery of a young $\tau \sim \clage$, metal-poor $[\textrm{Fe}/\textrm{H}] \sim \clfeh$, low-mass $M \sim 1200~\msun$ stellar association in the Milky Way halo, Galactocentric $(R, z) \sim (23, 15)~\textrm{kpc}$.
 The association --- \clustername\ --- is spatially near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
-By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $d \approx 30~\textrm{kpc}$.
+By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $D \approx \cldist$.
 At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with MW disk.
-The estimated age of \clustername\ is consistent with the time of last passage through the Galactic midplane.
-We therefore speculate that this star-formation event was triggered by the last disk midplane passage of the Magellanic stream gas, which occurred at a Galactocentric radius $R \approx XX~\kpc$.
-However, most details of this idea remain a mystery: the Magellanic Stream is low column density, the Milky Way disk at this large radius has low surface density, and the relative velocity of the gas is large.
-Spectroscopic follow-up is needed to confirm its kinematic association with the Magellanic Stream \hi, but either way \todo{this is an interesting thing.}
+The estimated age of \clustername\ is consistent with the time of last passage through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by the last disk midplane passage of the Magellanic stream gas, which occurred at a Galactocentric radius $R \approx 30~\kpc$.
+However, most details of this idea remain a mystery: the Magellanic Stream is low column density, the Milky Way disk at this large radius has low surface density, and the relative velocity of the stream gas and MW gas is large.
+However it formed, the discovery of a young stellar cluster in the Milky Way halo presents an interesting opportunity for study.
 \end{abstract}
@@
 
-\subsection{The stellar population of \clustername}
+\subsection{The stellar population and physical characteristics of \clustername}
 \label{sec:popchars}
@@
 Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
-We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx 130~\textrm{Myr}$, distance $D \approx 29~\kpc$, and metallicity $\feh \approx -1.1$.
-Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain an abundance of binary star systems.
+We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx \clage$, distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$.
+Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain a significant number of binary or multiple star systems.
 
 We use the isochrone corresponding to the median posterior sample to estimate the total stellar mass of the cluster.
-By assuming we are 100\% complete to stars with $(g-i) < 0.3)$, and by assuming a Kroupa initial mass function \citep{Kroupa:TODO}, we use the number of observed stars and the isochrone to compute the total mass;
-We find that $M_{\rm tot, *} \approx 1200~\msun$.
+By assuming that the \decam\ imaging is 100\% complete to stars with $(g-i) < 0.3)$ and $g < 22$, and by assuming a Kroupa initial mass function \citep{Kroupa:TODO}, we use the number of observed stars and the isochrone to compute the total mass, $M_{\rm tot, *} \approx 1200~\msun$.
+
 The mass and age of \clustername\ are comparable to Milky Way disk open clusters, but with a much lower metallicity, and a much larger spatial extent.
 For example, the Pleiades has an age $\sim 135~\textrm{Myr}$ \citep{Gossage:2018}, but a physical size $\sim 5~\textrm{pc}$.
-At a distance of $29~\kpc$, \clustername\ spans $\sim 1.5^\circ$, corresponding to a physical size $\sim 760~\textrm{pc}$.
-If it formed unbound, but with a size comparable to the present size of the Pleiades, this corresponds to an expansion velocity $\sim 6~\kms$, which would be detectable with precise radial velocity measurements of stars on either side of \clustername.
+At a distance of $\cldist$, \clustername\ spans $\sim 1.5^\circ$, corresponding to a physical size $\sim 700$--$800~\textrm{pc}$.
+If it formed unbound, but with an initial size comparable to the present size of the Pleiades, this corresponds to an expansion velocity $\sim 6~\kms$, which would be detectable with precise radial velocity measurements of stars on either side of \clustername.
 
@@
 
-\subsection{Relation to the Magellanic stream}
+\subsection{Relation to the Magellanic Stream}
 \label{sec:higas}
@@
 
+\todo{Radial velocity follow-up is needed for internal motion, and check association with gas}
+
 \begin{figure}
@@
 
+\subsection{The Galactic orbit of \clustername}
+\label{sec:orbit}
+
 \begin{figure}
@@
 
-\section{Discussion} \label{sec:discussion}
-
-- Streams or clusters in the halo from star-formation from Sgr or dwarf gas
-
-- Sgr young globular clusters: same thing as this? Indication of when Sgr lost its gas?
-
-- Stars have the right metallicity to be SMC gas, I think
-
-- TODO: where would interaction point between LMC gas and MW disk gas be today? ~150–200 Myr ago is almost 1 complete disk rotation. see Bekki:2008
+% \section{Discussion} \label{sec:discussion}
+%
+% - Streams or clusters in the halo from star-formation from Sgr or dwarf gas
+%
+% - Sgr young globular clusters: same thing as this? Indication of when Sgr lost its gas?
+%
+% - Stars have the right metallicity to be SMC gas, I think
+%
+% - TODO: where would interaction point between LMC gas and MW disk gas be today? ~150–200 Myr ago is almost 1 complete disk rotation. see Bekki:2008
 
@@
 
-We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername --- with an age $\tau \approx 150~\textrm{Myr}$, heliocentric distance $D \approx 30~\kpc$, and metallicity $\feh \approx -1.1$.
+We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername --- with an age $\tau \approx \clage$, heliocentric distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$.
 At its present day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic gas stream and thus it plausibly formed from Magellanic stream gas.

### 2018-11-02 ms.tex
things

@@
 
-\todo{Nidever}
+At the sky location and distance of \clustername, i.e.
+well into the Galactic halo, the only plausible gas reservoirs that could have formed a young cluster are the Magellanic Stream, or a previously unknown high velocity cloud (HVC).
+HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
+Both processes clearly occur: the Magellanic Stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{TODO} is a metal-rich ($\feh \sim 0.5$), HVC that could have originated from the Galactic disk \citep{TODO}.
 
-We have used the new Gaia data to detect a young, metal-poor cluster in the halo of the Milky Way at a distance of 25 kpc and a MW z-height of 12 kpc.
-The detection of such a young cluster so far from the star-forming disks of any nearby
-galaxy is highly unusual.  However, the proximity of the new cluster to the Leading Arm of the Magellanic Stream suggests
-that the cluster originated from this metal-poor gas \citep{Fox:2018}.
+Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk have, at present-day, significantly higher metallicity than this cluster.
+\figurename~\ref{fig:XXXX} shows the \hi column density in the region around the leading arm of the Magellanic Stream, with the location of \clustername\ marked.
+While no bulk metallicity measurements exist for the LA gas, \todo{...recent measurements suggest comparable to SMC?} \citep{Fox:2018}.
+Given its extragalactic origin, its proximity to the Magellanic Stream suggests that \clustername\ could have formed from this gas.
 Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, MoniBidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
+
+\todo{which gas feature? discuss longitude vs. vlsr}
 
@@
 \label{sec:orbit}
+
+\todo{Assume velocity, get orbit. Lower energy than LMC, but expected if dissipated during star formation? How much orbital energy lost? Give orbital parameters at midplane.}
 

### 2018-11-03 ms.tex
gaia section

@@
 % \submitjournal{ApJ}
-\shorttitle{A recent star formation event in the Magellanic Stream}
+\shorttitle{A recent star formation event in the Magellanic stream}
 \shortauthors{Price-Whelan et al.}
@@
 The estimated age of \clustername\ is consistent with the time of last passage through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by the last disk midplane passage of the Magellanic stream gas, which occurred at a Galactocentric radius $R \approx 30~\kpc$.
-However, most details of this idea remain a mystery: the Magellanic Stream is low column density, the Milky Way disk at this large radius has low surface density, and the relative velocity of the stream gas and MW gas is large.
+However, most details of this idea remain a mystery: the Magellanic stream is low column density, the Milky Way disk at this large radius has low surface density, and the relative velocity of the stream gas and MW gas is large.
 However it formed, the discovery of a young stellar cluster in the Milky Way halo presents an interesting opportunity for study.
@@
 These systems likely came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
-The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC, SMC) and about 50 dwarf satellites within the virial radius of the Galaxy.
+The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC, SMC), and about 50 dwarf satellites within the virial radius of the Galaxy.
 While Sagittarius was likely stripped of its neutral gas long ago through repeated passage about the Milky Way \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
@@
 Recent chemical abundance measurements along several sightlines passing through the LA again suggested the SMC origin \citep{Fox:2018, Richter:2018}.
-Recent hydrodynamical simulations of the MCs on the first infall to the Milky Way, however, showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas creates filamentary gas structures both in the LA and the Magellanic Stream \citep{Pardy:2018}.
+Recent hydrodynamical simulations of the MCs on the first infall to the Milky Way, however, showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas creates filamentary gas structures both in the LA and the Magellanic stream \citep{Pardy:2018}.
 Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the leading arm \citep{Nidever:2008, Besla:2012}.
@@
 
-In this \articlename, we report the discovery of a clustered association of young stars at the far edge of the LA-2 feature ($L_{\textrm{MS}} \sim 65^\circ$) that is unambiguously located far into the Galactic halo ($d_\odot \sim 30~\textrm{kpc}$) and therefore likely formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
+In this \articlename, we report the discovery of a clustered association of young stars at the far edge of the LA-2 feature ($L_{\textrm{MS}} \sim 65^\circ$) that is unambiguously located far into the Galactic halo ($D \sim \cldist$) and therefore plausibly formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
 This provides a clear distance measurement to the leading arm of the MS to be compared with models of \lmcsmc\ interaction and infall into the Milky Way, and also provides an opportunity to study recent star formation in a regime unlike that of the Milky Way.
-\todo{or any other?}
+The discovery of \clustername\ will enable new modeling efforts that track the infall of the LMC-SMC, the tidal stripping of Magellanic gas, and the interaction of this gas with the Milky Way.
 
-In \sectionname~\ref{sec:data}, we present the initial discovery with \gaia\ \DR{2} and follow-up observations with DECam to obtain deeper photometry of the region around the association.
-In \sectionname~\ref{sec:results}, we derive estimates for the total stellar mass of, age of, and distance to the association, and present a plausible formation scenario.
-In \sectionname~\ref{sec:discussion}, we discuss implications for future searches for stars associated with the MS, and discrepancies with existing models of the LA.
+In \sectionname~\ref{sec:data}, we present the initial discovery with \gaia\ \DR{2} and follow-up observations with \decam\ to obtain deeper photometry of the region around the association.
+In \sectionname~\ref{sec:results}, we use the \decam\ photometry to infer the age, metallicity, and distance to \clustername, and discuss plausible formation scenarios for this cluster.
+% In \sectionname~\ref{sec:discussion}, we discuss implications for future searches for stars associated with the MS, and discrepancies with existing models of the LA.
 We conclude in \sectionname~\ref{sec:conclusion}.
@@
 We then combine mutually-connected comoving pairs into small groups of stars that are colocated on the sky and comoving in proper motions, and remove groups that have $<4$ members.
-We cross-match the mean sky positions of the groups to locations of local group galaxies \todo{citation} \citep{Mcconaghie} and Milky Way globular clusters \todo{citation} \citep{Harris} and filter out all groups that lie within 1 degree of these known objects.
+We cross-match the mean sky positions of the groups to locations of local group galaxies \citep{McConnachie:2012} and Milky Way globular clusters \citep[2010 edition;][]{Harris} and filter out all groups that lie within 1 degree of these known objects.
 After these filters, just one group of blue, comoving stars remains at $(\textrm{RA}, \textrm{Dec}) \sim (179, -29)^\circ$.
 
-We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of this group, with a width of $12^\circ$ and a height of $12^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
-We cross-match the resulting catalog with \acronym{GALEX} \citep{Martin:2005} using a positional cross-match requiring source separation $<2~\textrm{arcsec}$, and with \pans\ \citep{Chambers:2016} using the cross-match provided by the \gaia\ science archive.
-\figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram (left) and the \acronym{GALEX} NUV minus \pans\ $g$-band versus \gaia\ \bprp\ color-color diagram (right) from the cross-matched photometry.
-All magnitudes are corrected for dust extinction using the SFD \citep{Schlegel:1998, Sclafly:2011} dust map.
-The green polygon in the left panel of \figurename~\ref{fig:cmds} highlights the over-density of blue stars that were identified as comoving from the proper motion search described above: surprisingly, this appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
-The lines in the right panel of \figurename~\ref{fig:cmds} show isochrones from the \acronym{MIST} \citep[blue;][]{Choi:2016} and \acronym{PARSEC} \citep[red;][]{Bressan:2012, Marigo:2017} isochrone libraries for a 50 Myr stellar population with metallicity $\feh = -0.5$ (dashed) or $\feh = -1.5$ (solid).
-\todo{Remake this plot with just FeH=-1.}
+We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of this group, with a width of $5^\circ$ and a height of $5^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
+\figurename~\ref{fig:cmds} shows the \gaia\ data for this region.
+The left panel of \figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}: Surprisingly, this appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
+The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions, respectively, of all stars in this sky region (grey background density), and only stars in the CMD selection polygon as markers (blue).
+
+The \gaia\ data demonstrate the presence of a co-moving, clustered over-density of blue stars, but the \gaia\ photometry is too shallow to resolve anything but the brightest main sequence stars.
+With the \gaia\ data alone, the distance, age, and metallicity of the cluster therefore cannot be determined, as these quantities are degenerate where the main sequence is nearly vertical.
+In the next section, we describe deeper \decam\ imaging obtained over a portion of the cluster.
 
@@
 \centering
-\includegraphics[width=\textwidth]{figures/gaia-galex-cmd.pdf}
-\caption{Color-magnitude and color-color diagrams with \gaia\ ($G$, BP, RP), \acronym{GALEX} (NUV), and \pans\ ($g$) magnitudes.
+\includegraphics[width=\textwidth]{figures/gaia-cmd-pm.pdf}
+\caption{Color-magnitude diagram, sky positions, and proper motions from \gaia\ \DR{2} for the region around $(\alpha, \delta) \sim (179, -29)^\circ$.
+\textbf{Left panel}: \gaia\ color-magnitude diagram (CMD) for all sources with $G < 20$ and sky position within 3 degrees of $(\alpha, \delta) = (179.5, -28.8)^\circ$.
+Red line shows a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone shifted to a distance of $30~\kpc$.
 Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
-Green polygon in left panel highlights the over-density of blue, comoving stars identified by the search described in \sectionname~\ref{sec:discovery}.
-Red and blue lines in right panel show the zero-age main sequence of a $50~\textrm{Myr}$ stellar population with the metallicity indicated from the \acronym{MIST} \citep{TODO} and \acronym{PARSEC} \citep{TODO} isochrone libraries.
+\textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).
+Blue markers show only sources in the blue selection polygon shown in the CMD (left panel).
+\textbf{Right panel}: Proper motions for all sources in the shown sky region (grey 2D histogram).
+Blue markers again show only sources in the blue CMD selection region (left panel).
 }
@@
 
-\subsection{Relation to the Magellanic Stream}
+\subsection{Relation to the Magellanic stream}
 \label{sec:higas}
@@
 At the sky location and distance of \clustername, i.e.
-well into the Galactic halo, the only plausible gas reservoirs that could have formed a young cluster are the Magellanic Stream, or a previously unknown high velocity cloud (HVC).
+well into the Galactic halo, the only plausible gas reservoirs that could have formed a young cluster are the Magellanic stream, or a previously unknown high velocity cloud (HVC).
 HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
-Both processes clearly occur: the Magellanic Stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{TODO} is a metal-rich ($\feh \sim 0.5$), HVC that could have originated from the Galactic disk \citep{TODO}.
+Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{TODO} is a metal-rich ($\feh \sim 0.5$) HVC that could have originated from the Galactic disk \citep{TODO}.
+Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk that could have driven gas out into the halo have, at present-day, significantly higher metallicity than this cluster.
 
-Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk have, at present-day, significantly higher metallicity than this cluster.
-\figurename~\ref{fig:XXXX} shows the \hi column density in the region around the leading arm of the Magellanic Stream, with the location of \clustername\ marked.
+Here we take a closer look at the \hi gas in the vicinity of \clustername.
+\figurename~\ref{fig:XXXX} shows the \hi column density in the region around the leading arm of the Magellanic stream, with the location of \clustername\ marked.
 While no bulk metallicity measurements exist for the LA gas, \todo{...recent measurements suggest comparable to SMC?} \citep{Fox:2018}.
-Given its extragalactic origin, its proximity to the Magellanic Stream suggests that \clustername\ could have formed from this gas.
+Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.
 Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, MoniBidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
@@
 % We evaluate the hypothesis that the cluster formed in the Leading Arm.
-The mean proper motion values in the Magellanic Stream coordinate system \citep{Nidever:2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.
+The mean proper motion values in the Magellanic stream coordinate system \citep{Nidever:2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.
 The simulations of \citet{Besla:2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.
-The Magellanic Stream simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the effects of ram pressure from the hot MW halo which could cause the gas to drop in its orbit to smaller Galactocentric distances (NEED TO DOUBLE-CHECK THIS).
+The Magellanic stream simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the effects of ram pressure from the hot MW halo which could cause the gas to drop in its orbit to smaller Galactocentric distances (NEED TO DOUBLE-CHECK THIS).
 In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the position of the position of the cluster with a velocity of \vlsr=70 \kmse.
@@
 WHERE (parallax < 1 OR parallax IS NULL)
-    AND ra > 173.5 AND ra < 185.5
-    AND dec > -35.0 AND dec < -23.0
+    AND ra > 177 AND ra < 182
+    AND dec > -31.3 AND dec < -26.3
 \end{verbatim}

### 2018-11-03 ms.tex
captions and data section

@@
 The left panel of \figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}: Surprisingly, this appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
-The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions, respectively, of all stars in this sky region (grey background density), and only stars in the CMD selection polygon as markers (blue).
+The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions, respectively, of all stars in this sky region (grey background density), and only stars in the CMD selection polygon as black markers.
 
-The \gaia\ data demonstrate the presence of a co-moving, clustered over-density of blue stars, but the \gaia\ photometry is too shallow to resolve anything but the brightest main sequence stars.
+The \gaia\ data demonstrate the presence of a young, distant, spatially-clustered, and co-moving stellar over-density --- named \clustername\ --- but the \gaia\ photometry is too shallow to resolve anything but the brightest main sequence stars.
 With the \gaia\ data alone, the distance, age, and metallicity of the cluster therefore cannot be determined, as these quantities are degenerate where the main sequence is nearly vertical.
@@
 \textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).
-Blue markers show only sources in the blue selection polygon shown in the CMD (left panel).
+Black markers show only sources in the blue selection polygon shown in the CMD (left panel).
 \textbf{Right panel}: Proper motions for all sources in the shown sky region (grey 2D histogram).
-Blue markers again show only sources in the blue CMD selection region (left panel).
+Black markers again show only sources in the blue CMD selection region (left panel).
 }
@@
 
-\todo{Nidever}
+We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on a portion of the cluster discovered using the \gaia\ data (see previous section).
+\todo{Nidever: can you describe the observations? Exposure times, dither, whatever is usually done...}
 
-% Figure \ref{fig_skypm} shows the spatial and proper motion distribution in the region of interest with the objects in
-% a small proper motion selection shown as black and red dots.  The color magnitude diagram (CMD) of the same objects
-% is shown in Figure \ref{fig_cmd} and clearly reveals a sequence of objects that follow the shape of a young main-sequence.
-% The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at fa distance of 25 kpc.
-Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths:2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever:2008}.
-% The component of the LA II can be seen on the left-hand side of the figure and a similar \hie stream can be seen near the
-% position of the cluster.
-% Yumi:
-% Need a sentence or two for dust extinction correction somewhere in the above two paragraphs?
+The photometry was reduced...\todo{Nidever: describe your pipeline?}
+
+\figurename~\ref{fig:decam-field} shows the sky positions of the \gaia\ CMD-selected sources (black markers; see same in middle panel, \figurename~\ref{fig:cmds}), along with point sources identified in the $g$-band data obtained with \decam: sources in control fields are shown as red markers, and sources in cluster fields are shown as blue markers.
+We note that the smaller over-density located northeast of the \decam\ field was not followed up in this work.
+
+\figurename~\ref{fig:decam-cmd} shows \decam\ color-magnitude diagrams for the control and cluster sub-fields (the magnitudes here are not extinction-corrected).
+We find that the $u$-band data were too shallow to be useful for this work, so restrict the further analysis in this work to the $g$- and $i$-bands.
+The blue comoving group, \clustername, identified in \sectionname~\ref{sec:discovery} using \gaia\ data alone shows up as a clear young main sequence in the cluster fields (right panel of \figurename~\ref{fig:decam-cmd}).
+Later, we use photometry in the sub-region of the cluster fields identified by the dashed rectangle to infer the cluster parameters.
+
+ % Notebook: Figure-DECam-CMD
+ \begin{figure}
+ \centering
+ \includegraphics[width=0.6\textwidth]{figures/DECam-field.pdf}
+ \caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ $g$-band follow up (blue and red markers).
+ Red markers show sources in the \decam\ field used as control sources, and blue markers show sources used as cluster member candidates.}
+ \label{fig:decam-field}
+ \end{figure}
 
@@
 \includegraphics[width=0.8\textwidth]{figures/DECam-cmd.pdf}
-\caption{TODO}
+\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
+Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
+The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
+}
 \label{fig:decam-cmd}
@@
 
+% TODO: change to just inferring mean proper motion of the cluster!
 \subsection{Determining kinematic membership}

### 2018-11-03 ms.tex
methods description

@@
 In the subsections below, we perform two independent analyses of the data available for \clustername.
-In \sectionname~\ref{sec:pmclean}, we use astrometric data from \gaia\ \DR{2} to identify members probabilistically, then demonstrate that the high-probability kinematic members appear as a clear young main sequence in the \gaia\ CMD.
-In \sectionname~\ref{sec:popmodel}, we use photometric data from \decam\ to again identify members probabilistically, and simultaneously infer the cluster parameters (age, metallicity, distance, etc.).
+First, in \sectionname~\ref{sec:pmclean}, we use astrometric data from \gaia\ \DR{2} to determine the mean proper motion of the cluster by modeling the kinematics of the cluster and background sources.
+Then, in \sectionname~\ref{sec:popmodel}, we use photometric data from \decam\ to assign membership probabilities to sources and simultaneously infer the cluster stellar population parameters (age, metallicity, distance, etc.).
 We perform these analyses separately because \gaia\ \DR{2} only includes the most massive members of the cluster, but the addition of lower main sequence members apparent in the \decam\ photometry provide a much better constraint on the cluster parameters.

### 2018-11-03 ms.tex
todo
shtuff

@@
 
-% TODO: change to just inferring mean proper motion of the cluster!
-\subsection{Determining kinematic membership}
+\subsection{Measuring the mean proper motion of \clustername}
 \label{sec:pmclean}
 
-We select probable members of \clustername\ by constructing a probabilistic model of the cluster and background population using astrometric data from \gaia.
+We infer the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background population using astrometric data from \gaia.
 We start by selecting all stars with $\bprp_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
 \figurename~\ref{fig:pm-members}, left (grey points), shows the sky positions of stars that pass this blue cut in the region around the young cluster.
-The larger solid-line (green) circle indicates the region we define as the cluster area, and the two smaller dashed-line (blue) circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
+The larger solid-line circle indicates the region we define as the cluster area, and the two smaller dashed-line circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
 The control fields are designed to, together, have the same total area as the cluster field.
-The top-left panel of the middle panels shows the proper motion distribution in the control fields, and top-right panel in the middle shows the proper motion distribution of the cluster field.
+The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.
 The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.} is the identified comoving association of blue stars.
 
-To model membership of the cluster based on the observed proper motions, $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, we first construct a model for the error-deconvolved proper motion distribution in the control fields using ``extreme deconvolution'' \citep[XD;][]{TODO} with two Gaussian components.
-The bottom-left panel of the middle panels of \figurename~\ref{fig:pm-members} shows the $2\sigma$ contours of the two inferred Gaussian components (blue) from running XD, which takes into account the full error distributions for each proper motion measurement (i.e.
+To measure the mean cluster proper motion, $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, we first construct a model for the error-deconvolved proper motion distribution in the control fields using ``extreme deconvolution'' \citep[XD;][]{Bovy:2011} with two Gaussian components, which takes into account the full error distributions for each proper motion measurement (i.e.
 including covariances), $\mat{C}_\mu$, provided by \gaia\ \DR{2}.
-After running XD, we fix the parameters of the background model and model the cluster field proper motion distribution using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{x}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
+After running XD, we fix the parameters of the background model and model the proper motion distribution in the cluster region using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{x}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
 In detail, taking $f$ to be the fraction of blue stars in this region belonging to the young cluster, and \truepm\ to be the true proper motion for a single star,
@@
 
-We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{Goodman:XX, Foreman-Mackey:2013} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
+We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{Goodman:2010, emcee} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
 We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
-We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties, and to compute, for each star, posterior probabilities of belonging to the cluster mixture component.
+We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
 For the young cluster, we find $\bs{m} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
-The bottom-left panel of the middle panels of \figurename~\ref{fig:pm-members} shows, in black (small black ellipse), the inferred median proper motion and proper-motion dispersion of the young cluster.
-The proper-motion dispersion is consistent with zero, but is unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.
-
-The bottom-right panel of the middle panels of \figurename~\ref{fig:pm-members} shows all stars in the cluster field, but each marker is colored by the probability of (kinematically) belonging to the young cluster.
-The right (large) panel of \figurename~\ref{fig:pm-members} shows the sky positions of all stars with $\textrm{probability} > 0.5$ of belonging to the cluster: These comoving, blue stars show a clear spatial over-density in this region.
-
-To further validate the existence of this cluster, we visualize the \gaia\ color-magnitude diagrams of the high-probability members in both the control and cluster fields (see leftmost panel of \figurename~\ref{fig:pm-members}).
-\figurename~\ref{fig:pm-members-cmd} shows the CMDs for all stars in this sky region (grey background) in both panels, and stars with $\text{probability} > 0.5$ of belonging to the young cluster (black markers) in the control field (left, 5 stars) and cluster field (right, 65 stars).
-The colored lines show $\feh = -1$ isochrones with ages indicated at a distance of 30~\kpc.
-In the next section, we model the distribution of stars in the \decam\ color-magnitude diagram to determine the characteristics of the stellar population.
+The proper-motion dispersion is consistent with zero, so is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.
 
@@
 \label{fig:pm-members}
-\end{figure}
-
-% Notebook: Proper-motion-membership
-\begin{figure}
-\centering
-\includegraphics[width=0.8\textwidth]{figures/pm-members-cmd.pdf}
-\caption{\gaia\ color-magnitude diagrams for stars in the sky region around \clustername: grey background in both panels shows the distribution for all stars, and black points show stars with $\textrm{probability} > 0.5$ of (kinematically) belonging to \clustername.
-Left panel is for stars in the control fields, right panel is for stars in the cluster field.
-Colored lines show $\feh = -1$ isochrones from the \acronym{MIST} \citep{TODO} isochrone library for the ages indicated at a distance of \isodist.}
-\label{fig:pm-members-cmd}
 \end{figure}
@@
 \section{Results} \label{sec:results}
+
+% TODO: make a table with all inferred parameters!
+% - mean sky position
+% - inferred proper motion
+% - distance
+% - age, metallicity, mass
+% - extinction
 

### 2018-11-03 ms.tex
more references

@@
 We then combine mutually-connected comoving pairs into small groups of stars that are colocated on the sky and comoving in proper motions, and remove groups that have $<4$ members.
-We cross-match the mean sky positions of the groups to locations of local group galaxies \citep{McConnachie:2012} and Milky Way globular clusters \citep[2010 edition;][]{Harris} and filter out all groups that lie within 1 degree of these known objects.
+We cross-match the mean sky positions of the groups to locations of local group galaxies \citep{McConnachie:2012} and Milky Way globular clusters \citep[2010 edition;][]{Harris:1996} and filter out all groups that lie within 1 degree of these known objects.
 After these filters, just one group of blue, comoving stars remains at $(\textrm{RA}, \textrm{Dec}) \sim (179, -29)^\circ$.
@@
 
-In detail, we start by using the \texttt{isochrones} package \citep{Morton:XXXX} to generate posterior samplings over stellar parameters for each individual source given its photometry and an interim prior.
+In detail, we start by using the \texttt{isochrones} package \citep{Morton:2015} to generate posterior samplings over stellar parameters for each individual source given its photometry and an interim prior.
 We use the \acronym{MIST} \citep{Choi:2016} isochrone library, and \texttt{isochrones} automatically performs interpolation between the provided grid of stellar isochrones to evaluate predicted stellar parameters at a given location in the CMD.
-The stellar parameters for each source are its ``equal evolutionary point'' number $\eep$ (see \acronym{MIST} documentation; \citealt{WHO}), age $\tau$, metallicity $\feh$, extinction $A_V$, and distance $D$, which can be uniquely mapped to a point in the observed CMD;
+The stellar parameters for each source are its ``equal evolutionary point'' number $\eep$ (see \acronym{MIST} documentation\footnote{\url{http://waps.cfa.harvard.edu/MIST/}}), age $\tau$, metallicity $\feh$, extinction $A_V$, and distance $D$, which can be uniquely mapped to a point in the observed CMD;
 The likelihood of a given set of these parameters, $\bs{\theta} = (\eep, \tau, \feh, A_V, D)$, is then computed from the photometry and (assumed Gaussian) photometric uncertainties given the predicted photometry.
@@
 \end{equation}
-We employ the ``importance sampling trick'' (see, e.g., Appendix of \citealt{Price-Whelan:2018} or \citealt{Hogg:2008, Foreman-Mackey:2013} for other examples) to re-write an approximate form for this marginal likelihood as
+We employ the ``importance sampling trick'' (see, e.g., Appendix of \citealt{Price-Whelan:2018} or \citealt{Hogg:2010, Foreman-Mackey:2014} for other examples) to re-write an approximate form for this marginal likelihood as
 \begin{equation}
@@
 We use uniform priors for all of these, as summarized in \tablename~\ref{tbl:hyperpriors}.
-We then use \texttt{emcee} \citep{Goodman:XX, Foreman-Mackey:2013} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
+We then use \texttt{emcee} \citep{Goodman:2010, Foreman-Mackey:2013} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
 \begin{equation}

### 2018-11-03 ms.tex
names

@@
 \centering
-\includegraphics[width=0.8\textwidth]{figures/DECam-cmd.pdf}
+\includegraphics[width=0.6\textwidth]{figures/DECam-cmd.pdf}
 \caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
@@
 
-\subsection{Measuring the mean proper motion of \clustername}
+\subsection{Inferring the mean proper motion}
 \label{sec:pmclean}
@@
 
-\subsection{Stellar population modeling}
+\subsection{Inferring the stellar population parameters}
 \label{sec:popmodel}
@@
 We use uniform priors for all of these, as summarized in \tablename~\ref{tbl:hyperpriors}.
-We then use \texttt{emcee} \citep{Goodman:2010, Foreman-Mackey:2013} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
+We then use \texttt{emcee} \citep{Goodman:2010, emcee} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
 \begin{equation}

### 2018-11-03 ms.tex
authors
reorg

@@
 
-\author[0000-0002-8537-5711]{Timothy~Morton} % TODO: check orcID
-\affiliation{Department of Astrophysical Sciences,
-             Princeton University, Princeton, NJ 08544, USA}
-
 \author[0000-0002-3569-7421]{Edward~F.~Schlafly}
@@
 \affiliation{Institute for Theory and Computation, Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, MS-51, Cambridge, MA 02138, USA}
+
+\author[0000-0002-8537-5711]{Timothy~Morton} % TODO: check orcID
+\affiliation{Department of Astrophysical Sciences,
+             Princeton University, Princeton, NJ 08544, USA}
 
@@
 
-We report the discovery of a young $\tau \sim \clage$, metal-poor $[\textrm{Fe}/\textrm{H}] \sim \clfeh$, low-mass $M \sim 1200~\msun$ stellar association in the Milky Way halo, Galactocentric $(R, z) \sim (23, 15)~\textrm{kpc}$.
-The association --- \clustername\ --- is spatially near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
+We report the discovery of a young $\tau \sim \clage$, low-mass $M \sim 1200~\msun$, metal-poor $[\textrm{Fe}/\textrm{H}] \sim \clfeh$ stellar association in the Milky Way halo, \clustername.
+At a Galactocentric position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
 By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $D \approx \cldist$.
@@
 
-The halo of the Milky Way is characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
-This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the formation of the Galaxy: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
-These systems likely came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
-The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC, SMC), and about 50 dwarf satellites within the virial radius of the Galaxy.
-While Sagittarius was likely stripped of its neutral gas long ago through repeated passage about the Milky Way \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
+% The halo of the Milky Way is characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
+% This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the formation of the Galaxy: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
+% These systems likely came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
+% The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC, SMC), and about 50 dwarf satellites within the virial radius of the Galaxy.
+% While Sagittarius was likely stripped of its neutral gas long ago through repeated passage about the Milky Way \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
 
-The Magellanic stream (MS) is a large stream of (predominantly) hydrogen gas emanating from the \lmcsmc\ system that contains a significant fraction of the total gas mass associated with the \lmcsmc\ \citep{Bruns:2005}.
+The Magellanic stream (MS) is a large stream of (predominantly) hydrogen gas emanating from the \lmcsmc\ system that contains a significant fraction of the total gas mass associated with the \lmcsmc\ \citep{Bruns:2005} and wraps nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
 The stream was discovered in early surveys of 21 cm emission and has since been studied in great detail by large-area radio sky surveys, and in H$\alpha$ emission \citep{Weiner:1996, Barger:2017}.
@@
 
-We infer the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background population using astrometric data from \gaia.
+We infer the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background populations using astrometric data from \gaia.
 We start by selecting all stars with $\bprp_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.

### 2018-11-03 ms.tex
captions

@@
 % - Keywords after abstract
+% - Split cluster into 2? Price-Whelan 1a and 1b?
 
@@
 We infer the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background populations using astrometric data from \gaia.
-We start by selecting all stars with $\bprp_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
+We start by selecting all stars with $(\bprp)_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
 \figurename~\ref{fig:pm-members}, left (grey points), shows the sky positions of stars that pass this blue cut in the region around the young cluster.
@@
 The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.} is the identified comoving association of blue stars.
+Note that \figurename~\ref{fig:pm-members} is only meant an illustration: The cluster proper motion is determined probabilistically by taking into account the full \gaia\ covariance matrices for each source, as described below.
 
@@
 \includegraphics[width=\textwidth]{figures/pm-model.pdf}
-\caption{\todo{APW}
-Add proper motion vector?}
+\caption{\textbf{Left panel}: Sky positions of all \gaia\ sources in this region with $\bprp < 0.35$ (grey markers).
+The circles show the regions used as cluster and control fields in the proper motion inference (\sectionname~\ref{sec:pmclean}).
+The control fields, together, have the same area as the cluster field.
+\textbf{Right panel}: The colored 2D density shows the difference in number of sources per pixel in the cluster field versus the two control fields (see left panel).
+The clear over-density in the cluster field (blue) are stars in \clustername.}
 \label{fig:pm-members}
@@
 \includegraphics[width=0.7\textwidth]{figures/hierarch-corner.pdf}
-\caption{TODO}
+\caption{A corner plot showing marginal posterior probability distributions estimated from the the posterior samples generated from the hierarchical inference of the cluster population parameters.}
 \label{fig:hierarch-corner}
@@
 \section{Results} \label{sec:results}
-
-% TODO: make a table with all inferred parameters!
-% - mean sky position
-% - inferred proper motion
-% - distance
-% - age, metallicity, mass
-% - extinction
 
@@
 \includegraphics[width=0.6\textwidth]{figures/hierarch-results.pdf}
-\caption{TODO}
+\caption{The \decam\ color-magnitude diagram for sources with probabilty $>0.5$ of belonging to \clustername\ (markers).
+The solid line (blue) shows the \acronym{MIST} isochrone for the median posterior sample from the hierarchical inference of the cluster population parameters, shifted to the inferred distance to \clustername, and extincted with the inferred extinction.
+The dashed line (green) shows the same isochrone, shifted $\approx 0.75$ magnitudes brighter, representing the expected location of the equal-mass binary sequence of the cluster.
+}
 \label{fig:hierarch-iso}
 \end{figure}
+
+\begin{table}[ht]
+\begin{center}
+    \begin{tabular}{ r | l | l}
+        \toprule
+        Parameter & Value & Description \\
+        \tableline
+        $\mean{\alpha}$ & $178.8^\circ$ & mean right ascension \\
+        $\mean{\delta}$ & $-29.4^\circ$ & mean declination \\
+        $\mean{D}$ & $29~\kpc$ & mean Heliocentric distance \\
+        $\mean{\mu_\alpha}$ & $-0.56~\masyr$ & mean proper motion in RA\\
+        $\mean{\mu_\delta}$ & $0.47~\masyr$ & mean proper motion in Dec\\
+        \tableline
+        $\tau$ & $130~\textrm{Myr}$ & age \\
+        $M$ & $1200~\msun$ & total mass \\
+        $\feh$ & $-1.1$ & metallicity \\
+        \tableline
+        $A_V$ & $0.3$ & extinction \\
+        \toprule
+    \end{tabular}
+\caption{Inferred parameters for \clustername.
+\label{tbl:clusterparams}}
+\end{center}
+\end{table}
 

### 2018-11-04 ms.tex
twocolumn

@@
 % - Sand, Seth, et al. Virgo: blue stars with nothing else
-% - Keywords after abstract
 % - Split cluster into 2? Price-Whelan 1a and 1b?
 
-\documentclass[modern]{aastex62}
+% \documentclass[modern]{aastex62}
+\documentclass[twocolumn]{aastex62}
 \usepackage{amsmath}
@@
 We report the discovery of a young $\tau \sim \clage$, low-mass $M \sim 1200~\msun$, metal-poor $[\textrm{Fe}/\textrm{H}] \sim \clfeh$ stellar association in the Milky Way halo, \clustername.
-At a Galactocentric position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
+At a Galactocentric (cylindrical) position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
 By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $D \approx \cldist$.
@@
 
-\keywords{Galaxy: halo}
+\keywords{
+    Galaxy: open clusters and associations --
+    Galaxy: halo --
+    stars: formation --
+    surveys}
 
@@
 
+% Notebook: Figure-CMDs
+\begin{figure*}[htb!]
+\centering
+\includegraphics[width=\textwidth]{figures/gaia-cmd-pm.pdf}
+\caption{Color-magnitude diagram, sky positions, and proper motions from \gaia\ \DR{2} for the region around $(\alpha, \delta) \sim (179, -29)^\circ$.
+\textbf{Left panel}: \gaia\ color-magnitude diagram (CMD) for all sources with $G < 20$ and sky position within 3 degrees of $(\alpha, \delta) = (179.5, -28.8)^\circ$.
+Red line shows a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone shifted to a distance of $30~\kpc$.
+Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
+\textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).
+Black markers show only sources in the blue selection polygon shown in the CMD (left panel).
+\textbf{Right panel}: Proper motions for all sources in the shown sky region (grey 2D histogram).
+Black markers again show only sources in the blue CMD selection region (left panel).
+}
+\label{fig:cmds}
+\end{figure*}
+
 \section{Data} \label{sec:data}
@@
 
-% Notebook: Figure-CMDs
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/gaia-cmd-pm.pdf}
-\caption{Color-magnitude diagram, sky positions, and proper motions from \gaia\ \DR{2} for the region around $(\alpha, \delta) \sim (179, -29)^\circ$.
-\textbf{Left panel}: \gaia\ color-magnitude diagram (CMD) for all sources with $G < 20$ and sky position within 3 degrees of $(\alpha, \delta) = (179.5, -28.8)^\circ$.
-Red line shows a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone shifted to a distance of $30~\kpc$.
-Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
-\textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).
-Black markers show only sources in the blue selection polygon shown in the CMD (left panel).
-\textbf{Right panel}: Proper motions for all sources in the shown sky region (grey 2D histogram).
-Black markers again show only sources in the blue CMD selection region (left panel).
-}
-\label{fig:cmds}
-\end{figure}
-
 \subsection{Follow-up with \decam}
@@
  \centering
- \includegraphics[width=0.6\textwidth]{figures/DECam-field.pdf}
+ \includegraphics[width=0.45\textwidth]{figures/DECam-field.pdf}
  \caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ $g$-band follow up (blue and red markers).
@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/DECam-cmd.pdf}
+\includegraphics[width=0.45\textwidth]{figures/DECam-cmd.pdf}
 \caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
@@
 \label{sec:pmclean}
+
+% Notebook: Proper-motion-membership
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width=\textwidth]{figures/pm-model.pdf}
+\caption{\textbf{Left panel}: Sky positions of all \gaia\ sources in this region with $\bprp < 0.35$ (grey markers).
+The circles show the regions used as cluster and control fields in the proper motion inference (\sectionname~\ref{sec:pmclean}).
+The control fields, together, have the same area as the cluster field.
+\textbf{Right panel}: The colored 2D density shows the difference in number of sources per pixel in the cluster field versus the two control fields (see left panel).
+The clear over-density in the cluster field (blue) are stars in \clustername.}
+\label{fig:pm-members}
+\end{figure*}
 
@@
 The proper-motion dispersion is consistent with zero, so is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.
-
-% Notebook: Proper-motion-membership
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/pm-model.pdf}
-\caption{\textbf{Left panel}: Sky positions of all \gaia\ sources in this region with $\bprp < 0.35$ (grey markers).
-The circles show the regions used as cluster and control fields in the proper motion inference (\sectionname~\ref{sec:pmclean}).
-The control fields, together, have the same area as the cluster field.
-\textbf{Right panel}: The colored 2D density shows the difference in number of sources per pixel in the cluster field versus the two control fields (see left panel).
-The clear over-density in the cluster field (blue) are stars in \clustername.}
-\label{fig:pm-members}
-\end{figure}
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{figures/hierarch-corner.pdf}
+\includegraphics[width=0.48\textwidth]{figures/hierarch-corner.pdf}
 \caption{A corner plot showing marginal posterior probability distributions estimated from the the posterior samples generated from the hierarchical inference of the cluster population parameters.}
@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/hierarch-results.pdf}
+\includegraphics[width=0.48\textwidth]{figures/hierarch-results.pdf}
 \caption{The \decam\ color-magnitude diagram for sources with probabilty $>0.5$ of belonging to \clustername\ (markers).

### 2018-11-04 ms.tex
refs

@@
 % Recent star formation associated with the Leading Arm of the Magellanic stream}
-\title{\textbf{Discovery of a disrupting open cluster in the Galactic halo:\\
+\title{\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\
        a recent star formation event in the leading arm of the Magellanic stream}}
@@
 The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.
-The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.} is the identified comoving association of blue stars.
+The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$ is the identified comoving association of blue stars.\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.}
 Note that \figurename~\ref{fig:pm-members} is only meant an illustration: The cluster proper motion is determined probabilistically by taking into account the full \gaia\ covariance matrices for each source, as described below.
 
-To measure the mean cluster proper motion, $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, we first construct a model for the error-deconvolved proper motion distribution in the control fields using ``extreme deconvolution'' \citep[XD;][]{Bovy:2011} with two Gaussian components, which takes into account the full error distributions for each proper motion measurement (i.e.
-including covariances), $\mat{C}_\mu$, provided by \gaia\ \DR{2}.
+To measure the cluster (mean) proper motion, we first construct a model for the error-deconvolved proper motion distribution in the control fields using ``extreme deconvolution'' \citep[XD;][]{Bovy:2011} with two Gaussian components.
+XD takes into account the full error distributions for each proper motion measurement $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, including covariances $\mat{C}_\mu$, provided by \gaia\ \DR{2}.
 After running XD, we fix the parameters of the background model and model the proper motion distribution in the cluster region using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{x}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
@@
 \end{align}
-where $\norm(\bs{y} \given \bs{x}, \mat{C})$ represents the multidimensional normal distribution with mean $\bs{x}$ and covariance matrix $\mat{C}$, and $\mathbb{I}$ is the identity matrix.
+where $\norm(\cdot \given \bs{y}, \mat{C})$ represents the multidimensional normal distribution with mean $\bs{y}$ and covariance matrix $\mat{C}$, and $\mathbb{I}$ is the identity matrix.
 Because all distributions are Gaussian, the per-star parameters (the true proper motions, \truepm) can be analytically marginalized out so that the per-star likelihood can be expressed as $p(\bs{\mu} \given f, \bs{x}, s, \mat{C}_\mu)$.
@@
 \begin{align}
-    p(\{\bs{\mu}_n\}_N \given \given f, \bs{x}, s, \{\mat{C}_{\mu, n}\}_N) &=
+    p(\{\bs{\mu}_n\}_N \given f, \bs{x}, s, \{\mat{C}_{\mu, n}\}_N) &=
         \prod_n^N p(\bs{\mu}_n \given f, \bs{x}, s, \mat{C}_{\mu, n}) \quad .
@@
 
-We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{Goodman:2010, emcee} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
+We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{emcee, Goodman:2010} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
 We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
 We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
-For the young cluster, we find $\bs{m} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
-The proper-motion dispersion is consistent with zero, so is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.
+For the young cluster, we find $\bs{x} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
+The proper-motion dispersion is consistent with zero, and is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.
 
@@
 
-The deeper photometry from \decam\ provides a clear view of the stellar population of \clustername\ down to stellar masses $M \sim 0.9~\msun$:
-\figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (single stellar population in right panel).
+While the \gaia\ data provide exquisite astrometric data for the brightest members of \clustername, constraints on the stellar population from the \gaia\ data alone are limited by degeneracies in the mapping from the color-magnitude diagram to stellar parameters.
+To measure the cluster population parameters, we therefore use the deeper photometry from \decam, which provides a clear view of the main sequence of \clustername\ down to stellar masses $M \sim 0.9~\msun$.
+\figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
 We use the $g$- and $i$-band photometry for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
-To summarize our methodology, we generate posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture of a single stellar population and a background population.
-The results of this modeling are presented in \sectionname~\ref{sec:popchars}.
+To summarize our methodology, we first generate independent posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture model of the cluster and a background population.
+If you prefer to skip the details, the results of this modeling are presented in \sectionname~\ref{sec:popchars}.
 
 In detail, we start by using the \texttt{isochrones} package \citep{Morton:2015} to generate posterior samplings over stellar parameters for each individual source given its photometry and an interim prior.
-We use the \acronym{MIST} \citep{Choi:2016} isochrone library, and \texttt{isochrones} automatically performs interpolation between the provided grid of stellar isochrones to evaluate predicted stellar parameters at a given location in the CMD.
-The stellar parameters for each source are its ``equal evolutionary point'' number $\eep$ (see \acronym{MIST} documentation\footnote{\url{http://waps.cfa.harvard.edu/MIST/}}), age $\tau$, metallicity $\feh$, extinction $A_V$, and distance $D$, which can be uniquely mapped to a point in the observed CMD;
+We use the \acronym{MIST} \citep{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015} isochrone grid, and \texttt{isochrones} automatically performs interpolation between the provided grid of stellar isochrones to predict photometry given a set of stellar parameters.
+Here, the stellar parameters for each source are its ``equal evolutionary point'' number $\eep$ (see \acronym{MIST} documentation\footnote{\url{http://waps.cfa.harvard.edu/MIST/}}), age $\tau$, metallicity $\feh$, extinction $A_V$, and distance $D$, which can be uniquely mapped to a point in the observed CMD;
 The likelihood of a given set of these parameters, $\bs{\theta} = (\eep, \tau, \feh, A_V, D)$, is then computed from the photometry and (assumed Gaussian) photometric uncertainties given the predicted photometry.
@@
 
-As expected, we find that the photometry for individual sources in the lower main sequence are very poorly constrained in all parameters, and the prior tends to pull the posterior samplings to prefer closer, older stellar parameters.
-This is a weakness of our methodology for performing the hierarchical inference: each source is considered independently, even though there is clear structure in the CMD (i.e.
-\figurename~\ref{fig:decam-cmd}).
-A more correct way to do this would be to infer the stellar parameters of \emph{all} stars, the cluster hyperparameters, and the background simultaneously.
-However, for the \Nisofit\ stars we are using (in the red box in \figurename~\ref{fig:decam-cmd}), this model would have $\sim$2,000 free parameters, if left unmarginalized.
-We are developing tools to perform star cluster parameter inference in this way (Morton et al., in prep.), but here we adopt a simple hack to allow us to instead perform individual posterior samplings and then combine into a hierarchical inference.
-
-The brightest stars in the cluster have very precise \decam\ photometry, and have precise astrometry from \gaia, and therefore have membership probabilities from the previous section (\sectionname~\ref{sec:pmclean}).
-Given their location in the CMD, these stars must be young, and so also have much better constrained stellar parameters.
-We therefore use the brightest, high-probability \emph{kinematic} member --- XXX --- as an ``anchor'' star:
-We model every other source (i.e.
-excluding XXX) in the \decam\ selection region by fitting the photometry of it and the anchor star simultaneously, assuming they have the same age, metallicity, distance, and extinction but different \eep\ values.
-Motivated by the possible signature of an (unresolved) binary sequence in the \decam\ CMD, we add one further piece of complexity to the model by allowing the photometry of each non-anchor source to be fit as an unresolved binary star system.
-This adds an additional parameter, the unresolved binary mass ratio $q$, to the list of inferred stellar parameters for each source.
-The details of this model are handled by the \texttt{isochrones} package.
-
-\begin{table}[ht]
+\begin{table}[ht!]
 \begin{center}
@@
 
-Ultimately we generate posterior samplings over the parameters $(\bs{\theta}, q)$ for each of the \Nisofit\ sources in the selected region of the \decam\ CMD using \texttt{PyMultinest} \citep{TODO}, and store the value of the prior evaluated at the location of each sample.
+We find that the photometry for individual sources in the lower main sequence are very poorly constrained in all parameters, and the prior tends to pull the posterior samplings to prefer closer, older stellar parameters.
+This is a weakness of our methodology for performing the hierarchical inference: Each source is considered independently, even though there is clear structure in the CMD (i.e.
+\figurename~\ref{fig:decam-cmd}), and inferring isochronal parameters for individual lower main sequence stars is a fundamentally degenerate problem.
+A more correct way to do this would be to infer the stellar parameters of \emph{all} stars, the cluster hyperparameters, and the background simultaneously.
+However, for the \Nisofit\ stars we are using (in the red box in \figurename~\ref{fig:decam-cmd}), this model would have $\sim$2,000 free parameters if left unmarginalized.
+We are developing tools to perform star cluster parameter inference in this way (Morton et al., in prep.), but here we adopt a simple hack to allow us to instead perform individual posterior samplings and then combine those samplings into a hierarchical inference.
+
+The brightest stars in the cluster have very precise \decam\ photometry, and have precise astrometry from \gaia.
+Given their location in the CMD, these stars must be young, and so also have much better constrained stellar parameters.
+We therefore use the brightest \emph{kinematic} member of \clustername\ as an ``anchor'' star:
+We model every other source in the \decam\ selection region (i.e.
+excluding this one) by fitting the photometry of it and the anchor star simultaneously, assuming they have the same age, metallicity, distance, and extinction but different \eep\ values.
+Motivated by the possible signature of an (unresolved) binary sequence in the \decam\ CMD, we add one further piece of complexity to the model by allowing the photometry of each non-anchor source to be fit as an unresolved binary star system.
+This adds an additional parameter, the unresolved binary mass ratio $q$, to the list of inferred stellar parameters for each source, but, for this work, we ignore the binary companions and implicitly marginalize over $q$ in what follows.
+The details of this model are handled by the \texttt{isochrones} package.
+
+We generate posterior samplings over the parameters $(\bs{\theta}, q)$ for each of the \Nisofit\ sources in the selected region of the \decam\ CMD using \texttt{PyMultinest} \citep{Buchner:2014, Feroz:2008, Feroz:2009}, and store the value of the prior evaluated at the location of each sample.
 We then use these samples and interim prior values to construct our hierarchical model, as described below.
+
 In the hierarchical model, we assume that the stellar parameters of each primary star in the selected region are either drawn from the cluster, or a background (stellar halo) population.
-For the cluster, we assume the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\bs{\alpha} = (\tau^*, \feh^*, D^*, A_V^*)$ as hyperparameters of the hierarchical inference.
+For the cluster, we assume that the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\bs{\alpha} = (\tau^*, \feh^*, D^*, A_V^*)$ as hyperparameters of the hierarchical inference.
 For the background model, we assume the same priors as specified in \tablename~\ref{tbl:priors}.
-The one additional parameter that must be included in this hierarchical model is the ``mixture weight'': the global fraction of sources that are likely cluster members, $f$.
-To compute the likelihood of the hierarchical model, we use the individual posterior samplings to marginalize over the per-source $k$ stellar parameters $\bs{\theta}_k$ to compute the marginal likelihood $p(\bs{m}_k \given \bs{\alpha}, f)$, where $\bs{m}_k = (g, i)_k$ is the vector of photometric data;
-This likelihood for a single source $k$ given a set of hyperparameters $(\bs{\alpha}, f)$ is
+The one additional parameter that must be included in this hierarchical model is the mixture weight: The global fraction of sources that are likely cluster members, $f$.
+To compute the likelihood for the hierarchical model, we use the individual posterior samplings to marginalize over the per-source stellar parameters $\bs{\theta}_n$ to compute the marginal likelihood $p(\bs{m}_n \given \bs{\alpha}, f)$, where $\bs{m}_n = (g, i)_n$ is the vector of photometric data for source $n$;
+This likelihood for a single source given a set of hyperparameters $(\bs{\alpha}, f)$ is then
 \begin{equation}
-    p(\bs{m}_k \given \bs{\alpha}, f) = \int \dd \bs{\theta}_k \,
-        p(\bs{m}_k \given \bs{\theta}_k) \,
-        p(\bs{\theta}_k \given \bs{\alpha}, f) \quad .
+    p(\bs{m}_n \given \bs{\alpha}, f) = \int \dd \bs{\theta}_n \,
+        p(\bs{m}_n \given \bs{\theta}_n) \,
+        p(\bs{\theta}_n \given \bs{\alpha}, f) \quad .
 \end{equation}
@@
 \begin{equation}
-    p(\bs{m}_k \given \bs{\alpha}, f) \approx \frac{\mathcal{Z}_k}{J} \,
-        \sum_j^J \frac{p(\bs{\theta}_{kj} \given \bs{\alpha}, f)}{p(\bs{\theta}_{kj} \given \bs{\alpha}_0, f)}
+    p(\bs{m}_n \given \bs{\alpha}, f) \approx \frac{\mathcal{Z}_n}{K} \,
+        \sum_k^K \frac{p(\bs{\theta}_{nk} \given \bs{\alpha}, f)}{p(\bs{\theta}_{nk} \given \bs{\alpha}_0, f)}
         \label{eq:marglike}
 \end{equation}
-where the index $j$ specifies the index of one of $J$ posterior samples generated from the independent samplings (described above), $\mathcal{Z}_k$ is a constant, and the denominator, $p(\bs{\theta}_{kj} \given \bs{\alpha}_0, f)$, are the values of the interim prior used to do the independent samplings.
-In this work, $K=\Nisofit$ and we adopt $J=2048$.
+where the index $k$ specifies the index of one of $K$ posterior samples generated from the independent samplings (described above), $\mathcal{Z}_n$ is a constant, and the denominator, $p(\bs{\theta}_{nk} \given \bs{\alpha}_0, f)$, are the values of the interim prior used to do the independent samplings.
+In this work, $N=\Nisofit$ and we adopt $K=2048$.
 
-\todo{we ignore the $q$!}
-With the marginal likelihood (\equationname~\ref{eq:marglike}), we then need to specify prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, and we can then generate posterior samples for the hyperparameters;
+With the marginal likelihood (\equationname~\ref{eq:marglike}), we then need to specify prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, and we can then generate posterior samples for the hyperparameters.
 We use uniform priors for all of these, as summarized in \tablename~\ref{tbl:hyperpriors}.
-We then use \texttt{emcee} \citep{Goodman:2010, emcee} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
+We use \texttt{emcee} \citep{emcee, Goodman:2010} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
 \begin{equation}
-    p(\bs{\alpha}, f \given \{\bs{m}_k\}) \propto
+    p(\bs{\alpha}, f \given \{\bs{m}_n\}) \propto
         p(\bs{\alpha}) \, p(f) \,
-        \prod_k^K p(\bs{m}_k \given \bs{\alpha}, f) \quad .
+        \prod_n^N p(\bs{m}_n \given \bs{\alpha}, f) \quad .
 \end{equation}
 Here we use 64 walkers and run for an initial 128 steps to burn-in the sampler before running for a final 1024 steps.
-\figurename~\ref{fig:hierarch-corner} shows a corner plot showing all 1D and 2D marginal posterior probability distributions estimated from the samples.
+\figurename~\ref{fig:hierarch-corner} shows a corner plot with all 1D and 2D marginal posterior probability distributions estimated from the samples.
 
@@
 \figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
-Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
-We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx \clage$, distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$.
-Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain a significant number of binary or multiple star systems.
+Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
+We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx \clage$, distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
+Also plotted in \figurename~\ref{fig:hierarch-iso} is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample: The abundance of sources between the nominal isochrone and the binary sequence highlights the fact that the cluster may contain a significant number of binary or multiple star systems, but we leave a detailed study of multiplicity to future work.
 
 We use the isochrone corresponding to the median posterior sample to estimate the total stellar mass of the cluster.
-By assuming that the \decam\ imaging is 100\% complete to stars with $(g-i) < 0.3)$ and $g < 22$, and by assuming a Kroupa initial mass function \citep{Kroupa:TODO}, we use the number of observed stars and the isochrone to compute the total mass, $M_{\rm tot, *} \approx 1200~\msun$.
+By assuming that the \decam\ imaging is 100\% complete to stars with $(g-i) < 0.3)$ and $g < 22$, and by assuming a Kroupa initial mass function \citep{Kroupa:2001}, we use the number of observed stars and the isochrone to compute the total mass, $M_{\rm tot, *} \approx 1200~\msun$.
 
@@
 HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
-Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{TODO} is a metal-rich ($\feh \sim 0.5$) HVC that could have originated from the Galactic disk \citep{TODO}.
-Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk that could have driven gas out into the halo have, at present-day, significantly higher metallicity than this cluster.
+Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{Smith:1963} is a metal-rich \citep[$\feh \sim 0.5$[]{Fox:2016} HVC that plausibly originated from the Galactic disk \citep[e.g.,][]{Bregman:1980}.
+Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk that could have driven gas so far out into the halo have, at present-day, significantly higher metallicity than this cluster.
 
+% TODO: Nidever plots at different velocities?
 Here we take a closer look at the \hi gas in the vicinity of \clustername.
@@
     \package{numpy} \citep{numpy},
+    \package{PyMultinest} \citep{Buchner:2014},
     \package{schwimmbad} \citep{schwimmbad},

### 2018-11-04 ms.tex
more things

@@
 
+If we assume that \clustername\ is associated with nearby \hi in the Magellanic stream, we have measurements of all 6 phase-space components of the cluster and can compute orbits for \clustername.
+However, as discussed in \sectionname~\ref{sec:higas}, there are two prominent but distinct velocity components of \hi along the line of sight to \clustername.
+We therefore integrate orbits of the cluster using both values of the line-of-sight velocity from these two gas components.
+\figurename~\ref{fig:orbits}
+
 \begin{figure}
 \centering
-\includegraphics[width=8cm]{orbits.png}
-\caption{Integrated orbits (over 60 Myr) of the star cluster using the Gaia DR2 proper motions, the
-\hi~velocity and a distance of 25 kpc.  The orbits intersect the MW midplane about
-60 Myr ago which is close to the age of the cluster.}
-\label{fig_gass}
+\includegraphics[width=\textwidth]{orbits.pdf}
+\caption{TODO:}
+\label{fig:orbits}
 \end{figure}

### 2018-11-04 ms.tex
orbits

@@
 \title{\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\
-       a recent star formation event in the leading arm of the Magellanic stream}}
+       a recent star formation event in the leading arm of the Magellanic stream?}}
 
@@
 \centering
-\includegraphics[width=\textwidth]{orbits.pdf}
+\includegraphics[width=0.5\textwidth]{figures/orbits.pdf}
 \caption{TODO:}

### 2018-11-05 ms.tex
fig
Update on Overleaf.

@@
 We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on a portion of the cluster discovered using the \gaia\ data (see previous section).
-\todo{Nidever: can you describe the observations? Exposure times, dither, whatever is usually done...}
-
-The photometry was reduced...\todo{Nidever: describe your pipeline?}
+Observations were obtained with the Dark Energy Camera (DECam) on the CTIO 4m Blanco telescope on UT 2018 May 20 with 3$\times$300s
+exposures in $u-$, $g-$, and $i$-band.
+The NOAO Community Pipeline (CP; \citealt{Valdes:2014}; Valdes et al., in preparation) InstCal images, which have the instrumental signature removed, were downloaded from the NOAO Archive\footnote{\url{http://archive.noao.edu}} for further processing.
+Forced PSF photometry was performed with the PHOTRED pipeline \citep{Nidever:2017} which uses the DAOPHOT ALLSTAR \citep{Stetson:1987} and ALLFRAME \citep{Stetson:1994} suite of programs.
+The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for
+global zero-point and color-terms in each band.
+%\todo{Nidever: can you describe the observations? Exposure times, dither, whatever is usually done...}
+%The photometry was reduced...\todo{Nidever: describe your pipeline?}
 
@@
 \centering
-\includegraphics[width=0.48\textwidth]{figures/hierarch-results.pdf}
+\includegraphics[width=0.45\textwidth]{figures/hierarch-results.pdf}
 \caption{The \decam\ color-magnitude diagram for sources with probabilty $>0.5$ of belonging to \clustername\ (markers).
@@
 Here we take a closer look at the \hi gas in the vicinity of \clustername.
-\figurename~\ref{fig:XXXX} shows the \hi column density in the region around the leading arm of the Magellanic stream, with the location of \clustername\ marked.
+\figurename~\ref{fig:gass_maps} shows the \hi column density of the catalog of Gaussian centers \citep[producted with the techniques and software from][]{Nidever:2008} from the Galactic All Sky Survey \citep[GASS;][]{McClure-Griffiths:2009,Kalberla:2010} in the region around the Leading Arm of the Magellanic stream, with the location of \clustername\ marked.
 While no bulk metallicity measurements exist for the LA gas, \todo{...recent measurements suggest comparable to SMC?} \citep{Fox:2018}.
 Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.
-Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, MoniBidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
+Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
 
@@
 \centering
-\includegraphics[width=8cm]{gass_vlsrmlon.pdf}
-\caption{GASS position-velocity diagram.}
-\label{fig_gass}
+\includegraphics[width=8cm]{figures/gass_vlsrmlon.pdf}
+\caption{The position-velocity diagram of GASS Gaussian centers.}
+\label{fig:gasspv}
 \end{figure}
@@
 \centering
-\includegraphics[width=8cm]{gass_mlatmlon.pdf}
-\caption{GASS \hi column density in the region of LA II. The red cross marks the position
-of the young cluster.}
-\label{fig_gass}
+%\includegraphics[width=8cm]{gass_mlatmlon.pdf}
+\includegraphics[width=8cm]{figures/gass_maps_v2.pdf}
+\caption{GASS \hi column density in the region of LA II at three different velocities.
+The red circle marks the position of the young cluster.}
+\label{fig:gass_maps}
 \end{figure}
@@
 
+D.L.N thanks Peter Kalberla for making the GASS datacubes available in Magellanic Stream coordinates.
+
 This work has made use of data from the European Space Agency (ESA)

### 2018-11-05 ms.tex
small things

@@
 
-We report the discovery of a young $\tau \sim \clage$, low-mass $M \sim 1200~\msun$, metal-poor $[\textrm{Fe}/\textrm{H}] \sim \clfeh$ stellar association in the Milky Way halo, \clustername.
+We report the discovery of a young $\tau \sim \clage$, low-mass $M \sim 1200~\msun$, metal-poor $[\textrm{Fe}/\textrm{H}] \sim \clfeh$ stellar association in the Milky Way halo: \clustername.
 At a Galactocentric (cylindrical) position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
@@
 
-% The halo of the Milky Way is characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
-% This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the formation of the Galaxy: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
-% These systems likely came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
-% The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC, SMC), and about 50 dwarf satellites within the virial radius of the Galaxy.
-% While Sagittarius was likely stripped of its neutral gas long ago through repeated passage about the Milky Way \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
+The halo of the Milky Way is characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
+This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the formation of the Galaxy: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
+These systems likely came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
+The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC, SMC), and about 50 dwarf satellites within the virial radius of the Galaxy.
+While Sagittarius was likely stripped of its neutral gas long ago through repeated passage about the Milky Way \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
+Here, we report the first discovery of a young cluster of co-moving stars in the Milky Way halo that suggests that young stars can form and exist in this otherwise quenched and aging structural component of the Galaxy.
 
@@
 
+\section{Data} \label{sec:data}
+
 % Notebook: Figure-CMDs
-\begin{figure*}[htb!]
+\begin{figure*}[ht!]
 \centering
@@
 \end{figure*}
-
-\section{Data} \label{sec:data}
 
@@
 
-\subsection{The stellar population and physical characteristics of \clustername}
+\subsection{Stellar population and physical characteristics}
 \label{sec:popchars}
@@
 HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
-Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{Smith:1963} is a metal-rich \citep[$\feh \sim 0.5$[]{Fox:2016} HVC that plausibly originated from the Galactic disk \citep[e.g.,][]{Bregman:1980}.
+Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{Smith:1963} is a metal-rich \citep[$\feh \sim 0.5$][]{Fox:2016} HVC that plausibly originated from the Galactic disk \citep[e.g.,][]{Bregman:1980}.
 Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk that could have driven gas so far out into the halo have, at present-day, significantly higher metallicity than this cluster.

### 2018-11-06 ms.tex
reorder

@@
 HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
-Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{Smith:1963} is a metal-rich \citep[$\feh \sim 0.5$][]{Fox:2016} HVC that plausibly originated from the Galactic disk \citep[e.g.,][]{Bregman:1980}.
+Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the mysterious Smith Cloud \citep{Smith:1963} is a metal-rich \citep[$\feh \sim 0.5$][]{Fox:2016} HVC that plausibly originated from the Galactic disk \citep[e.g.,][]{Bregman:1980}.
 Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk that could have driven gas so far out into the halo have, at present-day, significantly higher metallicity than this cluster.
 
-% TODO: Nidever plots at different velocities?
-Here we take a closer look at the \hi gas in the vicinity of \clustername.
-\figurename~\ref{fig:gass_maps} shows the \hi column density of the catalog of Gaussian centers \citep[producted with the techniques and software from][]{Nidever:2008} from the Galactic All Sky Survey \citep[GASS;][]{McClure-Griffiths:2009,Kalberla:2010} in the region around the Leading Arm of the Magellanic stream, with the location of \clustername\ marked.
-While no bulk metallicity measurements exist for the LA gas, \todo{...recent measurements suggest comparable to SMC?} \citep{Fox:2018}.
+Here we take a closer look at the \hi gas in the vicinity of \clustername\ to assess its possible relation to the Magellanic stream.
+\figurename~\ref{fig:gass_maps} shows the \hi column density of the catalog of Gaussian centers \citep[producted with the techniques and software from][]{Nidever:2008} from the Galactic All Sky Survey \citep[GASS;][]{McClure-Griffiths:2009, Kalberla:2010} in the region around the Leading Arm of the Magellanic stream and plotted in the Magellanic stream coordinate system ($L_{\rm MS}, B_{\rm MS}$).
+The location of \clustername\ marked (red circle), and the three panels show three different velocity slices (indicated on each panel).
+The Magellanic stream gas is most visible and densest at the highest velocities where the LA II feature is found, around $L_{\rm MS} \lesssim 61^\circ$ and $B_{\rm MS} \sim -12^\circ$, but the lower panels (i.e.
+slower gas) still displays some of the same morphology as LA II.
+Some relatively low density gas remains in the vicinity of \clustername\ in all panels, but is most abundant in the lower velocity slices (middle and bottom panels of \figurename~\ref{fig:gass_maps}).
+
+However, if the cluster did form from the Magellanic stream gas, and the gas interacted with the Milky Way disk, the dynamics of the stars and the gas could have decoupled as soon as the stars formed.
+Given the geometry of the current location of \clustername, in this scenario we would expect a moderate velocity difference to primarily appear in terms of a difference in the tangential velocities of the stars and the gas (which is not measured).
+We therefore take a closer look at the velocity of the gas in the region around $B_{\rm MS} \sim -13^\circ$ to estimate the line of sight velocity of the stars: \figurename~\ref{fig:gasspv} shows the same GASS data but now shown in a position-velocity diagram.
+The longitude of \clustername\ is marked as the vertical (red) line.
+The LA II feature is again visible as the $V_{\textrm{LSR}} > 200~\kms$ filament of gas at $L_{\rm MS} \lesssim 60^\circ$ (and a faint extension near $L_{\rm MS} \sim 65^\circ$), but two other prominent filaments are prominent at lower velocities $V_{\textrm{LSR}} \sim 60~\kms$ and $V_{\textrm{LSR}} \sim 100~\kms$ from $L_{\rm MS} \lesssim 65^\circ$.
+Therefore, ignoring the disk gas (around $V_{\textrm{LSR}}=-20$--$20~\kms$), it seems that there are three qualitatively different velocities that the gas (and plausibly \clustername) could have: $V_{\textrm{LSR}} \approx (60, 110, 230)~\kms$.
+The origin of these other filaments is not known:
+Did the low velocity filaments originate in the Magellanic stream, but were decelerated through interactions with Milky Way gas?
+\todo{Is that right?
+I don't see much discussion of these features in other papers}.
+The ....
+
+While no bulk metallicity measurements exist for the LA gas, recent measurements of oxygen and silicon abundances suggest that the gas is comparable to the SMC \citep{Fox:2018}.
+...
+
 Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.
@@
 \centering
-\includegraphics[width=8cm]{figures/gass_vlsrmlon.pdf}
-\caption{The position-velocity diagram of GASS Gaussian centers.}
-\label{fig:gasspv}
-\end{figure}
-
-\begin{figure}
-\centering
 %\includegraphics[width=8cm]{gass_mlatmlon.pdf}
@@
 \label{fig:gass_maps}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{figures/gass_vlsrmlon.pdf}
+\caption{The position-velocity diagram of GASS Gaussian centers.}
+\label{fig:gasspv}
 \end{figure}

### 2018-11-06 ms.tex
results

--- 2018-11-05 ms.tex
@@
 % - Split cluster into 2? Price-Whelan 1a and 1b?
+% - discuss Blanco 1: high latitude, similar age, high binary fraction
+% - Make a PGM for this model?
 
@@
 
-\begin{table}[ht!]
+\begin{table}[htb]
 \begin{center}
@@
     \end{tabular}
-\caption{Prior probability distributions for each of the stellar parameters defined in \sectionname~\ref{sec:popmodel}.
+\caption{Prior probability distributions for each of the stellar parameters defined in \sectionname~\ref{sec:popmodel}, used for the independent (per star) posterior samplings.
 \label{tbl:priors}}
@@
 
-\begin{table}[ht]
+\begin{table}[hbt]
 \begin{center}
@@
     \end{tabular}
-\caption{Prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$.
+\caption{Prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, used for the hierarchical inference of the cluster stellar population parameters.
 \label{tbl:hyperpriors}}
@@
 \end{table}
-
-% TODO: Make a PGM for this model?
 
@@
 \label{sec:popchars}
+
+% Notebook: Figure-hierarch-results
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/hierarch-results.pdf}
+\caption{The \decam\ color-magnitude diagram for sources with probabilty $>0.5$ of belonging to \clustername\ (markers).
+The solid line (blue) shows the \acronym{MIST} isochrone for the median posterior sample from the hierarchical inference of the cluster population parameters, shifted to the inferred distance to \clustername, and extincted with the inferred extinction.
+The dashed line (green) shows the same isochrone, shifted $\approx 0.75$ magnitudes brighter, representing the expected location of the equal-mass binary sequence of the cluster.
+}
+\label{fig:hierarch-iso}
+\end{figure}
 
@@
 
-% Notebook: Figure-hierarch-results
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{figures/hierarch-results.pdf}
-\caption{The \decam\ color-magnitude diagram for sources with probabilty $>0.5$ of belonging to \clustername\ (markers).
-The solid line (blue) shows the \acronym{MIST} isochrone for the median posterior sample from the hierarchical inference of the cluster population parameters, shifted to the inferred distance to \clustername, and extincted with the inferred extinction.
-The dashed line (green) shows the same isochrone, shifted $\approx 0.75$ magnitudes brighter, representing the expected location of the equal-mass binary sequence of the cluster.
-}
-\label{fig:hierarch-iso}
-\end{figure}
-
-\begin{table}[ht]
+\begin{table}[htb]
 \begin{center}
@@
         $\tau$ & $130~\textrm{Myr}$ & age \\
-        $M$ & $1200~\msun$ & total mass \\
+        $M$ & $1200~\msun$ & total stellar mass \\
         $\feh$ & $-1.1$ & metallicity \\
@@
     \end{tabular}
-\caption{Inferred parameters for \clustername.
+\caption{Inferred properties of \clustername.
 \label{tbl:clusterparams}}
@@
 
-At the sky location and distance of \clustername, i.e.
-well into the Galactic halo, the only plausible gas reservoirs that could have formed a young cluster are the Magellanic stream, or a previously unknown high velocity cloud (HVC).
-HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
-Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{Smith:1963} is a metal-rich \citep[$\feh \sim 0.5$][]{Fox:2016} HVC that plausibly originated from the Galactic disk \citep[e.g.,][]{Bregman:1980}.
-Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk that could have driven gas so far out into the halo have, at present-day, significantly higher metallicity than this cluster.
+\begin{figure}[t]
+\centering
+%\includegraphics[width=8cm]{gass_mlatmlon.pdf}
+\includegraphics[width=8cm]{figures/gass_maps_v2.pdf}
+\caption{GASS \hi column density in the region of LA II, shown in three different velocity slices (corresponding to and indicated in each panel).
+The coordinate system is the Magellanic stream spherical coordinate system defined in \cite{Nidever:2008}, and the units of $L_{\rm MS}$ and $B_{\rm MS}$ are degrees.
+The colorbar shows the column density of \hi in units of \todo{WHAT UNITS?}.
+The red circle marks the position of \clustername.}
+\label{fig:gass_maps}
+\end{figure}
 
-% TODO: Nidever plots at different velocities?
-Here we take a closer look at the \hi gas in the vicinity of \clustername.
-\figurename~\ref{fig:gass_maps} shows the \hi column density of the catalog of Gaussian centers \citep[producted with the techniques and software from][]{Nidever:2008} from the Galactic All Sky Survey \citep[GASS;][]{McClure-Griffiths:2009,Kalberla:2010} in the region around the Leading Arm of the Magellanic stream, with the location of \clustername\ marked.
-While no bulk metallicity measurements exist for the LA gas, \todo{...recent measurements suggest comparable to SMC?} \citep{Fox:2018}.
-Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.
-Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
-
-\todo{which gas feature? discuss longitude vs. vlsr}
-
-% We evaluate the hypothesis that the cluster formed in the Leading Arm.
-The mean proper motion values in the Magellanic stream coordinate system \citep{Nidever:2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.
-The simulations of \citet{Besla:2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.
-The Magellanic stream simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the effects of ram pressure from the hot MW halo which could cause the gas to drop in its orbit to smaller Galactocentric distances (NEED TO DOUBLE-CHECK THIS).
-In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the position of the position of the cluster with a velocity of \vlsr=70 \kmse.
-
-\todo{Radial velocity follow-up is needed for internal motion, and check association with gas}
-
-\begin{figure}
+\begin{figure}[t]
 \centering
@@
 
-\begin{figure}
-\centering
-%\includegraphics[width=8cm]{gass_mlatmlon.pdf}
-\includegraphics[width=8cm]{figures/gass_maps_v2.pdf}
-\caption{GASS \hi column density in the region of LA II at three different velocities.
-The red circle marks the position of the young cluster.}
-\label{fig:gass_maps}
-\end{figure}
+At the sky location and distance of \clustername, i.e.
+well into the Galactic halo, the only plausible gas reservoirs that could have formed a young cluster are the Magellanic stream, or a previously unknown high velocity cloud (HVC).
+HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
+Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the mysterious Smith Cloud \citep{Smith:1963} is a metal-rich \citep[$\feh \sim 0.5$][]{Fox:2016} HVC that plausibly originated from the Galactic disk \citep[e.g.,][]{Bregman:1980}.
+Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk that could have driven gas so far out into the halo have, at present-day, significantly higher metallicity than this cluster.
+
+We therefore take a closer look at the \hi gas in the vicinity of \clustername\ to assess its possible relation to the Magellanic stream.
+While no bulk metallicity measurements exist for the Magellanic stream Leading Arm gas, recent measurements of oxygen and silicon abundances suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2018, Richter:2018}.
+If \clustername\ formed from this gas, we would then expect that the stellar metallicity should be similar to young stars in the SMC.
+In the outskirts of the SMC, the metallicity distribution of the youngest stars ($\textrm{age} < 2~\textrm{Gyr}$) has a peak around $\feh \sim -1$ and a spread of $\sigma_{\feh} \sim 0.2~\textrm{dex}$, which at least means that the metallicity of \clustername\ ($\feh \approx -1.1$) is consistent with young SMC stars \citep{Dobbie:2014}.
+
+We next look at the kinematics of high velocity gas in this region.
+\figurename~\ref{fig:gass_maps} shows the \hi column density of the catalog of Gaussian centers \citep[producted with the techniques and software from][]{Nidever:2008} from the Galactic All Sky Survey \citep[GASS;][]{McClure-Griffiths:2009, Kalberla:2010} in the region around the Leading Arm of the Magellanic stream and plotted in the Magellanic stream coordinate system \citep[$L_{\rm MS}, B_{\rm MS}$;][]{Nidever:2008}.
+The location of \clustername\ is marked (red circle), and the three panels show three different velocity slices (indicated on each panel).
+The Magellanic stream gas is most visible and densest at the highest velocities where the LA II feature is found, around $L_{\rm MS} \lesssim 61^\circ$ and $B_{\rm MS} \sim -12^\circ$, but the lower panels (i.e.
+slower gas) still displays some of the same morphology as the highest velocity slice.
+
+This is also apparent in a position-velocity diagram of the same range of longitudes:
+\figurename~\ref{fig:gasspv} shows the velocity of gas in this region (all longitudes, but near $B_{\rm MS} \sim -13^\circ$) as a function of $L_{\rm MS}$.
+Here, the longitude of \clustername\ is marked as the vertical (red) line.
+The LA II feature is again visible as the $V_{\textrm{LSR}} > 200~\kms$ filament of gas at $L_{\rm MS} \lesssim 60^\circ$ (and a faint extension near $L_{\rm MS} \sim 65^\circ$), but two other prominent filaments with similar morphologies are apparent at lower velocities $V_{\textrm{LSR}} \sim 60~\kms$ and $V_{\textrm{LSR}} \sim 100~\kms$ from $L_{\rm MS} \lesssim 65^\circ$.
+
+The entire region shown in \figurename~\ref{fig:gass_maps} is on the other side of the Galactic disk with respect to the Magellanic clouds, meaning that all of the gas in this region has passed through the Galactic midplane.
+The similar filamentary structure in the high and lower velocity gas therefore raises the question: Did the low velocity filaments originate in the Magellanic stream, but were decelerated through interactions with Milky Way gas?
+\todo{Is this an accepted explanation?
+I don't see much discussion of these features in other papers}
+This presents a possible formation scenario for \clustername.
+If the cluster formed from the Magellanic stream gas, and some of the gas interacted with the Milky Way disk, the dynamics of the stars and the gas that interacted would have decoupled as soon as the stars formed.
+Given the geometry of the current location of \clustername\ (i.e.
+our viewing angle from the solar position), in this scenario we would expect a moderate velocity difference between the gas that interacted and stars to primarily appear as a difference in the tangential velocities of the stars and the gas (which is not measured).
+We can therefore use the line-of-sight velocity of the gas as a proxy for the line-of-sight velocity of the stars in \clustername\ to study the Galactic orbit of the cluster, as discussed in the next section.
 
@@
 
-\todo{Assume velocity, get orbit. Lower energy than LMC, but expected if dissipated during star formation? How much orbital energy lost? Give orbital parameters at midplane.}
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width=0.9\textwidth]{figures/orbits.pdf}
+\caption{The past orbit of \clustername in Galactocentric Cartesian coordinates, computed by assuming a line-of-sight velocity equal to each of three different possible gas  filaments in the LA II region of the Magellanic stream (as indicated in right panel).
+In these coordinates, the Sun is at $(x, y, z) = (-8.1, 0, 0)~\kpc$, and the present-day locations of \clustername\ (filled black marker) and the LMC (open black marker) are indicated.
+The time at each point in the orbits is indicated by the colorbar, with the darkest regions corresponding to $t = -130~\textrm{Myr}$, the inferred age of \clustername.
+The past and future orbit of the LMC are shown as the colored line and dashed line, respectively.
+}
+\label{fig:orbits}
+\end{figure*}
 
-If we assume that \clustername\ is associated with nearby \hi in the Magellanic stream, we have measurements of all 6 phase-space components of the cluster and can compute orbits for \clustername.
-However, as discussed in \sectionname~\ref{sec:higas}, there are two prominent but distinct velocity components of \hi along the line of sight to \clustername.
-We therefore integrate orbits of the cluster using both values of the line-of-sight velocity from these two gas components.
-\figurename~\ref{fig:orbits}
+Ignoring the disk gas (between $V_{\textrm{LSR}} \sim -20$--$20~\kms$ in \figurename~\ref{fig:gasspv}), it seems that there are three qualitatively different line-of-sight velocities that the gas (and plausibly \clustername) could have: $V_{\textrm{LSR}} \approx (60, 110, 230)~\kms$.
+If we adopt these velocity measurements as the line-of-sight (LOS) velocity of \clustername, we have measurements of all 6 phase-space components and can compute orbits for the cluster.
+We compute Galactic orbits of the cluster using each of the three values of the line-of-sight velocity from the LA II region filaments.
+\figurename~\ref{fig:orbits} shows these three orbits computed by integrating the position of \clustername\ backwards in time:
+The two panels of \figurename~\ref{fig:orbits} show the Galactocentric Cartesian trajectories of \clustername\ over the last $260~\textrm{Myr}$ by assuming each of the three plausible line-of-sight velocities discussed above (as labeled in the right panel).
+Also shown is the present-day location of the LMC (open black circle), the present-day location of \clustername\ (filled black circle), the past orbit of the LMC over the same period, and the projected future orbit of the LMC (dashed line).
+For the two lower LOS velocity cases, the orbit of \clustername\ crosses the midplane of the Galactic disk at a time comparable to the age of the cluster (i.e.
+when the color is darkest, corresponding to a time $\approx -130~\textrm{Myr}$).
 
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{figures/orbits.pdf}
-\caption{TODO:}
-\label{fig:orbits}
-\end{figure}
+However, note that while the orbits of \clustername\ and the LMC are generally in the same orbital plane and have the same sense about the Galaxy, none of the orbits closely approach or cross the orbit of the LMC.
+This is expected if the gas shocked or otherwise lost kinetic energy through, e.g., ram pressure --- as is expected to explain the morphology of the LA material \citep[e.g.,][]{Hammer:2015} --- during or before the star formation event that produced \clustername.
 
-% \section{Discussion} \label{sec:discussion}
-%
-% - Streams or clusters in the halo from star-formation from Sgr or dwarf gas
-%
-% - Sgr young globular clusters: same thing as this? Indication of when Sgr lost its gas?
-%
-% - Stars have the right metallicity to be SMC gas, I think
-%
-% - TODO: where would interaction point between LMC gas and MW disk gas be today? ~150–200 Myr ago is almost 1 complete disk rotation. see Bekki:2008
+Precise radial velocity measurements of stars in \clustername\ will definitively rule on this scenario.
+For one, with a precision $\sigma_v \lesssim 2~\kms$, the internal kinematics of \clustername\ could be resolved, and in particular the expansion rate could be measured.
+But even low-precision velocity measurements would either confirm the association between \clustername\ and one of the three LA II-region gas filaments, or would challenge this scenario.
 
 \section{Conclusion} \label{sec:conclusion}
+
+Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.
+
+Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
 

### 2018-11-06 ms.tex
oops conclusions

@@
 
-Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.
-
+We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername\ --- with an age $\tau \approx \clage$, heliocentric distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$.
+At its present day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic gas stream and thus it plausibly formed from Magellanic stream gas.
+The age of the cluster is broadly consistent with the time it would have most recently crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
 Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
 
-We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername --- with an age $\tau \approx \clage$, heliocentric distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$.
-At its present day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic gas stream and thus it plausibly formed from Magellanic stream gas.
-The age of the cluster is broadly consistent with the time it would have most recently crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
 The discovery of \clustername\ provides a critical distance constraint to the Magellanic stream and will aid future Magellanic system and Milky Way modeling efforts.

### 2018-11-06 ms.tex
milky way model

@@
 The two panels of \figurename~\ref{fig:orbits} show the Galactocentric Cartesian trajectories of \clustername\ over the last $260~\textrm{Myr}$ by assuming each of the three plausible line-of-sight velocities discussed above (as labeled in the right panel).
-Also shown is the present-day location of the LMC (open black circle), the present-day location of \clustername\ (filled black circle), the past orbit of the LMC over the same period, and the projected future orbit of the LMC (dashed line).
+To compute the orbits, we use a three-component Milky Way mass model consisting of a disk \citep{Miyamoto:1975}, a bulge \citep{Hernquist:1990}, and a spherical dark matter halo \citep{Navarro:1996}.
+The parameters of this model are set to match the circular velocity profile and disk properties of \citet{Bovy:2015}, and is implemented in the \texttt{gala} package \citep{gala} as the \texttt{MilkyWayPotential}.
+We note that we do not include the LMC/SMC as a component of our mass model.
+
+Also shown in \figurename~\ref{fig:orbits} is the present-day location of the LMC (open black circle), the present-day location of \clustername\ (filled black circle), the past orbit of the LMC over the same period, and the projected future orbit of the LMC (dashed line).
 For the two lower LOS velocity cases, the orbit of \clustername\ crosses the midplane of the Galactic disk at a time comparable to the age of the cluster (i.e.

### 2018-11-07 ms.tex
tim comments

@@
 % - Make a PGM for this model?
+% - release data for the candidate members!
+% - You refer to the prior on EEP as "uniform."  While on the surface this is what it looks like in 'isochrones', that is not quite correct (and would be erroneous).
+Rather, the effective prior on EEP p(E) is transformed from a Salpeter-IMF mass prior, where p(E) = p(M) * |dM/dEEP|.
+Not sure the most succinct way to communicate this, but Table 1 is incorrect as is.
+% - I think Figure 6 would benefit from showing the non-cluster members as well, maybe with a low alpha, to demonstrate how the model picks out the sequence like a charm.
 
@@
 
-\newcommand{\articlename}{\textsl{Letter}}
+\newcommand{\articlename}{\textsl{Article}}
 \newcommand{\sectionname}{Section}
@@
              Princeton University, Princeton, NJ 08544, USA}
+\affiliation{Department of Astronomy, University of Florida, 211 Bryant Space Science Center, P.O Box 112055, Gainesville, FL 32611-2055 USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, NY 10010, USA}
 
@@
 
+The DECam results are based on observations at Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory (NOAO Prop.
+ID: 2018A-0251; PI: Finkbeiner), which is operated by the Association of Universities for Research in Astronomy (AURA) under a cooperative agreement with the National Science Foundation.
+
 This work has made use of data from the European Space Agency (ESA)
@@
     \package{IPython} \citep{ipython},
+    \package{isochrones} \citep{Morton:2015},
     \package{matplotlib} \citep{mpl},

### 2018-11-07 ms.tex
units
add non-members

@@
 Not sure the most succinct way to communicate this, but Table 1 is incorrect as is.
-% - I think Figure 6 would benefit from showing the non-cluster members as well, maybe with a low alpha, to demonstrate how the model picks out the sequence like a charm.
 
@@
 \includegraphics[width=0.45\textwidth]{figures/hierarch-results.pdf}
-\caption{The \decam\ color-magnitude diagram for sources with probabilty $>0.5$ of belonging to \clustername\ (markers).
+\caption{The \decam\ color-magnitude diagram for sources with probability $>0.5$ of belonging to \clustername\ (dark, larger markers), and sources with probability $<0.5$ (lighter, smaller markers).
 The solid line (blue) shows the \acronym{MIST} isochrone for the median posterior sample from the hierarchical inference of the cluster population parameters, shifted to the inferred distance to \clustername, and extincted with the inferred extinction.
@@
 %\includegraphics[width=8cm]{gass_mlatmlon.pdf}
-\includegraphics[width=8cm]{figures/gass_maps_v2.pdf}
+\includegraphics[width=8cm]{figures/gass_maps_v3.pdf}
 \caption{GASS \hi column density in the region of LA II, shown in three different velocity slices (corresponding to and indicated in each panel).
 The coordinate system is the Magellanic stream spherical coordinate system defined in \cite{Nidever:2008}, and the units of $L_{\rm MS}$ and $B_{\rm MS}$ are degrees.
-The colorbar shows the column density of \hi in units of \todo{WHAT UNITS?}.
+The colorbar shows the column density of \hi in units of $10^19~\textrm{atoms}~\textrm{cm}^{-2}$.
 The red circle marks the position of \clustername.}

### 2018-11-09 ms.tex
move figure 1 up
Update on Overleaf.
IMF

@@
 % - release data for the candidate members!
-% - You refer to the prior on EEP as "uniform."  While on the surface this is what it looks like in 'isochrones', that is not quite correct (and would be erroneous).
-Rather, the effective prior on EEP p(E) is transformed from a Salpeter-IMF mass prior, where p(E) = p(M) * |dM/dEEP|.
-Not sure the most succinct way to communicate this, but Table 1 is incorrect as is.
 
@@
 % Recent star formation associated with the Leading Arm of the Magellanic stream}
-\title{\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\
+\title{\textbf{Discovery of a disrupting open cluster far into the Milky Way halo:\\
        a recent star formation event in the leading arm of the Magellanic stream?}}
@@
 \affiliation{Department of Astrophysical Sciences,
-             Princeton University, Princeton, NJ 08544, USA}
+             Princeton University,
+             4 Ivy Lane, Princeton, NJ 08544, USA}
 \email{adrn@astro.princeton.edu}
@@
 \author[0000-0003-2808-275X]{Douglas~P.~Finkbeiner}
-\affiliation{Institute for Theory and Computation, Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, MS-51, Cambridge, MA 02138, USA}
+\affiliation{Institute for Theory and Computation, Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
 
-\author[0000-0002-8537-5711]{Timothy~Morton} % TODO: check orcID
+\author[0000-0002-8537-5711]{Timothy~Morton}
 \affiliation{Department of Astrophysical Sciences,
-             Princeton University, Princeton, NJ 08544, USA}
+             Princeton University,
+             4 Ivy Lane, Princeton, NJ 08544, USA}
 \affiliation{Department of Astronomy, University of Florida, 211 Bryant Space Science Center, P.O Box 112055, Gainesville, FL 32611-2055 USA}
@@
 \author[0000-0003-2644-135X]{Sergey E. Koposov}
-\affiliation{McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, 5000 Forbes Avenue, Pittsburgh, PA 15213, USA}
+\affiliation{McWilliams Center for Cosmology, Carnegie Mellon University, 5000 Forbes Avenue, Pittsburgh, PA 15213, USA}
 \affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
@@
 
+% Notebook: Figure-CMDs
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width=\textwidth]{figures/gaia-cmd-pm.pdf}
+\caption{Color-magnitude diagram, sky positions, and proper motions from \gaia\ \DR{2} for the region around $(\alpha, \delta) \sim (179, -29)^\circ$.
+\textbf{Left panel}: \gaia\ color-magnitude diagram (CMD) for all sources with $G < 20$ and sky position within 3 degrees of $(\alpha, \delta) = (179.5, -28.8)^\circ$.
+Red line shows a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone shifted to a distance of $30~\kpc$.
+Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
+\textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).
+Black markers show only sources in the blue selection polygon shown in the CMD (left panel).
+\textbf{Right panel}: Proper motions for all sources in the shown sky region (grey 2D histogram).
+Black markers again show only sources in the blue CMD selection region (left panel).
+}
+\label{fig:cmds}
+\end{figure*}
+
 Streams formed from tidally stripped material --- such as the Sagittarius or Palomar 5 \citep{Odenkirchen:2001} stellar streams, or gas streams such as the MS --- encode information about the orbital history and future trajectory of their progenitor system \citep[e.g.,][]{Johnston:1999}.
@@
 \section{Data} \label{sec:data}
-
-% Notebook: Figure-CMDs
-\begin{figure*}[ht!]
-\centering
-\includegraphics[width=\textwidth]{figures/gaia-cmd-pm.pdf}
-\caption{Color-magnitude diagram, sky positions, and proper motions from \gaia\ \DR{2} for the region around $(\alpha, \delta) \sim (179, -29)^\circ$.
-\textbf{Left panel}: \gaia\ color-magnitude diagram (CMD) for all sources with $G < 20$ and sky position within 3 degrees of $(\alpha, \delta) = (179.5, -28.8)^\circ$.
-Red line shows a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone shifted to a distance of $30~\kpc$.
-Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
-\textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).
-Black markers show only sources in the blue selection polygon shown in the CMD (left panel).
-\textbf{Right panel}: Proper motions for all sources in the shown sky region (grey 2D histogram).
-Black markers again show only sources in the blue CMD selection region (left panel).
-}
-\label{fig:cmds}
-\end{figure*}
 
@@
 The priors for each parameter are summarized in \tablename~\ref{tbl:priors}.
-The bounds on $\eep$ limit the isochrone to evolutionary phases between the zero-age main sequence to the terminal-age main sequence.
+The bounds on $\eep$ limit the isochrone to evolutionary phases between the zero-age main sequence to the terminal-age main sequence, but this prior is actually computed using the stellar mass computed from the isochrone parameters (see caption of \tablename~\ref{tbl:priors}).
 The prior and bounds on $A_V$ are set to prefer small and reasonable values of extinction for this moderately high Galactic latitude region.
@@
         \toprule
-        $\eep$ & uniform & $(202, 355)$ \\
         $\tau$ & uniform & $(10~\textrm{Myr}, 15~\textrm{Gyr})$ \\
         $\feh$ & uniform & $(-2, 0.5)$ \\
+        $\eep$ & (see caption) & $(202, 355)$ \\
         $A_V$ & $\propto A_V^{-1}$ & $(0.001, 1)~\textrm{mag}$ \\
@@
 \caption{Prior probability distributions for each of the stellar parameters defined in \sectionname~\ref{sec:popmodel}, used for the independent (per star) posterior samplings.
+The prior on \eep\ is computed by calculating the stellar mass, $m$, corresponding to a given point in the isochrone parameter space, $(\eep, \tau, \feh)$, and computing the probability from a Salpeter \citep{Salpeter:1955} mass prior such that $p(\eep) = p(m)\,\left|\frac{\dd m}{\dd \eep}\right|$, following the prescription used in \texttt{isochrones} \citep{Morton:2015}.
 \label{tbl:priors}}
@@
 
-The entire region shown in \figurename~\ref{fig:gass_maps} is on the other side of the Galactic disk with respect to the Magellanic clouds, meaning that all of the gas in this region has passed through the Galactic midplane.
+The entire region shown in \figurename~\ref{fig:gass_maps} is on the other side of the Galactic disk with respect to the Magellanic clouds, meaning that all of the Magellanic stream gas in this region has passed through the Galactic midplane.
 The similar filamentary structure in the high and lower velocity gas therefore raises the question: Did the low velocity filaments originate in the Magellanic stream, but were decelerated through interactions with Milky Way gas?
-\todo{Is this an accepted explanation?
-I don't see much discussion of these features in other papers}
 This presents a possible formation scenario for \clustername.
@@
 our viewing angle from the solar position), in this scenario we would expect a moderate velocity difference between the gas that interacted and stars to primarily appear as a difference in the tangential velocities of the stars and the gas (which is not measured).
-We can therefore use the line-of-sight velocity of the gas as a proxy for the line-of-sight velocity of the stars in \clustername\ to study the Galactic orbit of the cluster, as discussed in the next section.
+We can therefore use the line-of-sight velocity of the gas as a proxy for the line-of-sight velocity of the stars in \clustername\ to study the Galactic orbit of the cluster, as discussed in the next section, and because we do not yet have radial velocity information for the stars.
 

### 2018-11-09 ms.tex
tweaks
better caption for fig 8

@@
 We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of this group, with a width of $5^\circ$ and a height of $5^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
-\figurename~\ref{fig:cmds} shows the \gaia\ data for this region.
-The left panel of \figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}: Surprisingly, this appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
+\figurename~\ref{fig:cmds} shows the \gaia\ data for this region:
+The left panel shows the \gaia\ color-magnitude diagram, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}.
+Surprisingly, this group appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
 The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions, respectively, of all stars in this sky region (grey background density), and only stars in the CMD selection polygon as black markers.
@@
 \label{sec:decam}
+
+% Notebook: Figure-DECam-CMD
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/DECam-field.pdf}
+\caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ $g$-band follow up (blue and red markers).
+Red markers show sources in the \decam\ field used as control sources, and blue markers show sources used as cluster member candidates.}
+\label{fig:decam-field}
+\end{figure}
+
+% Notebook: Figure-DECam-CMD
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/DECam-cmd.pdf}
+\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
+Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
+The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
+}
+\label{fig:decam-cmd}
+\end{figure}
 
@@
 
- % Notebook: Figure-DECam-CMD
- \begin{figure}
- \centering
- \includegraphics[width=0.45\textwidth]{figures/DECam-field.pdf}
- \caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ $g$-band follow up (blue and red markers).
- Red markers show sources in the \decam\ field used as control sources, and blue markers show sources used as cluster member candidates.}
- \label{fig:decam-field}
- \end{figure}
-
-% Notebook: Figure-DECam-CMD
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{figures/DECam-cmd.pdf}
-\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
-Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
-The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
-}
-\label{fig:decam-cmd}
-\end{figure}
-
 \section{Methods} \label{sec:methods}
@@
 % Notebook: Proper-motion-membership
-\begin{figure*}[ht!]
+\begin{figure*}[t!]
 \centering
-\includegraphics[width=\textwidth]{figures/pm-model.pdf}
+\includegraphics[width=0.9\textwidth]{figures/pm-model.pdf}
 \caption{\textbf{Left panel}: Sky positions of all \gaia\ sources in this region with $\bprp < 0.35$ (grey markers).
@@
     \begin{tabular}{ r | l | l}
+        \multicolumn{3}{c}{\textbf{Inferred properties of \clustername}} \\
         \toprule
@@
     \end{tabular}
-\caption{Inferred properties of \clustername.
+\caption{This table summarizes the measured or inferred kinematic and stellar population parameters of the young halo stellar cluster \clustername.
 \label{tbl:clusterparams}}
@@
 \includegraphics[width=8cm]{figures/gass_vlsrmlon.pdf}
-\caption{The position-velocity diagram of GASS Gaussian centers.}
+\caption{The position-velocity diagram of GASS \hi Gaussian centers in the same region as \figurename~\ref{fig:gass_maps}, showing the line-of-sight velocity (in the local standard of rest frame) of gas near \clustername.
+Note that the densest gas at the longitude of \clustername\ (vertical line) appears to be associated with the lower velocity filaments seen at lower longitudes $L_{\textrm{MS}} \lesssim 60^\circ$, which may be decelerated gas associated with the Magellanic stream.
+}
 \label{fig:gasspv}
@@
 
+\facility{Blanco (DECam)}
+
 \bibliographystyle{aasjournal}

### 2018-11-09 ms.tex
Update on Overleaf.

@@
 
-We report the discovery of a young $\tau \sim \clage$, low-mass $M \sim 1200~\msun$, metal-poor $[\textrm{Fe}/\textrm{H}] \sim \clfeh$ stellar association in the Milky Way halo: \clustername.
+We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($[\textrm{Fe}/\textrm{H}] \sim \clfeh$) stellar association in the Milky Way halo: \clustername.
 At a Galactocentric (cylindrical) position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
 By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $D \approx \cldist$.
-At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with MW disk.
-The estimated age of \clustername\ is consistent with the time of last passage through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by the last disk midplane passage of the Magellanic stream gas, which occurred at a Galactocentric radius $R \approx 30~\kpc$.
-However, most details of this idea remain a mystery: the Magellanic stream is low column density, the Milky Way disk at this large radius has low surface density, and the relative velocity of the stream gas and MW gas is large.
+At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with Milky Way disk.
+The estimated age of \clustername\ is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by the last disk midplane passage, which occurred at a Galactocentric radius $R \approx 30~\kpc$.
+However, most details of this idea remain a mystery: the Magellanic stream is low column density, the Milky Way disk at this large radius has low gas surface density, and the relative velocity of the leading arm gas and Milky Way gas is large.
 However it formed, the discovery of a young stellar cluster in the Milky Way halo presents an interesting opportunity for study.
@@
 \section{Introduction} \label{sec:intro}
-
+%Yumi: Intro can be condensed and go into the point quickly.
 The halo of the Milky Way is characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
@@
 These systems likely came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
-The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC, SMC), and about 50 dwarf satellites within the virial radius of the Galaxy.
+The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC and SMC), and about 50 dwarf satellites within the virial radius of the Galaxy.
 While Sagittarius was likely stripped of its neutral gas long ago through repeated passage about the Milky Way \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
@@
 
+% Yumi: this paragraph needs to be clear. The MS is the trailing gas and the LA is the leading gas. Both together is 200 degrees long.
 The Magellanic stream (MS) is a large stream of (predominantly) hydrogen gas emanating from the \lmcsmc\ system that contains a significant fraction of the total gas mass associated with the \lmcsmc\ \citep{Bruns:2005} and wraps nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
@@
 Recent chemical abundance measurements along several sightlines passing through the LA again suggested the SMC origin \citep{Fox:2018, Richter:2018}.
-Recent hydrodynamical simulations of the MCs on the first infall to the Milky Way, however, showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas creates filamentary gas structures both in the LA and the Magellanic stream \citep{Pardy:2018}.
-Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the leading arm \citep{Nidever:2008, Besla:2012}.
+Recent hydrodynamical simulations of the MCs on the first infall to the Milky Way, however, showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas creates filamentary gas structures both in the LA and the MS \citep{Pardy:2018}.
+Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the LA \citep{Nidever:2008, Besla:2012}.
 However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions with gas in the outer Milky Way disk may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.

### 2018-11-09 ms.tex
data tables

--- 2018-11-09 ms.tex
@@
-% TODO
-% - Sand, Seth, et al. Virgo: blue stars with nothing else
+% TODO: after submission
 % - Split cluster into 2? Price-Whelan 1a and 1b?
@@
 % - Make a PGM for this model?
-% - release data for the candidate members!
 
@@
 The proper-motion dispersion is consistent with zero, and is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.
+\tablename~\ref{tbl:gaiadata} contains a subset of the \gaia\ \DR{2} data for stars in the cluster field, with kinematic membership probabilities determined from this modeling procedure.
 
@@
 
+\clearpage
+
 \appendix
@@
 
+\section{Data}
+\label{sec:data}
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c | c | c | c | c | c | c | c | c}
+        \multicolumn{9}{c}{\textbf{Catalog of \gaia\ sources and kinematic probability}}\\
+        \texttt{source\_id} & \texttt{ra} & \texttt{dec} & \texttt{pmra} & \texttt{pmdec} & \texttt{G0} & \texttt{BP0} & \texttt{RP0} & \texttt{member\_prob} \\
+        \tableline
+        3462048793708019200 & 184.799 & -34.971 &  0.09 & -1.61 & 19.79 & 19.915 & 19.61 & 0.00 \\
+        3462056696448285440 & 184.511 & -34.988 & -4.24 & -1.32 & 20.80 & 20.498 & 20.31 & 0.09 \\
+        3462062670747949312 & 184.426 & -34.816 & -0.56 & -2.77 & 20.33 & 20.363 & 20.06 & 0.00 \\
+        3462062709402484224 & 184.407 & -34.809 & -7.50 & -3.16 & 20.67 & 20.437 & 20.09 & 0.01 \\
+        3462065904858152832 & 184.705 & -34.783 &  0.91 & -1.95 & 20.64 & 20.625 & 20.37 & 0.12 \\
+        \multicolumn{9}{c}{...}\\
+        \multicolumn{9}{c}{\textit{(5983 rows)}}
+    \end{tabular}
+    \caption{Select \gaia\ \DR{2} data and membership probabilities computed for all stars in the cluster region (see \figurename~\ref{fig:pm-members}).}
+    \label{tbl:gaiadata}
+\end{table}
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{c | c | c | c | c | c | c | c | c | c}
+        \multicolumn{10}{c}{\textbf{Catalog of \decam\ photometry for point sources}}\\
+        \texttt{name} & \texttt{ra} & \texttt{dec} & \texttt{g} & \texttt{g\_err} & \texttt{i} & \texttt{i\_err} & \texttt{control\_mask} & \texttt{cluster\_mask} & \texttt{member\_mask} \\
+        \tableline
+        J115311.06-283133.4 & 178.296 & -28.525 & 24.09 & 0.46 & 23.99 & 0.33 & True & False & False \\
+        J115403.33-283553.8 & 178.513 & -28.598 & 25.27 & 0.29 & 22.70 & 0.04 & True & False & False \\
+        J115424.21-283749.6 & 178.600 & -28.630 & 24.61 & 0.25 & 23.83 & 0.28 & True & False & False \\
+        J115413.93-283343.6 & 178.558 & -28.562 & 25.37 & 0.41 & 22.76 & 0.05 & True & False & False \\
+        J115419.62-283635.8 & 178.581 & -28.609 & 24.20 & 0.13 & 21.89 & 0.02 & True & False & False \\
+        \multicolumn{10}{c}{...}\\
+        \multicolumn{10}{c}{\textit{(51932 rows)}}
+    \end{tabular}
+    \caption{\decam\ photometry and sky positions for point sources in the observed \decam\ field.
+    The boolean columns \texttt{control\_mask} and \texttt{cluster\_mask} are True when a given source is in the control or cluster CCDs, respectively (see \figurename~\ref{fig:decam-field}).
+    The boolean column \texttt{member\_mask} is True when the source has a photometric membership probability $>0.5$ of belonging to the cluster stellar population (see \sectionname~\ref{sec:popmodel}).
+    }
+    \label{tbl:decamdata}
+\end{table}
+
 \software{

### 2018-11-09 ms.tex
Update on Overleaf.

--- 2018-11-09 ms.tex
@@
 \newcommand{\cldist}{\ensuremath{29~\textrm{kpc}}}
+
+% Edits
+\newcommand{\yumi}[1]{{\ \color{purple}{\textbf{Yumi: #1}\ }}}
 
@@
 Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
+\yumi{It seems you made extinction correction on this CMD.
+If so, please describe it in the text.}
 \textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).
@@
 
-We infer the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background populations using astrometric data from \gaia.
+We measure the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background populations using astrometric data from \gaia.
 We start by selecting all stars with $(\bprp)_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
@@
 The larger solid-line circle indicates the region we define as the cluster area, and the two smaller dashed-line circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
-The control fields are designed to, together, have the same total area as the cluster field.
+The control fields are designed to, together, have the same total area as the cluster field. \yumi{Any changes if you pick different control fields?}
 The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.

### 2018-11-10 ms.tex
edit intro

@@
 % Recent star formation associated with the Leading Arm of the Magellanic stream}
-\title{\textbf{Discovery of a disrupting open cluster far into the Milky Way halo:\\
+\title{\textbf{
+Discovery of a disrupting open cluster far into the Milky Way halo:\\
 a recent star formation event in the leading arm of the Magellanic stream?}}
@@
 
-We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($[\textrm{Fe}/\textrm{H}] \sim \clfeh$) stellar association in the Milky Way halo: \clustername.
-At a Galactocentric (cylindrical) position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
+We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association in the Milky Way halo: \clustername.
+At a Galactocentric cylindrical position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
 By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $D \approx \cldist$.
@@
 The estimated age of \clustername\ is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by the last disk midplane passage, which occurred at a Galactocentric radius $R \approx 30~\kpc$.
-However, most details of this idea remain a mystery: the Magellanic stream is low column density, the Milky Way disk at this large radius has low gas surface density, and the relative velocity of the leading arm gas and Milky Way gas is large.
+However, most details of this idea remain a mystery: the Magellanic stream has low column density, the Milky Way disk at this large radius has low gas density, and the relative velocity of the leading arm gas and Milky Way gas is large.
 However it formed, the discovery of a young stellar cluster in the Milky Way halo presents an interesting opportunity for study.
@@
 \section{Introduction} \label{sec:intro}
-%Yumi: Intro can be condensed and go into the point quickly.
-The halo of the Milky Way is characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
-This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the formation of the Galaxy: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
-These systems likely came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
+
+The halo of the Milky Way is typically characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
+This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted early on in the formation of the Galaxy \citep[massive dwarf galaxies][]{Deason:2015, Fiorentino:2015}.
+It is thought that these systems came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
 The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC and SMC), and about 50 dwarf satellites within the virial radius of the Galaxy.
-While Sagittarius was likely stripped of its neutral gas long ago through repeated passage about the Milky Way \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams that wrap nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
-Here, we report the first discovery of a young cluster of co-moving stars in the Milky Way halo that suggests that young stars can form and exist in this otherwise quenched and aging structural component of the Galaxy.
+While Sagittarius was likely stripped of its neutral gas long ago through repeated passage about the Milky Way \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
+Here, we report the first discovery of a young cluster of co-moving stars in the Milky Way halo that appears to be associated with this \lmcsmc\ gas stream, which suggests that young stars can form from tidally stripped gas during low-mass mergers and may therefore exist throughout the otherwise aging stellar halo of our Galaxy.
 
-% Yumi: this paragraph needs to be clear. The MS is the trailing gas and the LA is the leading gas. Both together is 200 degrees long.
-The Magellanic stream (MS) is a large stream of (predominantly) hydrogen gas emanating from the \lmcsmc\ system that contains a significant fraction of the total gas mass associated with the \lmcsmc\ \citep{Bruns:2005} and wraps nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
-The stream was discovered in early surveys of 21 cm emission and has since been studied in great detail by large-area radio sky surveys, and in H$\alpha$ emission \citep{Weiner:1996, Barger:2017}.
-With increased resolution, surveys have found small-scale structure and gas fragmentation \citep[e.g.,][]{Nidever:2008, For:2014} and a large-scale bifurcation, with %semi-distinct ``strands'' that lead back to the LMC and broader system, respectively \citep[e.g.,][]{Morras:1983, Putman:2003}.
-kinematically \citep{Nidever:2008} and chemically \citep{Fox:2013} distinct ``strands'' that lead back to the LMC and the SMC, respectively.
-As surveys push deeper to lower column densities, extensions of the stream have been found both in the trailing region \citep{Nidever:2010}, but also in the leading arm, which has been found to connect to regions of low-column-density gas ($N\sim 10^{18}$--$10^{19}~\textrm{cm}^{-2}$) on the other side of the Galactic disk \citep{Putman:1998, Nidever:2008}.
-The leading arm (LA) has been decomposed into three or four distinct ``features'' named LA1--4 \citep{Bruns:2005, Nidever:2008, Venzmer:2012} with total HI mass $\sim 4 \times10^7~\msun$ \citep{Venzmer:2012}.
+The Magellanic stream (MS), including gas in the leading arm (LA), is a large stream of predominantly hydrogen gas emanating from the \lmcsmc\ system that contains a significant fraction of the total gas mass associated with the \lmcsmc\ \citep{Bruns:2005} and wraps nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
+The trailing MS has been studied in great detail by large-area and high-resolution radio sky surveys: Recent surveys have found small-scale structure and gas fragmentation \citep[e.g.,][]{Nidever:2008, For:2014} and a large-scale bifurcation, with kinematically \citep{Nidever:2008} and chemically \citep{Fox:2013} distinct ``strands'' that lead back to the LMC and the SMC.
+The LA gas has been found to connect to regions of low-column-density gas ($N\sim 10^{18}$--$10^{19}~\textrm{cm}^{-2}$) on the other side of the Galactic disk \citep{Putman:1998, Nidever:2008}, and has been decomposed into distinct gas features named LA1--4 \citep{Bruns:2005, Nidever:2008, Venzmer:2012}.
+%that contain a small fraction of the total MS mass \citep[$\sim 4 \times10^7~\msun$;][]{Venzmer:2012}.
 
-The origin and formation of the LA features in the MS is still uncertain.
-Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC, thus implying that the gas in the LA was stripped from the SMC \citep{Putman:1998}.
-In later work, it has instead been argued that outer features of the LMC appear to lead directly into the LA-1 feature \citep{Nidever:2008}, implying an LMC origin for the leading arm.
-Recent chemical abundance measurements along several sightlines passing through the LA again suggested the SMC origin \citep{Fox:2018, Richter:2018}.
-Recent hydrodynamical simulations of the MCs on the first infall to the Milky Way, however, showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas creates filamentary gas structures both in the LA and the MS \citep{Pardy:2018}.
+The origin and formation of the LA features of the MS is still uncertain.
+Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC \citep{Putman:1998}, but it has also been argued that outer features of the LMC appear to lead directly into the LA1 feature, implying an LMC origin \citep{Nidever:2008}.
+Recent chemical abundance measurements along several sight-lines passing through the LA again suggested the SMC origin \citep{Fox:2018, Richter:2018}.
 Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the LA \citep{Nidever:2008, Besla:2012}.
-However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions with gas in the outer Milky Way disk may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.
+However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions with gas in the outer Milky Way disk (from the recent disk plane passage) may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.
+
+% Streams formed from tidally stripped material --- such as the Sagittarius or Palomar 5 \citep{Odenkirchen:2001} stellar streams, or gas streams such as the MS --- encode information about the orbital history and future trajectory of their progenitor system \citep[e.g.,][]{Johnston:1999}.
+% For this reason, streams of debris are of interest for constraining the dark matter distribution around the Galaxy, as well as for providing a fossil record of the Milky Way's accretion history \citep{Johnston:1998, Bullock:2005}.
+% Early models for the formation of the MS invoke ram pressure and tidal stripping to explain the sky distribution and extent of the MS, and typically require that the \lmcsmc\ system complete several orbits around the Galaxy in order to strip enough material \citep[e.g.,][]{Murai:1980, Gardiner:1994, Mastropietro:2005}.
+% However, later
+The gas in the MS therefore encodes information about the orbital history and future trajectory of the \lmcsmc, and about interactions between this gas and the Milky Way.
+Combined with recent proper motion measurements of the LMC \citep{Kallivayalil:2006} and improved models for the \lmcsmc\ that suggest they are on their first passage through the Galaxy \citep{Besla:2007, Besla:2010, Besla:2012}, several groups have used the MS to constrain properties of both the interaction history of the \lmcsmc\ and the dark matter halo of the Milky Way (see recent review by \citealt{DOnghia:2016}).
+In general, these new models for the formation of the MS rely on past interactions between the LMC and SMC to preprocess the Magellanic gas distribution before infall and eventual stripping by the tidal field of the Milky Way \citep{Besla:2012, Diaz:2012};
+More recent hydrodynamical simulations of the MCs showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas can create filamentary gas structures both in the LA and the MS \citep{Pardy:2018}.
+
+One critical difficulty in using the MS to further improve models of the \lmcsmc\ interaction and infall is the lack of distance information along the MS.
+No significant over-density of stars have been found associated with the trailing MS \citep{Guhathakurta:1998}, thus leaving distance and tangential velocity information largely unknown.
+While a small number of young OB stars have been found in the vicinity of the LA gas \citep{Casetti-Dinescu:2014, Zhang:2017}, given their sparsity and concentration near the Galactic plane, it is difficult to unambiguously associate them with the MS (they could instead be runaway OB stars from the Milky Way disk).
+
+In this \articlename, we report the discovery of a young stellar cluster at the far edge of the LA-2 feature ($L_{\textrm{MS}} \sim 65^\circ$) that is located far into the Galactic halo ($D \sim \cldist$) and therefore plausibly formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
+This provides the first precise distance measurement to the MS leading arm to be compared with simulations of the \lmcsmc\ in the Milky Way, and provides an opportunity to study recent star formation in a unique environment.
+The discovery of \clustername\ will enable new modeling efforts that track the infall of the \lmcsmc, the tidal stripping of Magellanic gas, and the interaction of this gas with the Milky Way.
+
+In \sectionname~\ref{sec:data}, we present the initial discovery with \gaia\ \DR{2} and follow-up observations with \decam\ to obtain deeper photometry of the region around the association.
+In \sectionname~\ref{sec:results}, we use the \gaia\ data to measure the kinematics, and \decam\ photometry to infer the age, metallicity, and distance to \clustername, and discuss plausible formation scenarios.
+% In \sectionname~\ref{sec:discussion}, we discuss implications for future searches for stars associated with the MS, and discrepancies with existing models of the LA.
+We conclude in \sectionname~\ref{sec:conclusion}.
 
 % Notebook: Figure-CMDs
-\begin{figure*}[ht!]
+\begin{figure*}[t!]
 \centering
@@
 \caption{Color-magnitude diagram, sky positions, and proper motions from \gaia\ \DR{2} for the region around $(\alpha, \delta) \sim (179, -29)^\circ$.
-\textbf{Left panel}: \gaia\ color-magnitude diagram (CMD) for all sources with $G < 20$ and sky position within 3 degrees of $(\alpha, \delta) = (179.5, -28.8)^\circ$.
+\textbf{Left panel}: \gaia\ color-magnitude diagram (CMD) for all sources with $G < 20$ and sky position within 3 degrees of $(\alpha, \delta) = (179.5, -28.8)^\circ$, extinction corrected following \citet{Danielski:2018}.
 Red line shows a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone shifted to a distance of $30~\kpc$.
 Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
-\yumi{It seems you made extinction correction on this CMD.
-If so, please describe it in the text.}
 \textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).
@@
 \end{figure*}
-
-Streams formed from tidally stripped material --- such as the Sagittarius or Palomar 5 \citep{Odenkirchen:2001} stellar streams, or gas streams such as the MS --- encode information about the orbital history and future trajectory of their progenitor system \citep[e.g.,][]{Johnston:1999}.
-For this reason, streams of debris are of interest for constraining the dark matter distribution around the Galaxy, as well as for providing a fossil record of the Milky Way's accretion history \citep{Johnston:1998, Bullock:2005}.
-Several groups have attempted to use the MS to constrain both the infall history of the \lmcsmc\ and the dark matter halo of the Milky Way (see recent review by \citealt{DOnghia:2016}).
-Early models for the formation of the MS invoke ram pressure and tidal stripping to explain the sky distribution and extent of the MS, and typically require that the \lmcsmc\ system complete several orbits around the Galaxy in order to strip enough material \citep[e.g.,][]{Murai:1980, Gardiner:1994, Mastropietro:2005}.
-However, later measurements of the proper motion of the LMC (\citealt{Kallivayalil:2006}, later confirmed by \gaia\ \citealt{van-der-Marel:2016}) and improved models for the infall dynamics \citep{Besla:2007} suggest instead that the \lmcsmc\ system could be on its first passage through the Galaxy \citep{Besla:2010, Besla:2012}.
-In addition, the orbit of the LMC implied by the new proper motion measurement appears to be offset by $\approx 10^\circ$ from the trailing MS \citep{Besla:2010}.
-Put together, these recent revelations have led to new models for the formation of the MS that largely rely on past interactions between the LMC and SMC to preprocess the gas distribution before infall and eventual stripping by the tidal field of the Milky Way \citep{Besla:2012, Diaz:2012}.
-
-One critical difficulty in using the MS to constrain models of the \lmcsmc\ interaction and infall is the lack of distance information along the stream.
-No significant over-density of stars have been found associated with the trailing portion of the MS \citep{Guhathakurta:1998}, thus leaving distance and tangential velocity information largely unknown.
-Recently, a small number of young OB stars have been found in the vicinity of the leading arm gas, with radial velocities consistent with having formed from the leading MS \citep{Casetti-Dinescu:2014, Zhang:2017}.
-However, given their sparsity and concentration near the Galactic plane, it is difficult to unambiguously associate them with the MS: these could instead be runaway OB stars from the Milky Way disk.
-
-In this \articlename, we report the discovery of a clustered association of young stars at the far edge of the LA-2 feature ($L_{\textrm{MS}} \sim 65^\circ$) that is unambiguously located far into the Galactic halo ($D \sim \cldist$) and therefore plausibly formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
-This provides a clear distance measurement to the leading arm of the MS to be compared with models of \lmcsmc\ interaction and infall into the Milky Way, and also provides an opportunity to study recent star formation in a regime unlike that of the Milky Way.
-The discovery of \clustername\ will enable new modeling efforts that track the infall of the LMC-SMC, the tidal stripping of Magellanic gas, and the interaction of this gas with the Milky Way.
-
-In \sectionname~\ref{sec:data}, we present the initial discovery with \gaia\ \DR{2} and follow-up observations with \decam\ to obtain deeper photometry of the region around the association.
-In \sectionname~\ref{sec:results}, we use the \decam\ photometry to infer the age, metallicity, and distance to \clustername, and discuss plausible formation scenarios for this cluster.
-% In \sectionname~\ref{sec:discussion}, we discuss implications for future searches for stars associated with the MS, and discrepancies with existing models of the LA.
-We conclude in \sectionname~\ref{sec:conclusion}.
 
@@
 \figurename~\ref{fig:cmds} shows the \gaia\ data for this region:
-The left panel shows the \gaia\ color-magnitude diagram, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}.
+The left panel shows the \gaia\ color-magnitude diagram, extinction corrected following the procedure used in \citet{Danielski:2018}, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}.
 Surprisingly, this group appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
@@
 
-\section{Conclusion} \label{sec:conclusion}
+\section{Conclusions} \label{sec:conclusion}
 
@@
 \section{Data}
-\label{sec:data}
+\label{sec:datatables}
 

### 2018-11-10 ms.tex
comments

@@
 
+\clearpage
+
 \subsection{Follow-up with \decam}
@@
 \label{fig:decam-field}
-\end{figure}
-
-% Notebook: Figure-DECam-CMD
-\begin{figure}[t!]
-\centering
-\includegraphics[width=0.45\textwidth]{figures/DECam-cmd.pdf}
-\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
-Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
-The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
-}
-\label{fig:decam-cmd}
 \end{figure}
@@
 We note that the smaller over-density located northeast of the \decam\ field was not followed up in this work.
+
+% Notebook: Figure-DECam-CMD
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/DECam-cmd.pdf}
+\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
+Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
+The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
+}
+\label{fig:decam-cmd}
+\end{figure}
 
@@
 The larger solid-line circle indicates the region we define as the cluster area, and the two smaller dashed-line circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
-The control fields are designed to, together, have the same total area as the cluster field. \yumi{Any changes if you pick different control fields?}
+The control fields are designed to, together, have the same total area as the cluster field, and were chosen to have similar latitudes as the cluster field in the Magellanic stream coordinate system \citep{Nidever:2008}.
 The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.

### 2018-11-10 ms.tex
ack

@@
 
-\subsection{Inferring the mean proper motion}
-\label{sec:pmclean}
-
 % Notebook: Proper-motion-membership
@@
 \end{figure*}
+
+\subsection{Inferring the mean proper motion}
+\label{sec:pmclean}
 
@@
 Ekta Patel (Arizona),
+Sarah Pearson (Flatiron),
 Josh Peek (STScI),

### 2018-11-10 ms.tex
new figures

@@
 The coordinate system is the Magellanic stream spherical coordinate system defined in \cite{Nidever:2008}, and the units of $L_{\rm MS}$ and $B_{\rm MS}$ are degrees.
-The colorbar shows the column density of \hi in units of $10^19~\textrm{atoms}~\textrm{cm}^{-2}$.
+The colorbar shows the column density of \hi in units of $10^{19}~\textrm{atoms}~\textrm{cm}^{-2}$.
 The red circle marks the position of \clustername.}
@@
 \caption{The position-velocity diagram of GASS \hi Gaussian centers in the same region as \figurename~\ref{fig:gass_maps}, showing the line-of-sight velocity (in the local standard of rest frame) of gas near \clustername.
+Here the colorbar shows the gas density in units of $10^{18}~\textrm{atoms}~\textrm{cm}^{-2}\,\textrm{deg}$.
 Note that the densest gas at the longitude of \clustername\ (vertical line) appears to be associated with the lower velocity filaments seen at lower longitudes $L_{\textrm{MS}} \lesssim 60^\circ$, which may be decelerated gas associated with the Magellanic stream.

### 2018-11-13 ms.tex
Update on Overleaf.
improve fig

@@
-% TODO: after submission
+% TODO: after submission?
 % - Split cluster into 2? Price-Whelan 1a and 1b?
@@
 
-\author[0000-0003-2808-275X]{Douglas~P.~Finkbeiner}
-\affiliation{Institute for Theory and Computation, Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
+% \author[0000-0003-2808-275X]{Douglas~P.~Finkbeiner}
+% \affiliation{Institute for Theory and Computation, Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
 
@@
 We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association in the Milky Way halo: \clustername.
-At a Galactocentric cylindrical position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
-By assuming that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the Magellanic stream, $D \approx \cldist$.
+From isochrone fitting to deeper, follow-up \decam\ imaging of the cluster, we also measure its distance, $D \approx \cldist$.
+At its present Galactocentric cylindrical position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
+If we assume that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the leading arm of the Magellanic stream.
 At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with Milky Way disk.
@@
 The trailing MS has been studied in great detail by large-area and high-resolution radio sky surveys: Recent surveys have found small-scale structure and gas fragmentation \citep[e.g.,][]{Nidever:2008, For:2014} and a large-scale bifurcation, with kinematically \citep{Nidever:2008} and chemically \citep{Fox:2013} distinct ``strands'' that lead back to the LMC and the SMC.
-The LA gas has been found to connect to regions of low-column-density gas ($N\sim 10^{18}$--$10^{19}~\textrm{cm}^{-2}$) on the other side of the Galactic disk \citep{Putman:1998, Nidever:2008}, and has been decomposed into distinct gas features named LA1--4 \citep{Bruns:2005, Nidever:2008, Venzmer:2012}.
+The LA gas has been found to connect to regions of low-column-density gas ($N\sim 10^{18}$--$10^{19}~\textrm{cm}^{-2}$) on the other side of the Galactic disk \citep{Putman:1998, Nidever:2008}, and has been decomposed into distinct gas features named LA I--IV \citep{Bruns:2005, Nidever:2008, Venzmer:2012}.
 %that contain a small fraction of the total MS mass \citep[$\sim 4 \times10^7~\msun$;][]{Venzmer:2012}.
@@
 The origin and formation of the LA features of the MS is still uncertain.
-Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC \citep{Putman:1998}, but it has also been argued that outer features of the LMC appear to lead directly into the LA1 feature, implying an LMC origin \citep{Nidever:2008}.
+Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC \citep{Putman:1998}, but it has also been argued that outer features of the LMC appear to lead directly into the LA I feature, implying an LMC origin \citep{Nidever:2008}.
 Recent chemical abundance measurements along several sight-lines passing through the LA again suggested the SMC origin \citep{Fox:2018, Richter:2018}.
@@
 
-In this \articlename, we report the discovery of a young stellar cluster at the far edge of the LA-2 feature ($L_{\textrm{MS}} \sim 65^\circ$) that is located far into the Galactic halo ($D \sim \cldist$) and therefore plausibly formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
+In this \articlename, we report the discovery of a young stellar cluster at the far edge of the LA II feature ($L_{\textrm{MS}} \sim 65^\circ$) that is located far into the Galactic halo ($D \sim \cldist$) and therefore plausibly formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
 This provides the first precise distance measurement to the MS leading arm to be compared with simulations of the \lmcsmc\ in the Milky Way, and provides an opportunity to study recent star formation in a unique environment.
@@
 In \sectionname~\ref{sec:data}, we present the initial discovery with \gaia\ \DR{2} and follow-up observations with \decam\ to obtain deeper photometry of the region around the association.
-In \sectionname~\ref{sec:results}, we use the \gaia\ data to measure the kinematics, and \decam\ photometry to infer the age, metallicity, and distance to \clustername, and discuss plausible formation scenarios.
+In \sectionname~\ref{sec:methods}, we use the \gaia\ data to measure the kinematics, and \decam\ photometry to infer the age, metallicity, and distance to \clustername
+In \sectionname~\ref{sec:results}, we interpret the inferred stellar population parameters of \clustername\ and discuss plausible formation scenarios.
 % In \sectionname~\ref{sec:discussion}, we discuss implications for future searches for stars associated with the MS, and discrepancies with existing models of the LA.
@@
 Our original intent was to search for small, distant, comoving groups of blue horizontal branch stars to identify new candidate satellites of the Milky Way.
-We therefore initially select all stars from \gaia\ with parallax $\varpi < 1$, color $-0.5 < (\bprp) < 0$, $G$-band magnitude $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see Appendix~\ref{sec:queries} for database query).
+We therefore initially select all stars from \gaia\ with parallax $\varpi < 1$, color $-0.5 < (\bprp) < 0$, $G$-band magnitude $G < 20$, and Galactic latitude $|b| > 20^\circ$ (see Appendix~\ref{sec:queries} for the database query).
 We further exclude stars within a $15^\circ$ radius from the LMC, and a $8^\circ$ radius from the SMC --- 27,895 stars remain after these cuts.
@@
 global zero-point and color-terms in each band.
-%\todo{Nidever: can you describe the observations? Exposure times, dither, whatever is usually done...}
-%The photometry was reduced...\todo{Nidever: describe your pipeline?}
 
@@
 We perform these analyses separately because \gaia\ \DR{2} only includes the most massive members of the cluster, but the addition of lower main sequence members apparent in the \decam\ photometry provide a much better constraint on the cluster parameters.
+The parameters derived from this analysis are summarized in \tablename~\ref{tbl:clusterparams}.
 
@@
 
-\subsection{Inferring the mean proper motion}
+\subsection{Inferring the mean proper motion with \gaia}
 \label{sec:pmclean}
@@
 The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$ is the identified comoving association of blue stars.\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.}
-Note that \figurename~\ref{fig:pm-members} is only meant an illustration: The cluster proper motion is determined probabilistically by taking into account the full \gaia\ covariance matrices for each source, as described below.
+Note that \figurename~\ref{fig:pm-members} is only meant as an illustration: The cluster proper motion is determined probabilistically by taking into account the full \gaia\ covariance matrices for each source, as described below.
 
@@
 For the young cluster, we find $\bs{x} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
-The proper-motion dispersion is consistent with zero, and is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.
+The proper-motion dispersion is consistent with zero, and is likely unmeasured, because of the proper motion uncertainties; 95\% of the posterior samples have $s < 0.09~\masyr$.
 \tablename~\ref{tbl:gaiadata} contains a subset of the \gaia\ \DR{2} data for stars in the cluster field, with kinematic membership probabilities determined from this modeling procedure.
 
-\subsection{Inferring the stellar population parameters}
+\subsection{Inferring the stellar population parameters with \decam photometry}
 \label{sec:popmodel}
@@
 \caption{Prior probability distributions for each of the stellar parameters defined in \sectionname~\ref{sec:popmodel}, used for the independent (per star) posterior samplings.
+The stellar parameters here are the ``equal evolutionary point'' number $\eep$, age $\tau$, metallicity $\feh$, extinction $A_V$, and distance $D$.
 The prior on \eep\ is computed by calculating the stellar mass, $m$, corresponding to a given point in the isochrone parameter space, $(\eep, \tau, \feh)$, and computing the probability from a Salpeter \citep{Salpeter:1955} mass prior such that $p(\eep) = p(m)\,\left|\frac{\dd m}{\dd \eep}\right|$, following the prescription used in \texttt{isochrones} \citep{Morton:2015}.
@@
 \caption{Prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, used for the hierarchical inference of the cluster stellar population parameters.
+The cluster parameters here are the cluster age $\tau^*$, metallicity $\feh^*$, extinction $A_V^*$, and distance $D^*$, and the fraction of stars in the field that belong to the cluster $f$.
 \label{tbl:hyperpriors}}
@@
 The parameters of this model are set to match the circular velocity profile and disk properties of \citet{Bovy:2015}, and is implemented in the \texttt{gala} package \citep{gala} as the \texttt{MilkyWayPotential}.
-We note that we do not include the LMC/SMC as a component of our mass model.
 
-Also shown in \figurename~\ref{fig:orbits} is the present-day location of the LMC (open black circle), the present-day location of \clustername\ (filled black circle), the past orbit of the LMC over the same period, and the projected future orbit of the LMC (dashed line).
+We tried including an LMC component as a Hernquist sphere \citep{Hernquist:1990} with masses between $10^{10}$--$2.5\times 10^{11}~\msun$, but find that the orbit of \clustername\ does not change much over the integration period.
+If the LMC mass were as high as $8\times 10^{11}~\msun$, all three orbits of \clustername\ return to and end up bound to the LMC, but at this large of a mass, the assumption of a fixed Milky Way reference frame is invalid.
+We therefore neglect \lmcsmc\ component in what follows, and present an alternate interpretation below.
+
+Also shown in \figurename~\ref{fig:orbits} is the present-day location of the LMC (open black circle), the present-day location of \clustername\ (filled black circle), the past orbit of the LMC over the same period, and the projected future orbit of the LMC (dashed line), all excluding the \lmcsmc\ as a mass component.
 For the two lower LOS velocity cases, the orbit of \clustername\ crosses the midplane of the Galactic disk at a time comparable to the age of the cluster (i.e.
 when the color is darkest, corresponding to a time $\approx -130~\textrm{Myr}$).
-
-However, note that while the orbits of \clustername\ and the LMC are generally in the same orbital plane and have the same sense about the Galaxy, none of the orbits closely approach or cross the orbit of the LMC.
-This is expected if the gas shocked or otherwise lost kinetic energy through, e.g., ram pressure --- as is expected to explain the morphology of the LA material \citep[e.g.,][]{Hammer:2015} --- during or before the star formation event that produced \clustername.
+However, while the orbits of \clustername\ and the LMC are generally in the same orbital plane and have the same sense about the Galaxy, none of the orbits closely approach (within the half-mass radius of our Hernquist model for the LMC) or cross the orbit of the LMC (even when including the LMC mass component).
+This is expected if the gas was shocked or otherwise lost kinetic energy through, e.g., ram pressure --- as is expected to explain the morphology of the LA material \citep[e.g.,][]{Hammer:2015} --- during or before the star formation event that produced \clustername.
+We therefore posit that the orbit of \clustername\ can be explained as having originated from the \lmcsmc\ system with some loss of orbital energy during the star formation event.
 
@@
 \acknowledgments
+
+We thank Doug Finkbeiner (Harvard) for contributing to the \decam\ observations that enabled this work.
 

### 2018-11-13 ms.tex
caption and abs

@@
 We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association in the Milky Way halo: \clustername.
-From isochrone fitting to deeper, follow-up \decam\ imaging of the cluster, we also measure its distance, $D \approx \cldist$.
-At its present Galactocentric cylindrical position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center, on the other side of the Milky Way disk relative to the LMC.
+From isochrone fitting to follow-up \decam\ imaging of the cluster, we also measure its distance, $D \approx \cldist$.
+At its present Galactocentric position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center on the other side of the Milky Way disk.
 If we assume that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the leading arm of the Magellanic stream.
@@
 Red line shows a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone shifted to a distance of $30~\kpc$.
-Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
+Shaded pixels (grey 2D histogram) show the density of all sources in the CMD for this sky region, and points (black markers) show only sources in the blue selection polygon shown.
 \textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).

### 2018-11-13 ms.tex
Update on Overleaf.

@@
 The gas in the MS therefore encodes information about the orbital history and future trajectory of the \lmcsmc, and about interactions between this gas and the Milky Way.
-Combined with recent proper motion measurements of the LMC \citep{Kallivayalil:2006} and improved models for the \lmcsmc\ that suggest they are on their first passage through the Galaxy \citep{Besla:2007, Besla:2010, Besla:2012}, several groups have used the MS to constrain properties of both the interaction history of the \lmcsmc\ and the dark matter halo of the Milky Way (see recent review by \citealt{DOnghia:2016}).
+Combined with recent proper motion measurements of the LMC \citep{Kallivayalil:2006, Kallivayalil:2013} and improved models for the \lmcsmc\ that suggest they are on their first passage through the Galaxy \citep{Besla:2007, Besla:2010, Besla:2012}, several groups have used the MS to constrain properties of both the interaction history of the \lmcsmc\ and the dark matter halo of the Milky Way (see recent review by \citealt{DOnghia:2016}).
 In general, these new models for the formation of the MS rely on past interactions between the LMC and SMC to preprocess the Magellanic gas distribution before infall and eventual stripping by the tidal field of the Milky Way \citep{Besla:2012, Diaz:2012};
@@
 
-In this \articlename, we report the discovery of a young stellar cluster at the far edge of the LA II feature ($L_{\textrm{MS}} \sim 65^\circ$) that is located far into the Galactic halo ($D \sim \cldist$) and therefore plausibly formed from gas in the leading arm of the Magellanic stream as it crossed the Galactic disk.
+In this \articlename, we report the discovery of a young stellar cluster at the far edge of the LA II feature ($L_{\textrm{MS}} \sim 65^\circ$) that is located far into the Galactic halo ($D \sim \cldist$) and therefore plausibly formed from gas in the leading arm of the MS as it crossed the Galactic disk.
 This provides the first precise distance measurement to the MS leading arm to be compared with simulations of the \lmcsmc\ in the Milky Way, and provides an opportunity to study recent star formation in a unique environment.
@@
 Forced PSF photometry was performed with the PHOTRED pipeline \citep{Nidever:2017} which uses the DAOPHOT ALLSTAR \citep{Stetson:1987} and ALLFRAME \citep{Stetson:1994} suite of programs.
-The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for
-global zero-point and color-terms in each band.
+The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for global zero-point and color-terms in each band.
 
@@
 First, in \sectionname~\ref{sec:pmclean}, we use astrometric data from \gaia\ \DR{2} to determine the mean proper motion of the cluster by modeling the kinematics of the cluster and background sources.
-Then, in \sectionname~\ref{sec:popmodel}, we use photometric data from \decam\ to assign membership probabilities to sources and simultaneously infer the cluster stellar population parameters (age, metallicity, distance, etc.).
+Then, in \sectionname~\ref{sec:popmodel}, we use photometric data from \decam\ to assign membership probabilities to sources and simultaneously measure the cluster stellar population parameters (age, metallicity, distance, etc.).
 We perform these analyses separately because \gaia\ \DR{2} only includes the most massive members of the cluster, but the addition of lower main sequence members apparent in the \decam\ photometry provide a much better constraint on the cluster parameters.

### 2018-11-13 ms.tex
Update on Overleaf.

@@
 The control fields are designed to, together, have the same total area as the cluster field, and were chosen to have similar latitudes as the cluster field in the Magellanic stream coordinate system \citep{Nidever:2008}.
+\yumi{by assuming a smooth background stellar density at similar latitudes?}
 The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.
@@
 XD takes into account the full error distributions for each proper motion measurement $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, including covariances $\mat{C}_\mu$, provided by \gaia\ \DR{2}.
-After running XD, we fix the parameters of the background model and model the proper motion distribution in the cluster region using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{x}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
+After running XD, we fix the parameters of the background model \yumi{you meant the model for the control fields?
+If so, please clarify that background model equals control fields model.} and model the proper motion distribution in the cluster region using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{x}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
 In detail, taking $f$ to be the fraction of blue stars in this region belonging to the young cluster, and \truepm\ to be the true proper motion for a single star,
@@
 We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
-We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
+\yumi{why this number of walkers and steps?
+depends on number of fitting parameters and autocorrelation time?}
+We then thin \yumi{thin?
+out of my own curiosity: why thinning is needed?} the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
 For the young cluster, we find $\bs{x} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.

### 2018-11-13 ms.tex
Update on Overleaf.

@@
 The likelihood of a given set of these parameters, $\bs{\theta} = (\eep, \tau, \feh, A_V, D)$, is then computed from the photometry and (assumed Gaussian) photometric uncertainties given the predicted photometry.
+\yumi{is it easy to use real photometric uncertainties instead of assuming Gaussian?
+If not, we can wait what the referee will say.}
 
@@
 The bounds on $\eep$ limit the isochrone to evolutionary phases between the zero-age main sequence to the terminal-age main sequence, but this prior is actually computed using the stellar mass computed from the isochrone parameters (see caption of \tablename~\ref{tbl:priors}).
-The prior and bounds on $A_V$ are set to prefer small and reasonable values of extinction for this moderately high Galactic latitude region.
+The prior and bounds on $A_V$ are set to prefer small and reasonable values of extinction for this moderately high Galactic latitude region. \yumi{Av is known to follow a log-normal distribution.}
 The prior on distance assumes a uniform space density of stars.
@@
 We are developing tools to perform star cluster parameter inference in this way (Morton et al., in prep.), but here we adopt a simple hack to allow us to instead perform individual posterior samplings and then combine those samplings into a hierarchical inference.
+\yumi{I like this fancy way.
+But it would be helpful for readers (potential users of this method) if you can briefly describe the strength of this methodology over the standard isochrone fitting for a star cluster?}
 
@@
 Given their location in the CMD, these stars must be young, and so also have much better constrained stellar parameters.
+\yumi{I am not convinced by that bright stars have better constrained stellar parameters.
+Their color and magnitude are sensitive to dust and effective temperature, but their age}
 We therefore use the brightest \emph{kinematic} member of \clustername\ as an ``anchor'' star:

### 2018-11-14 ms.tex
Update on Overleaf.

@@
 In general, these new models for the formation of the MS rely on past interactions between the LMC and SMC to preprocess the Magellanic gas distribution before infall and eventual stripping by the tidal field of the Milky Way \citep{Besla:2012, Diaz:2012};
-More recent hydrodynamical simulations of the MCs showed that the repeated encounters between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas can create filamentary gas structures both in the LA and the MS \citep{Pardy:2018}.
+More recent hydrodynamical simulations of the MCs showed that the repeated encounters even after the infall between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas can create filamentary gas structures both in the leading and trailing MS \citep{Pardy:2018}.
+Many observational studies \citep[e.g.,][]{Olsen:2011, Noel:2013, Mackey:2016, Carrera:2017, Choi:2018a, Choi:2018b, Zivick:2018, Belokurov:2019} have been made in the Magellanic system that are available to provide strong constraints on modeling the interaction history of the \lmcsmc\ in detail.
 
@@
 \textbf{Right panel}: The colored 2D density shows the difference in number of sources per pixel in the cluster field versus the two control fields (see left panel).
-The clear over-density in the cluster field (blue) are stars in \clustername.}
+The clear over-density in the cluster field (blue) are stars in \clustername. \yumi{can you add the mean proper motion vector of the cluster on this figure or figure 1?}}
 \label{fig:pm-members}
@@
 \yumi{I am not convinced by that bright stars have better constrained stellar parameters.
-Their color and magnitude are sensitive to dust and effective temperature, but their age}
+Their color and magnitude are sensitive to dust and effective temperature, but their age and metallicity would not constrained better than fainter stars.
+I suggest to remove the second half of the previous sentence.}
 We therefore use the brightest \emph{kinematic} member of \clustername\ as an ``anchor'' star:
@@
         p(\bs{\alpha}) \, p(f) \,
-        \prod_n^N p(\bs{m}_n \given \bs{\alpha}, f) \quad .
+        \prod_n^N p(\bs{m}_n \given \bs{\alpha}, f) \quad.
 \end{equation}
@@
 Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
+\yumi{How our Av is different from Schlegel map (https://irsa.ipac.caltech.edu/cgi-bin/bgTools/nph-bgExec)?
+Their Av is about 0.2.
+Are we consistent with them within uncertainty?}
 We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx \clage$, distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
@@
     \end{tabular}
-\caption{This table summarizes the measured or inferred kinematic and stellar population parameters of the young halo stellar cluster \clustername.
+\caption{This table summarizes the measured or inferred kinematic and stellar population parameters of the young halo stellar cluster \clustername. \yumi{please include uncertainties.}
 \label{tbl:clusterparams}}
@@
 At the sky location and distance of \clustername, i.e.
-well into the Galactic halo, the only plausible gas reservoirs that could have formed a young cluster are the Magellanic stream, or a previously unknown high velocity cloud (HVC).
+well into the Galactic halo, the only plausible gas reservoirs that could have formed a young cluster are the MS, or a previously unknown high velocity cloud (HVC).
 HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
-Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the mysterious Smith Cloud \citep{Smith:1963} is a metal-rich \citep[$\feh \sim 0.5$][]{Fox:2016} HVC that plausibly originated from the Galactic disk \citep[e.g.,][]{Bregman:1980}.
+Both processes clearly occur: the MS itself is evidence of gas accretion into the Milky Way halo, and the mysterious Smith Cloud \citep{Smith:1963} is a metal-rich \citep[$\feh \sim 0.5$][]{Fox:2016} HVC that plausibly originated from the Galactic disk \citep[e.g.,][]{Bregman:1980}.
 Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk that could have driven gas so far out into the halo have, at present-day, significantly higher metallicity than this cluster.
 
-We therefore take a closer look at the \hi gas in the vicinity of \clustername\ to assess its possible relation to the Magellanic stream.
-While no bulk metallicity measurements exist for the Magellanic stream Leading Arm gas, recent measurements of oxygen and silicon abundances suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2018, Richter:2018}.
+We therefore take a closer look at the \hi gas in the vicinity of \clustername\ to assess its possible relation to the MS.
+While no bulk metallicity measurements exist for the LA gas, recent measurements of oxygen and silicon abundances suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2018, Richter:2018}.
 If \clustername\ formed from this gas, we would then expect that the stellar metallicity should be similar to young stars in the SMC.
@@
 We next look at the kinematics of high velocity gas in this region.
-\figurename~\ref{fig:gass_maps} shows the \hi column density of the catalog of Gaussian centers \citep[producted with the techniques and software from][]{Nidever:2008} from the Galactic All Sky Survey \citep[GASS;][]{McClure-Griffiths:2009, Kalberla:2010} in the region around the Leading Arm of the Magellanic stream and plotted in the Magellanic stream coordinate system \citep[$L_{\rm MS}, B_{\rm MS}$;][]{Nidever:2008}.
+\figurename~\ref{fig:gass_maps} shows the \hi column density of the catalog of Gaussian centers \citep[producted with the techniques and software from][]{Nidever:2008} from the Galactic All Sky Survey \citep[GASS;][]{McClure-Griffiths:2009, Kalberla:2010} in the region around the LA and plotted in the MS coordinate system \citep[$L_{\rm MS}, B_{\rm MS}$;][]{Nidever:2008}.
 The location of \clustername\ is marked (red circle), and the three panels show three different velocity slices (indicated on each panel).
-The Magellanic stream gas is most visible and densest at the highest velocities where the LA II feature is found, around $L_{\rm MS} \lesssim 61^\circ$ and $B_{\rm MS} \sim -12^\circ$, but the lower panels (i.e.
+The MS gas is most visible and densest at the highest velocities where the LA II feature is found, around $L_{\rm MS} \lesssim 61^\circ$ and $B_{\rm MS} \sim -12^\circ$, but the lower panels (i.e.
 slower gas) still displays some of the same morphology as the highest velocity slice.
+\yumi{I was confused when I read this for the first time.
+You might want to mention earlier that HI velocities in the LA is measured to be larger than 150 kmc/s.
+Otherwise, the reader who are not familiar with the LA would misinterpret that the highest gas density around \clustername\ is found in the bottom panel.}
 
@@
 
-The entire region shown in \figurename~\ref{fig:gass_maps} is on the other side of the Galactic disk with respect to the Magellanic clouds, meaning that all of the Magellanic stream gas in this region has passed through the Galactic midplane.
-The similar filamentary structure in the high and lower velocity gas therefore raises the question: Did the low velocity filaments originate in the Magellanic stream, but were decelerated through interactions with Milky Way gas?
+The entire region shown in \figurename~\ref{fig:gass_maps} is on the other side of the Galactic disk with respect to the Magellanic clouds, meaning that all of the MS gas in this region has passed through the Galactic midplane.
+The similar filamentary structure in the high and lower velocity gas therefore raises the question: Did the low velocity filaments originate in the MS, but were decelerated through interactions with Milky Way gas?
 This presents a possible formation scenario for \clustername.
-If the cluster formed from the Magellanic stream gas, and some of the gas interacted with the Milky Way disk, the dynamics of the stars and the gas that interacted would have decoupled as soon as the stars formed.
+If the cluster formed from the LA gas, and some of the gas interacted with the Milky Way disk, the dynamics of the stars and the gas that interacted would have decoupled as soon as the stars formed.
 Given the geometry of the current location of \clustername\ (i.e.
@@
 \includegraphics[width=0.9\textwidth]{figures/orbits.pdf}
-\caption{The past orbit of \clustername in Galactocentric Cartesian coordinates, computed by assuming a line-of-sight velocity equal to each of three different possible gas  filaments in the LA II region of the Magellanic stream (as indicated in right panel).
+\caption{The past orbit of \clustername in Galactocentric Cartesian coordinates, computed by assuming a line-of-sight velocity equal to each of three different possible gas  filaments in the LA II region of the MS (as indicated in right panel).
 In these coordinates, the Sun is at $(x, y, z) = (-8.1, 0, 0)~\kpc$, and the present-day locations of \clustername\ (filled black marker) and the LMC (open black marker) are indicated.
@@
 We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername\ --- with an age $\tau \approx \clage$, heliocentric distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$.
-At its present day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic gas stream and thus it plausibly formed from Magellanic stream gas.
+At its present-day sky position, and at large distances, all significant quantities of \hi are associated with the LA and thus it plausibly formed from MS gas.
 The age of the cluster is broadly consistent with the time it would have most recently crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
-Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
+Previous studies have detected young stars in the LA and in the periphery of the LMC \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire young star cluster has been detected so far.% from the Clouds.
 
-The discovery of \clustername\ provides a critical distance constraint to the Magellanic stream and will aid future Magellanic system and Milky Way modeling efforts.
-It also provides an opportunity to study star formation in a unique environment, unlike that of the Milky Way disk or any other cluster-forming region.
+The discovery of \clustername\ provides a critical distance constraint to the LA and will aid future Magellanic system and Milky Way modeling efforts.
+It also provides an opportunity to study star formation in a unique environment (i.e., low gas density and low metallicity), unlike that of the Milky Way disk or any other cluster-forming region.
 The serendipitous discovery of this cluster is a reminder that the combined value of the \gaia\ data with deep, large-area imaging surveys provides a wealth of information about our Galaxy and stellar halo.
@@
 
+\facility{Blanco (DECam)}
+
 \software{
@@
 
-\facility{Blanco (DECam)}
-
 \bibliographystyle{aasjournal}

### 2018-11-14 ms.tex
chopping

@@
 It is thought that these systems came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
-The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC and SMC), and about 50 dwarf satellites within the virial radius of the Galaxy.
-While Sagittarius was likely stripped of its neutral gas long ago through repeated passage about the Milky Way \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
-Here, we report the first discovery of a young cluster of co-moving stars in the Milky Way halo that appears to be associated with this \lmcsmc\ gas stream, which suggests that young stars can form from tidally stripped gas during low-mass mergers and may therefore exist throughout the otherwise aging stellar halo of our Galaxy.
+The Milky Way, however, continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy \citep{Ibata:1994, Majewski:2003}, the presence of the Large and Small Magellanic Clouds (LMC and SMC), and about 50 dwarf satellites within the Galactic halo.
+While Sagittarius was likely stripped of its neutral gas long ago \citep{Burton:1999, Tepper-Garcia:2018}, the \lmcsmc\ system is associated with $\approx 8\times 10^8~\msun$ of \hi gas \citep{Bruns:2005}, which extends into leading and trailing gas streams \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
+Here we report the first discovery of a young star cluster in the Milky Way halo that appears to be associated with this \lmcsmc\ gas stream, which suggests that young stars can form from tidally stripped gas during low-mass mergers and may therefore exist throughout the otherwise aging stellar halo.
 
-The Magellanic stream (MS), including gas in the leading arm (LA), is a large stream of predominantly hydrogen gas emanating from the \lmcsmc\ system that contains a significant fraction of the total gas mass associated with the \lmcsmc\ \citep{Bruns:2005} and wraps nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010}.
+The Magellanic stream (MS), including gas in the leading arm (LA), is a large stream of predominantly hydrogen gas emanating from the \lmcsmc\ system that wraps nearly $\approx 200^\circ$ around the sky \citep{Mathewson:1974, Putman:1998, Bruns:2005, Nidever:2010} and contains a significant fraction of the total gas mass associated with the \lmcsmc\ \citep{Bruns:2005}.
 The trailing MS has been studied in great detail by large-area and high-resolution radio sky surveys: Recent surveys have found small-scale structure and gas fragmentation \citep[e.g.,][]{Nidever:2008, For:2014} and a large-scale bifurcation, with kinematically \citep{Nidever:2008} and chemically \citep{Fox:2013} distinct ``strands'' that lead back to the LMC and the SMC.
@@
 
-The origin and formation of the LA features of the MS is still uncertain.
-Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC \citep{Putman:1998}, but it has also been argued that outer features of the LMC appear to lead directly into the LA I feature, implying an LMC origin \citep{Nidever:2008}.
-Recent chemical abundance measurements along several sight-lines passing through the LA again suggested the SMC origin \citep{Fox:2018, Richter:2018}.
-Whatever the origin of the gas, it is clear that tidal stripping by the Milky Way is required to form the LA \citep{Nidever:2008, Besla:2012}.
-However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions with gas in the outer Milky Way disk (from the recent disk plane passage) may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.
+The origin and formation of these LA features is still uncertain.
+Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC \citep{Putman:1998}, but outer features of the LMC appear to lead directly into the LA I feature \citep{Nidever:2008}.
+Recent chemical abundance measurements along several sight-lines passing through the LA again support an SMC origin for the gas \citep{Fox:2018, Richter:2018}.
+Whatever the origin of the LA gas, it is clear that tidal stripping by the Milky Way is required to form the LA \citep{Nidever:2008, Besla:2012}.
+However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions the outer Milky Way disk (from the recent disk plane passage) may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.
 
@@
 % However, later
-The gas in the MS therefore encodes information about the orbital history and future trajectory of the \lmcsmc, and about interactions between this gas and the Milky Way.
-Combined with recent proper motion measurements of the LMC \citep{Kallivayalil:2006, Kallivayalil:2013} and improved models for the \lmcsmc\ that suggest they are on their first passage through the Galaxy \citep{Besla:2007, Besla:2010, Besla:2012}, several groups have used the MS to constrain properties of both the interaction history of the \lmcsmc\ and the dark matter halo of the Milky Way (see recent review by \citealt{DOnghia:2016}).
-In general, these new models for the formation of the MS rely on past interactions between the LMC and SMC to preprocess the Magellanic gas distribution before infall and eventual stripping by the tidal field of the Milky Way \citep{Besla:2012, Diaz:2012};
-More recent hydrodynamical simulations of the MCs showed that the repeated encounters even after the infall between the MCs strip gas not only from the SMC, but also from the LMC, and this tidally stripped gas can create filamentary gas structures both in the leading and trailing MS \citep{Pardy:2018}.
-Many observational studies \citep[e.g.,][]{Olsen:2011, Noel:2013, Mackey:2016, Carrera:2017, Choi:2018a, Choi:2018b, Zivick:2018, Belokurov:2019} have been made in the Magellanic system that are available to provide strong constraints on modeling the interaction history of the \lmcsmc\ in detail.
+The gas in the MS encodes information about the past and future trajectory of the \lmcsmc, and about interactions between this gas and the Milky Way.
+Combined with recent proper motion measurements of the LMC \citep{Kallivayalil:2006, Kallivayalil:2013} and improved models for the \lmcsmc\ that suggest they are on their first passage through the Galaxy \citep{Besla:2007, Besla:2010, Besla:2012}, several groups have used the MS to constrain properties of both the interaction history of the \lmcsmc\ and of the dark matter halo of the Milky Way (see recent review by \citealt{DOnghia:2016}).
+In general, these models for the formation of the MS rely on past interactions between the LMC and SMC to preprocess the Magellanic gas distribution before infall and eventual stripping by the tidal field of the Milky Way \citep{Besla:2012, Diaz:2012};
+More recent hydrodynamical simulations of the MCs showed that the repeated encounters between the \lmcsmc\ strip gas both from the SMC and the LMC, and this tidally stripped gas can then create filamentary structures both in the leading and trailing MS \citep{Pardy:2018}.
+Many observational studies \citep[e.g.,][]{Olsen:2011, Noel:2013, Mackey:2016, Carrera:2017, Choi:2018a, Choi:2018b, Zivick:2018, Belokurov:2019} of the \lmcsmc\ themselves will provide strong constraints the interaction history of the MCs.
 
 One critical difficulty in using the MS to further improve models of the \lmcsmc\ interaction and infall is the lack of distance information along the MS.
-No significant over-density of stars have been found associated with the trailing MS \citep{Guhathakurta:1998}, thus leaving distance and tangential velocity information largely unknown.
-While a small number of young OB stars have been found in the vicinity of the LA gas \citep{Casetti-Dinescu:2014, Zhang:2017}, given their sparsity and concentration near the Galactic plane, it is difficult to unambiguously associate them with the MS (they could instead be runaway OB stars from the Milky Way disk).
+No significant over-density of stars have been found associated with the trailing MS \citep{Guhathakurta:1998}, thus leaving distance and tangential velocity information unknown.
+While a small number of OB stars have been found in the vicinity of the LA gas \citep{Casetti-Dinescu:2014, Zhang:2017}, their sparsity and concentration near the Galactic plane make it difficult to unambiguously associate them with the MS and not runaway OB stars from the Milky Way disk.
 
@@
 \textbf{Right panel}: The colored 2D density shows the difference in number of sources per pixel in the cluster field versus the two control fields (see left panel).
-The clear over-density in the cluster field (blue) are stars in \clustername. \yumi{can you add the mean proper motion vector of the cluster on this figure or figure 1?}}
+The clear over-density in the cluster field (blue) are stars in \clustername.}
 \label{fig:pm-members}
@@
 The control fields are designed to, together, have the same total area as the cluster field, and were chosen to have similar latitudes as the cluster field in the Magellanic stream coordinate system \citep{Nidever:2008}.
-\yumi{by assuming a smooth background stellar density at similar latitudes?}
+We assume that the background density in the cluster field is equivalent to the average background density of the join control fields.
+From visual inspection of the CMDs of the control fields, we do not see any significant clustered over-density and therefore assume that these fields are dominated by the background stellar density.
 The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.
@@
 XD takes into account the full error distributions for each proper motion measurement $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, including covariances $\mat{C}_\mu$, provided by \gaia\ \DR{2}.
-After running XD, we fix the parameters of the background model \yumi{you meant the model for the control fields?
-If so, please clarify that background model equals control fields model.} and model the proper motion distribution in the cluster region using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{x}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
+After running XD on the proper motion distribution of the control fields, we fix the parameters of the density model and use this as the background model for the cluster field.
+We model the proper motion distribution in the cluster region using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{x}$ and isotropic variance $s^2$, and the XD-inferred background model, $p_{\textrm{XD}}$, for the background component.
 In detail, taking $f$ to be the fraction of blue stars in this region belonging to the young cluster, and \truepm\ to be the true proper motion for a single star,
@@
 We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{emcee, Goodman:2010} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
-We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
-\yumi{why this number of walkers and steps?
-depends on number of fitting parameters and autocorrelation time?}
-We then thin \yumi{thin?
-out of my own curiosity: why thinning is needed?} the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
+We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps, after which the chains appear converged.
+We then downsample the resulting chains by taking every 16th sample to preserve closer-to-independent samples, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
 For the young cluster, we find $\bs{x} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
@@
 The likelihood of a given set of these parameters, $\bs{\theta} = (\eep, \tau, \feh, A_V, D)$, is then computed from the photometry and (assumed Gaussian) photometric uncertainties given the predicted photometry.
-\yumi{is it easy to use real photometric uncertainties instead of assuming Gaussian?
+% \yumi{is it easy to use real photometric uncertainties instead of assuming Gaussian?
 If not, we can wait what the referee will say.}
+% Not easy, no - these are what David provides from his pipeline, and what Isochrones assumes as input. But the photometry is so precise the errors really are close to Gaussian
 
@@
 The bounds on $\eep$ limit the isochrone to evolutionary phases between the zero-age main sequence to the terminal-age main sequence, but this prior is actually computed using the stellar mass computed from the isochrone parameters (see caption of \tablename~\ref{tbl:priors}).
-The prior and bounds on $A_V$ are set to prefer small and reasonable values of extinction for this moderately high Galactic latitude region. \yumi{Av is known to follow a log-normal distribution.}
+The prior and bounds on $A_V$ are set to prefer small and reasonable values of extinction for this moderately high Galactic latitude region.
+% \yumi{Av is known to follow a log-normal distribution.} Yea the referee could push back, but we'll see!
 The prior on distance assumes a uniform space density of stars.
@@
 We are developing tools to perform star cluster parameter inference in this way (Morton et al., in prep.), but here we adopt a simple hack to allow us to instead perform individual posterior samplings and then combine those samplings into a hierarchical inference.
-\yumi{I like this fancy way.
+% \yumi{I like this fancy way.
 But it would be helpful for readers (potential users of this method) if you can briefly describe the strength of this methodology over the standard isochrone fitting for a star cluster?}
+% What is standard isochrone fitting?
 
 The brightest stars in the cluster have very precise \decam\ photometry, and have precise astrometry from \gaia.
-Given their location in the CMD, these stars must be young, and so also have much better constrained stellar parameters.
-\yumi{I am not convinced by that bright stars have better constrained stellar parameters.
-Their color and magnitude are sensitive to dust and effective temperature, but their age and metallicity would not constrained better than fainter stars.
-I suggest to remove the second half of the previous sentence.}
+Given their location in the CMD, these stars must be young.
 We therefore use the brightest \emph{kinematic} member of \clustername\ as an ``anchor'' star:
@@
 Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
-\yumi{How our Av is different from Schlegel map (https://irsa.ipac.caltech.edu/cgi-bin/bgTools/nph-bgExec)?
-Their Av is about 0.2.
-Are we consistent with them within uncertainty?}
 We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx \clage$, distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
+We find that the inferred extinction, $A_V \approx 0.33$, is somewhat larger than the value $A_{V, {\rm SFD}} \approx 0.2$ from the SFD dust map \citep{Schlegel:1998}.
+
 Also plotted in \figurename~\ref{fig:hierarch-iso} is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample: The abundance of sources between the nominal isochrone and the binary sequence highlights the fact that the cluster may contain a significant number of binary or multiple star systems, but we leave a detailed study of multiplicity to future work.
@@
         \toprule
-        Parameter & Value & Description \\
+        Name & Value & Description \\
         \tableline
-        $\mean{\alpha}$ & $178.8^\circ$ & mean right ascension \\
-        $\mean{\delta}$ & $-29.4^\circ$ & mean declination \\
-        $\mean{D}$ & $29~\kpc$ & mean Heliocentric distance \\
-        $\mean{\mu_\alpha}$ & $-0.56~\masyr$ & mean proper motion in RA\\
-        $\mean{\mu_\delta}$ & $0.47~\masyr$ & mean proper motion in Dec\\
+        $\mean{\alpha}$ & $178.8^\circ$ & right ascension \\
+        $\mean{\delta}$ & $-29.4^\circ$ & declination \\
+        $\mean{D}$ & $28.9 \pm 0.1~\kpc$ & Heliocentric distance \\
+        $\mean{\mu_\alpha}$ & $-0.56 \pm TODO~\masyr$ & proper motion in RA\\
+        $\mean{\mu_\delta}$ & $0.47 \pm TODO~\masyr$ & proper motion in Dec\\
         \tableline
-        $\tau$ & $130~\textrm{Myr}$ & age \\
+        $\tau$ & $130 \pm 6~\textrm{Myr}$ & age \\
         $M$ & $1200~\msun$ & total stellar mass \\
-        $\feh$ & $-1.1$ & metallicity \\
+        $\feh$ & $-1.10 \pm 0.02$ & metallicity \\
         \tableline
-        $A_V$ & $0.3$ & extinction \\
+        $A_V$ & $0.33 \pm 0.02$ & extinction \\
         \toprule
     \end{tabular}
-\caption{This table summarizes the measured or inferred kinematic and stellar population parameters of the young halo stellar cluster \clustername. \yumi{please include uncertainties.}
+\caption{This table summarizes the measured or inferred kinematic and stellar population parameters of the young halo stellar cluster \clustername.
+Formal precisions on all inferred parameters are very small, typically one to a few per cent, but we suspect that systematic errors with the photometry and isochrone models limit the accuracy of these measurements to $\sim 5\%$.
 \label{tbl:clusterparams}}
@@
 The discovery of \clustername\ provides a critical distance constraint to the LA and will aid future Magellanic system and Milky Way modeling efforts.
-It also provides an opportunity to study star formation in a unique environment (i.e., low gas density and low metallicity), unlike that of the Milky Way disk or any other cluster-forming region.
+It also provides an opportunity to study star formation in a unique environment (i.e.
+low gas density, low metallicity, and large velocity), unlike that of the Milky Way disk or any other local cluster-forming region.
 The serendipitous discovery of this cluster is a reminder that the combined value of the \gaia\ data with deep, large-area imaging surveys provides a wealth of information about our Galaxy and stellar halo.

### 2018-11-14 ms.tex
TODOs and some SK comments

@@
+% TODO: before submission
+% - Sergey's comment about the distance prior: to summarize, uniform space density could be very bad if the contaminants are field BHB / WDs.
+% - Arrows in Figure 7 and 8 to point out LA II and "low velocity filaments"
+% - On Figure 8, show ranges of velocities used in Figure 7
+% - Add note to results taht we focus on the larger component of the cluster, but clearly other young stars around, including another small clump. Need more photometric follow-up too!
+% - Draw inferred proper motion as a vector on Figure 1, middle panel
+
 % TODO: after submission?
@@
 % - Make a PGM for this model?
+% - With the PM model, go back and apply it to all stars, not just the blue cut. Gets to Sergey / others request to search for evolved stars
+% - Is the cluster elongated along its orbit?
 
@@
 Given their location in the CMD, these stars must be young.
-We therefore use the brightest \emph{kinematic} member of \clustername\ as an ``anchor'' star:
+We therefore use the brightest \emph{kinematic} member of \clustername\ as an ``anchor'' star: \todo{Specify which star this is! Catalog name?}
 We model every other source in the \decam\ selection region (i.e.
@@
 If it formed unbound, but with an initial size comparable to the present size of the Pleiades, this corresponds to an expansion velocity $\sim 6~\kms$, which would be detectable with precise radial velocity measurements of stars on either side of \clustername.
+\todo{Compare the size with systems in http://adsabs.harvard.edu/abs/2017MNRAS.472.2975M - (see eg their fig 4, 6)}
 
@@
 Note that the densest gas at the longitude of \clustername\ (vertical line) appears to be associated with the lower velocity filaments seen at lower longitudes $L_{\textrm{MS}} \lesssim 60^\circ$, which may be decelerated gas associated with the Magellanic stream.
+\todo{Somewhere state that this is a slice in Mag. latitude}
 }
@@
 
-Ignoring the disk gas (between $V_{\textrm{LSR}} \sim -20$--$20~\kms$ in \figurename~\ref{fig:gasspv}), it seems that there are three qualitatively different line-of-sight velocities that the gas (and plausibly \clustername) could have: $V_{\textrm{LSR}} \approx (60, 110, 230)~\kms$.
+Since the gas distribution in \figurename~\ref{fig:gasspv} shows excess at velocities $V_{\textrm{LSR}} \approx (60, 110, 230)~\km$ near the location of the cluster (ignoring the disk gas between $V_{\textrm{LSR}} \sim -20$--$20~\kms$), it seems that there are three qualitatively different line-of-sight velocities that the gas (and plausibly \clustername) could have.
+%: $V_{\textrm{LSR}} \approx (60, 110, 230)~\kms$.
 If we adopt these velocity measurements as the line-of-sight (LOS) velocity of \clustername, we have measurements of all 6 phase-space components and can compute orbits for the cluster.
@@
 D.L.N thanks Peter Kalberla for making the GASS datacubes available in Magellanic Stream coordinates.
+
+SK is supported by National Science Foundation grant AST-1813881.
 

### 2018-11-14 ms.tex
figures and sergey comments

@@
 % TODO: before submission
-% - Sergey's comment about the distance prior: to summarize, uniform space density could be very bad if the contaminants are field BHB / WDs.
-% - Arrows in Figure 7 and 8 to point out LA II and "low velocity filaments"
-% - On Figure 8, show ranges of velocities used in Figure 7
-% - Add note to results taht we focus on the larger component of the cluster, but clearly other young stars around, including another small clump. Need more photometric follow-up too!
-% - Draw inferred proper motion as a vector on Figure 1, middle panel
 
@@
 % - Is the cluster elongated along its orbit?
+% - Describe the strength of the hierarchical cluster params methodology
+% - Sergey's comment about the distance prior: to summarize, uniform space density could be very bad if the contaminants are field BHB / WDs.
 
@@
 Black markers show only sources in the blue selection polygon shown in the CMD (left panel).
+Arrow (green) indicates the inferred proper motion direction (\sectionname~\ref{sec:pmclean}).
+Subcomponents of the cluster (a and b) are indicated.
 \textbf{Right panel}: Proper motions for all sources in the shown sky region (grey 2D histogram).
@@
 We cross-match the mean sky positions of the groups to locations of local group galaxies \citep{McConnachie:2012} and Milky Way globular clusters \citep[2010 edition;][]{Harris:1996} and filter out all groups that lie within 1 degree of these known objects.
-After these filters, just one group of blue, comoving stars remains at $(\textrm{RA}, \textrm{Dec}) \sim (179, -29)^\circ$.
+After these filters, one group of comoving stars remains at $(\textrm{RA}, \textrm{Dec}) \sim (179, -29)^\circ$.
 
@@
 The \gaia\ data demonstrate the presence of a young, distant, spatially-clustered, and co-moving stellar over-density --- named \clustername\ --- but the \gaia\ photometry is too shallow to resolve anything but the brightest main sequence stars.
+The spatial morphology of the cluster is large on the sky, and interestingly substructured with at least two subcomponents (labeled a and b in \figurename~\ref{fig:cmds}) that are indistinguishable in terms of their proper motions and uncertainties.
 With the \gaia\ data alone, the distance, age, and metallicity of the cluster therefore cannot be determined, as these quantities are degenerate where the main sequence is nearly vertical.
 In the next section, we describe deeper \decam\ imaging obtained over a portion of the cluster.
-
-\clearpage
 
@@
 
-We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on a portion of the cluster discovered using the \gaia\ data (see previous section).
+We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on the ``a'' spatial component of the cluster (see \figurename~\ref{fig:cmds}) discovered using the \gaia\ data (see previous section).
 Observations were obtained with the Dark Energy Camera (DECam) on the CTIO 4m Blanco telescope on UT 2018 May 20 with 3$\times$300s
@@
 To measure the cluster population parameters, we therefore use the deeper photometry from \decam, which provides a clear view of the main sequence of \clustername\ down to stellar masses $M \sim 0.9~\msun$.
+We note that this analysis and the subsequent discussion only considers subregion (a) of \clustername, which dominates the total mass and number of stars in the cluster.
 \figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
@@
 % What is standard isochrone fitting?
+% Added to the TODO's for after submission
 
@@
 Given their location in the CMD, these stars must be young.
-We therefore use the brightest \emph{kinematic} member of \clustername\ as an ``anchor'' star: \todo{Specify which star this is! Catalog name?}
+We therefore use the brightest \emph{kinematic} member of \clustername\ --- \gaia\ source ID 3480046557809199616 --- as an ``anchor'' star:
 We model every other source in the \decam\ selection region (i.e.
@@
 We find that the inferred extinction, $A_V \approx 0.33$, is somewhat larger than the value $A_{V, {\rm SFD}} \approx 0.2$ from the SFD dust map \citep{Schlegel:1998}.
+We note again that, with the \decam\ photometry, we are limited to studying the subcomponent a of \clustername\ --- follow-up imaging of component b (see \figurename~\ref{fig:cmds}) would enable a similar analysis for the full cluster.
 
@@
         $\mean{D}$ & $28.9 \pm 0.1~\kpc$ & Heliocentric distance \\
-        $\mean{\mu_\alpha}$ & $-0.56 \pm TODO~\masyr$ & proper motion in RA\\
-        $\mean{\mu_\delta}$ & $0.47 \pm TODO~\masyr$ & proper motion in Dec\\
+        $\mean{\mu_\alpha}$ & $-0.56 \pm 0.04~\masyr$ & proper motion in RA\\
+        $\mean{\mu_\delta}$ & $0.47 \pm 0.02~\masyr$ & proper motion in Dec\\
         \tableline
@@
 \caption{GASS \hi column density in the region of LA II, shown in three different velocity slices (corresponding to and indicated in each panel).
+The colored rectangles under each velocity label correspond to the colored ranges in \figurename~\ref{fig:gasspv}.
 The coordinate system is the Magellanic stream spherical coordinate system defined in \cite{Nidever:2008}, and the units of $L_{\rm MS}$ and $B_{\rm MS}$ are degrees.
-The colorbar shows the column density of \hi in units of $10^{19}~\textrm{atoms}~\textrm{cm}^{-2}$.
-The red circle marks the position of \clustername.}
+The horizontal colorbar shows the column density of \hi in units of $10^{19}~\textrm{atoms}~\textrm{cm}^{-2}$.
+The open circle (green) marks the position of \clustername, and the feature commonly attributed to the LA is indicated in the top panel.}
 \label{fig:gass_maps}
@@
 \includegraphics[width=8cm]{figures/gass_vlsrmlon.pdf}
-\caption{The position-velocity diagram of GASS \hi Gaussian centers in the same region as \figurename~\ref{fig:gass_maps}, showing the line-of-sight velocity (in the local standard of rest frame) of gas near \clustername.
+\caption{The position-velocity diagram of GASS \hi Gaussian centers in a slice of Magellanic latitudes (indicated) in the same region as \figurename~\ref{fig:gass_maps}, showing the line-of-sight velocity (in the local standard of rest frame) of gas near \clustername.
+The colored rectangles (red, orange, yellow) indicate the three velocity slices used in \figurename~\ref{fig:gass_maps}.
 Here the colorbar shows the gas density in units of $10^{18}~\textrm{atoms}~\textrm{cm}^{-2}\,\textrm{deg}$.
 Note that the densest gas at the longitude of \clustername\ (vertical line) appears to be associated with the lower velocity filaments seen at lower longitudes $L_{\textrm{MS}} \lesssim 60^\circ$, which may be decelerated gas associated with the Magellanic stream.
-\todo{Somewhere state that this is a slice in Mag. latitude}
 }
@@
 \figurename~\ref{fig:gass_maps} shows the \hi column density of the catalog of Gaussian centers \citep[producted with the techniques and software from][]{Nidever:2008} from the Galactic All Sky Survey \citep[GASS;][]{McClure-Griffiths:2009, Kalberla:2010} in the region around the LA and plotted in the MS coordinate system \citep[$L_{\rm MS}, B_{\rm MS}$;][]{Nidever:2008}.
-The location of \clustername\ is marked (red circle), and the three panels show three different velocity slices (indicated on each panel).
+The location of \clustername\ is marked (green circle), and the three panels show three different velocity slices (indicated on each panel).
 The MS gas is most visible and densest at the highest velocities where the LA II feature is found, around $L_{\rm MS} \lesssim 61^\circ$ and $B_{\rm MS} \sim -12^\circ$, but the lower panels (i.e.
 slower gas) still displays some of the same morphology as the highest velocity slice.
-\yumi{I was confused when I read this for the first time.
-You might want to mention earlier that HI velocities in the LA is measured to be larger than 150 kmc/s.
-Otherwise, the reader who are not familiar with the LA would misinterpret that the highest gas density around \clustername\ is found in the bottom panel.}
 

### 2018-11-14 ms.tex
mackey

@@
 % TODO: after submission?
-% - Split cluster into 2? Price-Whelan 1a and 1b?
 % - discuss Blanco 1: high latitude, similar age, high binary fraction
@@
 At a distance of $\cldist$, \clustername\ spans $\sim 1.5^\circ$, corresponding to a physical size $\sim 700$--$800~\textrm{pc}$.
-If it formed unbound, but with an initial size comparable to the present size of the Pleiades, this corresponds to an expansion velocity $\sim 6~\kms$, which would be detectable with precise radial velocity measurements of stars on either side of \clustername.
-\todo{Compare the size with systems in http://adsabs.harvard.edu/abs/2017MNRAS.472.2975M - (see eg their fig 4, 6)}
+This is more comparable to (but still larger than) recent star formation sites in the Magellanic bridge \citep[e.g.,][]{Mackey:2017}, which likely formed as a result of the violent interaction between the MCs.
+If \clustername\ formed unbound, but with an initial size comparable to the present size of the Pleiades, this corresponds to an expansion velocity $\sim 6~\kms$, which would be detectable with precise radial velocity measurements of stars on either side of \clustername.
 
@@
 
-\section{Conclusions} \label{sec:conclusion}
+\section{Summary} \label{sec:conclusion}
 

### 2018-11-14 ms.tex
apw edits

@@
 
-We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association in the Milky Way halo: \clustername.
+We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association in the Milky Way halo.
 From isochrone fitting to follow-up \decam\ imaging of the cluster, we also measure its distance, $D \approx \cldist$.
@@
 At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with Milky Way disk.
-The estimated age of \clustername\ is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by the last disk midplane passage, which occurred at a Galactocentric radius $R \approx 30~\kpc$.
+The estimated age of the cluster is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by the last disk midplane passage at a Galactocentric radius $R \approx 30~\kpc$.
 However, most details of this idea remain a mystery: the Magellanic stream has low column density, the Milky Way disk at this large radius has low gas density, and the relative velocity of the leading arm gas and Milky Way gas is large.
@@
 Surprisingly, this group appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
-The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions, respectively, of all stars in this sky region (grey background density), and only stars in the CMD selection polygon as black markers.
+The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions of all stars in this sky region (grey background density), and only stars in the CMD selection polygon (black markers).
 
-The \gaia\ data demonstrate the presence of a young, distant, spatially-clustered, and co-moving stellar over-density --- named \clustername\ --- but the \gaia\ photometry is too shallow to resolve anything but the brightest main sequence stars.
+The \gaia\ data reveal the presence of a young, distant, spatially-clustered, and co-moving stellar over-density --- named \clustername\ --- but the \gaia\ photometry is too shallow to resolve anything but the brightest main sequence stars.
 The spatial morphology of the cluster is large on the sky, and interestingly substructured with at least two subcomponents (labeled a and b in \figurename~\ref{fig:cmds}) that are indistinguishable in terms of their proper motions and uncertainties.
-With the \gaia\ data alone, the distance, age, and metallicity of the cluster therefore cannot be determined, as these quantities are degenerate where the main sequence is nearly vertical.
+With the \gaia\ data alone, the distance, age, and metallicity of the cluster  cannot be determined, as these quantities are degenerate where the main sequence is nearly vertical.
 In the next section, we describe deeper \decam\ imaging obtained over a portion of the cluster.
@@
 \figurename~\ref{fig:decam-field} shows the sky positions of the \gaia\ CMD-selected sources (black markers; see same in middle panel, \figurename~\ref{fig:cmds}), along with point sources identified in the $g$-band data obtained with \decam: sources in control fields are shown as red markers, and sources in cluster fields are shown as blue markers.
-We note that the smaller over-density located northeast of the \decam\ field was not followed up in this work.
+We note that the smaller over-density located northeast of the \decam\ field, component b (see \figurename~\ref{fig:cmds}), was not followed up in this work.
 
@@
 The control fields are designed to, together, have the same total area as the cluster field, and were chosen to have similar latitudes as the cluster field in the Magellanic stream coordinate system \citep{Nidever:2008}.
-We assume that the background density in the cluster field is equivalent to the average background density of the join control fields.
+We assume that the background density in the cluster field is equivalent to the average background density of the joint control fields.
 From visual inspection of the CMDs of the control fields, we do not see any significant clustered over-density and therefore assume that these fields are dominated by the background stellar density.
@@
 \figurename~\ref{fig:gasspv} shows the velocity of gas in this region (all longitudes, but near $B_{\rm MS} \sim -13^\circ$) as a function of $L_{\rm MS}$.
-Here, the longitude of \clustername\ is marked as the vertical (red) line.
+Here, the longitude of \clustername\ is marked as the dashed vertical (green) line.
 The LA II feature is again visible as the $V_{\textrm{LSR}} > 200~\kms$ filament of gas at $L_{\rm MS} \lesssim 60^\circ$ (and a faint extension near $L_{\rm MS} \sim 65^\circ$), but two other prominent filaments with similar morphologies are apparent at lower velocities $V_{\textrm{LSR}} \sim 60~\kms$ and $V_{\textrm{LSR}} \sim 100~\kms$ from $L_{\rm MS} \lesssim 65^\circ$.
+
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=0.9\textwidth]{figures/orbits.pdf}
+\caption{The past orbit of \clustername in Galactocentric Cartesian coordinates, computed by assuming a line-of-sight velocity equal to each of three different possible gas  filaments in the LA II region of the MS (as indicated in right panel).
+In these coordinates, the Sun is at $(x, y, z) = (-8.1, 0, 0)~\kpc$, and the present-day locations of \clustername\ (filled black marker) and the LMC (open black marker) are indicated.
+The time at each point in the orbits is indicated by the colorbar, with the darkest regions corresponding to $t = -130~\textrm{Myr}$, the inferred age of \clustername.
+The past and future orbit of the LMC are shown as the colored line and dashed line, respectively.
+}
+\label{fig:orbits}
+\end{figure*}
 
@@
 
-\begin{figure*}[ht!]
-\centering
-\includegraphics[width=0.9\textwidth]{figures/orbits.pdf}
-\caption{The past orbit of \clustername in Galactocentric Cartesian coordinates, computed by assuming a line-of-sight velocity equal to each of three different possible gas  filaments in the LA II region of the MS (as indicated in right panel).
-In these coordinates, the Sun is at $(x, y, z) = (-8.1, 0, 0)~\kpc$, and the present-day locations of \clustername\ (filled black marker) and the LMC (open black marker) are indicated.
-The time at each point in the orbits is indicated by the colorbar, with the darkest regions corresponding to $t = -130~\textrm{Myr}$, the inferred age of \clustername.
-The past and future orbit of the LMC are shown as the colored line and dashed line, respectively.
-}
-\label{fig:orbits}
-\end{figure*}
-
-Since the gas distribution in \figurename~\ref{fig:gasspv} shows excess at velocities $V_{\textrm{LSR}} \approx (60, 110, 230)~\km$ near the location of the cluster (ignoring the disk gas between $V_{\textrm{LSR}} \sim -20$--$20~\kms$), it seems that there are three qualitatively different line-of-sight velocities that the gas (and plausibly \clustername) could have.
+Since the gas distribution in \figurename~\ref{fig:gasspv} shows excess at velocities $V_{\textrm{LSR}} \approx (60, 110, 230)~\kms$ near the location of the cluster (ignoring the disk gas between $V_{\textrm{LSR}} \sim -20$--$20~\kms$), it seems that there are three qualitatively different line-of-sight velocities that the gas (and plausibly \clustername) could have.
 %: $V_{\textrm{LSR}} \approx (60, 110, 230)~\kms$.
@@
 We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername\ --- with an age $\tau \approx \clage$, heliocentric distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$.
-At its present-day sky position, and at large distances, all significant quantities of \hi are associated with the LA and thus it plausibly formed from MS gas.
+At its present-day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic stream, and thus it plausibly formed from this gas.
 The age of the cluster is broadly consistent with the time it would have most recently crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
-Previous studies have detected young stars in the LA and in the periphery of the LMC \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire young star cluster has been detected so far.% from the Clouds.
+Previous studies have detected young stars in the leading arm and in the periphery of the LMC \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire young star cluster has been detected so far from the Clouds.
 
-The discovery of \clustername\ provides a critical distance constraint to the LA and will aid future Magellanic system and Milky Way modeling efforts.
+The discovery of \clustername\ provides a critical distance constraint to the leading arm Magellanic stream and will aid future Magellanic system and Milky Way modeling efforts.
 It also provides an opportunity to study star formation in a unique environment (i.e.

### 2018-11-14 ms.tex
oh

@@
 Cliff Johnson (Northwestern),
+Semyeong Oh (Cambridge),
 Ekta Patel (Arizona),

### 2019-05-09 ms.tex
add camargo refs

@@
 % - Sergey's comment about the distance prior: to summarize, uniform space density could be very bad if the contaminants are field BHB / WDs.
+% - https://ui.adsabs.harvard.edu/#abs/2008ApJ...673L.143M/abstract
 
@@
 % Edits
+\newcommand{\changes}[1]{{\ \color{red}{\textbf{#1}\ }}}
 \newcommand{\yumi}[1]{{\ \color{purple}{\textbf{Yumi: #1}\ }}}
@@
 
-We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association in the Milky Way halo.
-From isochrone fitting to follow-up \decam\ imaging of the cluster, we also measure its distance, $D \approx \cldist$.
+We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association at a heliocentric distance $D \approx \cldist$, placing it far into the Milky Way halo.
 At its present Galactocentric position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center on the other side of the Milky Way disk.
 If we assume that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the leading arm of the Magellanic stream.
-At this location relative to the LMC, the measured distance is inconsistent with predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with Milky Way disk.
-The estimated age of the cluster is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by the last disk midplane passage at a Galactocentric radius $R \approx 30~\kpc$.
-However, most details of this idea remain a mystery: the Magellanic stream has low column density, the Milky Way disk at this large radius has low gas density, and the relative velocity of the leading arm gas and Milky Way gas is large.
+The measured distance is inconsistent with stream predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with Milky Way disk.
+The estimated age of the cluster is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by its the last disk midplane passage.
+% at a Galactocentric radius $R \approx 30~\kpc$.
+Most details of this idea remain a puzzle: the Magellanic stream has low column density, the Milky Way disk at this large radius has low gas density, and the relative velocity of the leading arm gas and Milky Way gas is large.
 However it formed, the discovery of a young stellar cluster in the Milky Way halo presents an interesting opportunity for study.
+This cluster was discovered with \gaia\ astrometry and photometry alone, but folow-up \decam\ photometry was crucial for measuring its properties.
 \end{abstract}
@@
 
-The halo of the Milky Way is typically characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
-This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted early on in the formation of the Galaxy \citep[massive dwarf galaxies][]{Deason:2015, Fiorentino:2015}.
+The \changes{distant stellar} halo of the Milky Way is typically characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
+\changes{While there is some evidence that the inner stellar halo (within $\lesssim 5~\kpc$ of the sun) could contain young, embedded clusters at high Galactic latitude (e.g., \cite{Camargo:2015, Camargo:2016}; however, these may not be real \cite{Turner:2017}), the typical old age of the stellar halo} is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted early on in the formation of the Galaxy \citep[massive dwarf galaxies][]{Deason:2015, Fiorentino:2015}.
 It is thought that these systems came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.

### 2019-05-09 ms.tex
update figures and text

@@
 \figurename~\ref{fig:cmds} shows the \gaia\ data for this region:
-The left panel shows the \gaia\ color-magnitude diagram, extinction corrected following the procedure used in \citet{Danielski:2018}, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}.
+The left panel shows the \gaia\ color-magnitude diagram, extinction corrected following the procedure used in \citet{Danielski:2018} \changes{and the coefficients from \citet{Babusiaux:2018}}, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}.
 Surprisingly, this group appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
@@
 While the \gaia\ data provide exquisite astrometric data for the brightest members of \clustername, constraints on the stellar population from the \gaia\ data alone are limited by degeneracies in the mapping from the color-magnitude diagram to stellar parameters.
+\changes{In addition, uncertainty in the \gaia\ passbands can cause significant differences in \gaia\ \bprp\ color for very blue sources \citep{MAW:2018}.}
 To measure the cluster population parameters, we therefore use the deeper photometry from \decam, which provides a clear view of the main sequence of \clustername\ down to stellar masses $M \sim 0.9~\msun$.

### 2019-05-09 ms.tex
add uncertainties and update values

@@
 
-\newcommand{\clage}{\ensuremath{130~\textrm{Myr}}}
-\newcommand{\clfeh}{\ensuremath{-1.1}}
-\newcommand{\cldist}{\ensuremath{29~\textrm{kpc}}}
+\newcommand{\clage}{\ensuremath{116~\textrm{Myr}}}
+\newcommand{\clfeh}{\ensuremath{-1.14}}
+\newcommand{\cldist}{\ensuremath{28.7~\textrm{kpc}}}
+
+\newcommand{\clageerr}{\ensuremath{116 \pm 7~\textrm{Myr}}}
+\newcommand{\clfeherr}{\ensuremath{-1.14 \pm 0.05}}
+\newcommand{\cldisterr}{\ensuremath{28.7 \pm 0.4~\textrm{kpc}}}
+\newcommand{\claverr}{\ensuremath{0.21 \pm 0.02}}
 
@@
 Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
-We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx \clage$, distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
-We find that the inferred extinction, $A_V \approx 0.33$, is somewhat larger than the value $A_{V, {\rm SFD}} \approx 0.2$ from the SFD dust map \citep{Schlegel:1998}.
+\changes{We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau = \clageerr$, distance $D = \cldisterr$, and metallicity $\feh = \clfeherr$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
+We find that the inferred extinction, $A_V = \claverr$, is consistent with the value $A_{V, {\rm SFD}} \approx 0.2$ from the (revised) SFD dust map \citep{Schlegel:1998, Schlafly:2011}.}
 We note again that, with the \decam\ photometry, we are limited to studying the subcomponent a of \clustername\ --- follow-up imaging of component b (see \figurename~\ref{fig:cmds}) would enable a similar analysis for the full cluster.
@@
         $\mean{\delta}$ & $-29.4^\circ$ & declination \\
-        $\mean{D}$ & $28.9 \pm 0.1~\kpc$ & Heliocentric distance \\
+        $\mean{D}$ & $28.7 \pm 0.4~\kpc$ & Heliocentric distance \\
         $\mean{\mu_\alpha}$ & $-0.56 \pm 0.04~\masyr$ & proper motion in RA\\
@@
         \tableline
-        $\tau$ & $130 \pm 6~\textrm{Myr}$ & age \\
+        $\tau$ & $116 \pm 7~\textrm{Myr}$ & age \\
         $M$ & $1200~\msun$ & total stellar mass \\
-        $\feh$ & $-1.10 \pm 0.02$ & metallicity \\
+        $\feh$ & $-1.14 \pm 0.05$ & metallicity \\
         \tableline
-        $A_V$ & $0.33 \pm 0.02$ & extinction \\
+        $A_V$ & $0.21 \pm 0.02$ & extinction \\
         \toprule

### 2019-05-09 ms.tex
stddev

@@
 Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
-\changes{We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau = \clageerr$, distance $D = \cldisterr$, and metallicity $\feh = \clfeherr$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
+\changes{We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values and standard deviations of age $\tau = \clageerr$, distance $D = \cldisterr$, and metallicity $\feh = \clfeherr$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
 We find that the inferred extinction, $A_V = \claverr$, is consistent with the value $A_{V, {\rm SFD}} \approx 0.2$ from the (revised) SFD dust map \citep{Schlegel:1998, Schlafly:2011}.}

### 2019-05-09 ms.tex
addressing more todos

@@
 \changes{We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values and standard deviations of age $\tau = \clageerr$, distance $D = \cldisterr$, and metallicity $\feh = \clfeherr$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
-We find that the inferred extinction, $A_V = \claverr$, is consistent with the value $A_{V, {\rm SFD}} \approx 0.2$ from the (revised) SFD dust map \citep{Schlegel:1998, Schlafly:2011}.}
+We find that the inferred extinction, $A_V = \claverr$, is consistent with the value $A_{V, {\rm SFD}} \approx 0.2$ from the (recalibrated) SFD dust map \citep{Schlegel:1998, Schlafly:2011}.}
 We note again that, with the \decam\ photometry, we are limited to studying the subcomponent a of \clustername\ --- follow-up imaging of component b (see \figurename~\ref{fig:cmds}) would enable a similar analysis for the full cluster.
@@
 Also plotted in \figurename~\ref{fig:hierarch-iso} is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample: The abundance of sources between the nominal isochrone and the binary sequence highlights the fact that the cluster may contain a significant number of binary or multiple star systems, but we leave a detailed study of multiplicity to future work.
+\changes{We note that, similar to young open clusters in the Milky Way disk \citep[e.g.,][]{Babusiaux:2018}, the bluest stars in the CMD have more apparent scatter than the lower main sequence.
+This is likely a combination of many things that are not addressed in this work, such as binarity, convective core overshooting \citep[e.g.,][]{Yang:2017, Johnston:2019}, or an intrinsic spread in stellar parameters.}
 

### 2019-05-09 ms.tex
photo calib

@@
 % Edits
-\newcommand{\changes}[1]{{\ \color{red}{\textbf{#1}\ }}}
+\newcommand{\changes}[1]{{\ \color{black}{\textbf{#1}\ }}}
 \newcommand{\yumi}[1]{{\ \color{purple}{\textbf{Yumi: #1}\ }}}
@@
 
-We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association at a heliocentric distance $D \approx \cldist$, placing it far into the Milky Way halo.
+\changes{We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association at a heliocentric distance $D \approx \cldist$, placing it far into the Milky Way halo.}
 At its present Galactocentric position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center on the other side of the Milky Way disk.
@@
 Forced PSF photometry was performed with the PHOTRED pipeline \citep{Nidever:2017} which uses the DAOPHOT ALLSTAR \citep{Stetson:1987} and ALLFRAME \citep{Stetson:1994} suite of programs.
-The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for global zero-point and color-terms in each band.
+
+\changes{The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and
+with SkyMapper \citep{Wolf:2018} for the u-band observations.
+We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for u-band) to calibrate the photometry.
+The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
+The larger scatter in u-band---much larger than the uncertainty in the individual photometry---is due to the large differences in the DECam and SkyMapper u-band passbands.}
 
@@
 Later, we use photometry in the sub-region of the cluster fields identified by the dashed rectangle to infer the cluster parameters.
+
+\begin{center}
+\begin{deluxetable}{ccrrr}
+\tablecaption{DECam Photometric Transformation Equations}
+\tablecolumns{5}
+\tablewidth{400pt}
+\tablehead{
+\colhead{Band} & \colhead{Color} & \colhead{Zero-point term} & \colhead{Color term} & \colhead{RMS}
+}
+\startdata
+$u$  &  $g-i$ & 2.17820 $\pm$   0.016 &     \nodata  & 0.164 \\
+$g$  & $g-r$ & $-$0.052868 $\pm$  0.0068  &     $-$0.034937 $\pm$   0.0051  &  0.028 \\
+$i$   &  $i-z$ & $-$0.246645 $\pm$  0.0011 &     $-$ -0.07379 $\pm$   0.00069  &  0.028  \\
+
+\enddata
+\label{table_transphot}
+\end{deluxetable}
+\end{center}
 

### 2019-05-09 ms.tex
table

@@
 with SkyMapper \citep{Wolf:2018} for the u-band observations.
-We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for u-band) to calibrate the photometry.
+We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for u-band) to calibrate the photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
 The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
@@
 $u$  &  $g-i$ & 2.17820 $\pm$   0.016 &     \nodata  & 0.164 \\
-$g$  & $g-r$ & $-$0.052868 $\pm$  0.0068  &     $-$0.034937 $\pm$   0.0051  &  0.028 \\
-$i$   &  $i-z$ & $-$0.246645 $\pm$  0.0011 &     $-$ -0.07379 $\pm$   0.00069  &  0.028  \\
-
+$g$  & $g-r$ & $-0.052868 \pm  0.0068$  &     $-0.034937 \pm 0.0051$  &  0.028 \\
+$i$   &  $i-z$ & $-0.246645 \pm 0.0011$ &     $-0.07379 \pm 0.00069$  &  0.028
 \enddata
-\label{table_transphot}
+\label{tbl:transphot}
 \end{deluxetable}

### 2019-05-09 ms.tex
more comments

@@
 \begin{deluxetable}{ccrrr}
-\tablecaption{DECam Photometric Transformation Equations}
+\tablecaption{DECam Photometric Transformation Equations\label{tbl:transphot}}
 \tablecolumns{5}
@@
 \enddata
-\label{tbl:transphot}
 \end{deluxetable}
@@
 \figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
-We use the $g$- and $i$-band photometry for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
+We use the $g$- and $i$-band photometry \changes{(and $u$-band, though only the brightest $\sim$15 cluster field members are robustly detected)} for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
 To summarize our methodology, we first generate independent posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture model of the cluster and a background population.

### 2019-05-15 ms.tex
david n suggestions

@@
 
-\changes{The photometry was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and
-with SkyMapper \citep{Wolf:2018} for the u-band observations.
-We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for u-band) to calibrate the photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
+\changes{The instrumental photometry (i.e., $-2.5\log(\texttm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
+We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for u-band) to derive color transformations relating our instrumental DECam photometry to calibrated SkyMapper u- and PS1 grizy photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
+We apply this color transformation to put our photometry on the SkyMapper/PS1 system, enabling us to treat this photometry as if it were PS1/SkyMapper photometry in the isochrone modeling.
 The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
@@
 \figurename~\ref{fig:decam-cmd} shows \decam\ color-magnitude diagrams for the control and cluster sub-fields (the magnitudes here are not extinction-corrected).
-We find that the $u$-band data were too shallow to be useful for this work, so restrict the further analysis in this work to the $g$- and $i$-bands.
+% We find that the $u$-band data were too shallow to be useful for this work, so restrict the further analysis in this work to the $g$- and $i$-bands.
 The blue comoving group, \clustername, identified in \sectionname~\ref{sec:discovery} using \gaia\ data alone shows up as a clear young main sequence in the cluster fields (right panel of \figurename~\ref{fig:decam-cmd}).
@@
 \tablehead{
-\colhead{Band} & \colhead{Color} & \colhead{Zero-point term} & \colhead{Color term} & \colhead{RMS}
+\colhead{Band} & \colhead{Color} & \colhead{Zero-point term} & \colhead{Color term}
 }
 \startdata
-$u$  &  $g-i$ & 2.17820 $\pm$   0.016 &     \nodata  & 0.164 \\
-$g$  & $g-r$ & $-0.052868 \pm  0.0068$  &     $-0.034937 \pm 0.0051$  &  0.028 \\
-$i$   &  $i-z$ & $-0.246645 \pm 0.0011$ &     $-0.07379 \pm 0.00069$  &  0.028
+% $u$  &  \nodata & $2.178 \pm  0.016$ &     \nodata \\
+% $g$  & $g-r$ & $-0.05287 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
+% $i$   &  $i-z$ & $-0.24665 \pm 0.0011$ &     $-0.07379 \pm 0.00069$
+$u$  &  \nodata & $27.178 \pm  0.016$ &     \nodata \\
+$g$  & $g-r$ & $24.9471 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
+$i$   &  $i-z$ & $24.7534 \pm 0.0011$ &     $-0.07379 \pm 0.0007$
 \enddata
@@
 We therefore take a closer look at the \hi gas in the vicinity of \clustername\ to assess its possible relation to the MS.
-While no bulk metallicity measurements exist for the LA gas, recent measurements of oxygen and silicon abundances suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2018, Richter:2018}.
+While no bulk metallicity measurements exist for the LA gas, recent measurements of oxygen and silicon abundances ($\[O/H\] \sim -1$) suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2018, Richter:2018}.
 If \clustername\ formed from this gas, we would then expect that the stellar metallicity should be similar to young stars in the SMC.

### 2019-05-24 ms.tex
more updates

@@
 
-\newcommand{\clage}{\ensuremath{116~\textrm{Myr}}}
+\newcommand{\clage}{\ensuremath{117~\textrm{Myr}}}
 \newcommand{\clfeh}{\ensuremath{-1.14}}
@@
 
-\newcommand{\clageerr}{\ensuremath{116 \pm 7~\textrm{Myr}}}
+\newcommand{\clageerr}{\ensuremath{117 \pm 23~\textrm{Myr}}}
 \newcommand{\clfeherr}{\ensuremath{-1.14 \pm 0.05}}
-\newcommand{\cldisterr}{\ensuremath{28.7 \pm 0.4~\textrm{kpc}}}
-\newcommand{\claverr}{\ensuremath{0.21 \pm 0.02}}
+\newcommand{\cldisterr}{\ensuremath{28.7 \pm 0.5~\textrm{kpc}}}
+\newcommand{\claverr}{\ensuremath{0.205 \pm 0.011}}
 
@@
 Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC \citep{Putman:1998}, but outer features of the LMC appear to lead directly into the LA I feature \citep{Nidever:2008}.
-Recent chemical abundance measurements along several sight-lines passing through the LA again support an SMC origin for the gas \citep{Fox:2018, Richter:2018}.
+Recent chemical abundance measurements along several sight-lines passing through the LA again support an SMC origin for the gas \citep{Fox:2013, Fox:2018, Richter:2018}.
 Whatever the origin of the LA gas, it is clear that tidal stripping by the Milky Way is required to form the LA \citep{Nidever:2008, Besla:2012}.
@@
 
-\changes{The instrumental photometry (i.e., $-2.5\log(\texttm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
-We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for u-band) to derive color transformations relating our instrumental DECam photometry to calibrated SkyMapper u- and PS1 grizy photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
-We apply this color transformation to put our photometry on the SkyMapper/PS1 system, enabling us to treat this photometry as if it were PS1/SkyMapper photometry in the isochrone modeling.
+\changes{The instrumental photometry (i.e., $-2.5\log(\textrm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
+We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for the u-band) to derive color transformations relating our instrumental DECam photometry to calibrated PS1 grizy and SkyMapper u-band photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
+We apply this color transformation to the instrumental photometry---including a constant 25 mag offset applied by DAOPHOT and an offset by $2.5\,\log{t_{\rm exp}}$ given the exposure time $t_{\rm exp}$---to put our photometry on the PS1/DECam system.
+This calibration enables us to treat the photometry as if it were PS1 (g- and i-band) and DECam (u-band) photometry in the isochrone modeling described below.
 The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
-The larger scatter in u-band---much larger than the uncertainty in the individual photometry---is due to the large differences in the DECam and SkyMapper u-band passbands.}
+The larger scatter in u-band---larger than the uncertainty in the individual photometry---is due to the significant differences between the DECam and SkyMapper u-band passbands.
+}
 
@@
 \begin{deluxetable}{ccrrr}
-\tablecaption{DECam Photometric Transformation Equations\label{tbl:transphot}}
+\tablecaption{DECam Photometric Transformation\label{tbl:transphot}}
 \tablecolumns{5}
@@
 % $i$   &  $i-z$ & $-0.24665 \pm 0.0011$ &     $-0.07379 \pm 0.00069$
-$u$  &  \nodata & $27.178 \pm  0.016$ &     \nodata \\
-$g$  & $g-r$ & $24.9471 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
-$i$   &  $i-z$ & $24.7534 \pm 0.0011$ &     $-0.07379 \pm 0.0007$
+$u_{\rm DECam}$  &  \nodata & $27.178 \pm  0.016$ &     \nodata \\
+$g_{\rm PS1}$  & $g_{\rm inst.}-i_{\rm inst.}$ & $24.9471 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
+$i_{\rm PS1}$   &  $g_{\rm inst.}-i_{\rm inst.}$ & $24.7534 \pm 0.0011$ &     $-0.07379 \pm 0.0007$
 \enddata
@@
 We therefore take a closer look at the \hi gas in the vicinity of \clustername\ to assess its possible relation to the MS.
-While no bulk metallicity measurements exist for the LA gas, recent measurements of oxygen and silicon abundances ($\[O/H\] \sim -1$) suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2018, Richter:2018}.
+While no bulk metallicity measurements exist for the LA gas, recent measurements of oxygen and silicon abundances ($[\textrm{O}/\textrm{H}] \sim -1$) suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2013, Fox:2018, Richter:2018}.
 If \clustername\ formed from this gas, we would then expect that the stellar metallicity should be similar to young stars in the SMC.

### 2019-05-24 ms.tex
eddie comments

@@
 \includegraphics[width=0.45\textwidth]{figures/DECam-field.pdf}
-\caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ $g$-band follow up (blue and red markers).
+\caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ g-band follow up (blue and red markers).
 Red markers show sources in the \decam\ field used as control sources, and blue markers show sources used as cluster member candidates.}
@@
 
-We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on the ``a'' spatial component of the cluster (see \figurename~\ref{fig:cmds}) discovered using the \gaia\ data (see previous section).
+We obtained \decam\ u-, g-, and i-band imaging of a single field centered on the ``a'' spatial component of the cluster (see \figurename~\ref{fig:cmds}) discovered using the \gaia\ data (see previous section).
 Observations were obtained with the Dark Energy Camera (DECam) on the CTIO 4m Blanco telescope on UT 2018 May 20 with 3$\times$300s
@@
 \changes{The instrumental photometry (i.e., $-2.5\log(\textrm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
-We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for the u-band) to derive color transformations relating our instrumental DECam photometry to calibrated PS1 grizy and SkyMapper u-band photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
-We apply this color transformation to the instrumental photometry---including a constant 25 mag offset applied by DAOPHOT and an offset by $2.5\,\log{t_{\rm exp}}$ given the exposure time $t_{\rm exp}$---to put our photometry on the PS1/DECam system.
+We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was used for the u-band) to derive color transformations relating our instrumental DECam photometry to calibrated PS1 grizy and SkyMapper u-band photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
+We apply this color transformation to the instrumental photometry to put our photometry on the PS1/DECam system.
+% ---including a constant 25 mag offset applied by DAOPHOT and an offset by $2.5\,\log{t_{\rm exp}}$ given the exposure time $t_{\rm exp}$---
 This calibration enables us to treat the photometry as if it were PS1 (g- and i-band) and DECam (u-band) photometry in the isochrone modeling described below.
 The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
-The larger scatter in u-band---larger than the uncertainty in the individual photometry---is due to the significant differences between the DECam and SkyMapper u-band passbands.
+The larger scatter in u-band---larger than the uncertainty in the individual photometry---is due to the significant differences between the DECam and SkyMapper u-band passbands as well as the u-band's sensitivity to both temperature and metallicity.
 }
 
-\figurename~\ref{fig:decam-field} shows the sky positions of the \gaia\ CMD-selected sources (black markers; see same in middle panel, \figurename~\ref{fig:cmds}), along with point sources identified in the $g$-band data obtained with \decam: sources in control fields are shown as red markers, and sources in cluster fields are shown as blue markers.
+\figurename~\ref{fig:decam-field} shows the sky positions of the \gaia\ CMD-selected sources (black markers; see same in middle panel, \figurename~\ref{fig:cmds}), along with point sources identified in the g-band data obtained with \decam: sources in control fields are shown as red markers, and sources in cluster fields are shown as blue markers.
 We note that the smaller over-density located northeast of the \decam\ field, component b (see \figurename~\ref{fig:cmds}), was not followed up in this work.
@@
 \includegraphics[width=0.45\textwidth]{figures/DECam-cmd.pdf}
-\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
+\caption{\decam\ $g-i$ versus g color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
 Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
@@
 \startdata
-% $u$  &  \nodata & $2.178 \pm  0.016$ &     \nodata \\
-% $g$  & $g-r$ & $-0.05287 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
-% $i$   &  $i-z$ & $-0.24665 \pm 0.0011$ &     $-0.07379 \pm 0.00069$
 $u_{\rm DECam}$  &  \nodata & $27.178 \pm  0.016$ &     \nodata \\
@@
 We note that this analysis and the subsequent discussion only considers subregion (a) of \clustername, which dominates the total mass and number of stars in the cluster.
-\figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
-We use the $g$- and $i$-band photometry \changes{(and $u$-band, though only the brightest $\sim$15 cluster field members are robustly detected)} for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
+\figurename~\ref{fig:decam-cmd} shows the \decam\ g- and i-band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
+We use the g- and i-band photometry \changes{(and u-band, though only the brightest $\sim$15 cluster field members are robustly detected)} for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
 To summarize our methodology, we first generate independent posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture model of the cluster and a background population.

### 2019-05-24 ms.tex
a few minor tweaks

@@
 \changes{The instrumental photometry (i.e., $-2.5\log(\textrm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
-We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was used for the u-band) to derive color transformations relating our instrumental DECam photometry to calibrated PS1 grizy and SkyMapper u-band photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
+We use a robust linear fit to cross-matched sources (that appear in both PS1/SkyMapper and our observations) to obtain a zero-point and (for g- and i-band) color-term to derive color transformations relating our instrumental DECam photometry to calibrated PS1 grizy and SkyMapper u-band photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
 We apply this color transformation to the instrumental photometry to put our photometry on the PS1/DECam system.
@@
 The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
-The larger scatter in u-band---larger than the uncertainty in the individual photometry---is due to the significant differences between the DECam and SkyMapper u-band passbands as well as the u-band's sensitivity to both temperature and metallicity.
+The larger scatter in u-band---larger than the uncertainty in the individual photometric measurements---is due to the significant differences between the DECam and SkyMapper u-band passbands as well as the u-band's sensitivity to both temperature and metallicity.
 }

### 2019-05-24 ms.tex
typo
typos

@@
 \changes{We report the discovery of a young ($\tau \sim \clage$), low-mass ($M \sim 1200~\msun$), metal-poor ($\feh \sim \clfeh$) stellar association at a heliocentric distance $D \approx \cldist$, placing it far into the Milky Way halo.}
-At its present Galactocentric position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center on the other side of the Milky Way disk.
+At its present Galactocentric position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center on the other side of the Milky Way (MW) disk.
 If we assume that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the leading arm of the Magellanic stream.
-The measured distance is inconsistent with stream predictions from models of the LMC/SMC interaction and infall into the Milky Way that do not account for ram pressure and gas interaction with Milky Way disk.
-The estimated age of the cluster is consistent with the time of last passage of the leading arm gas through the Galactic midplane, and we therefore speculate that this star-formation event was triggered by its the last disk midplane passage.
+The measured distance is inconsistent with Magellanic stream model predictions that do not account for ram pressure and gas interaction with the MW disk.
+The estimated age of the cluster is consistent with the time of last passage of the leading arm gas through the Galactic midplane; We therefore speculate that this star-formation event was triggered by its last disk midplane passage.
 % at a Galactocentric radius $R \approx 30~\kpc$.
-Most details of this idea remain a puzzle: the Magellanic stream has low column density, the Milky Way disk at this large radius has low gas density, and the relative velocity of the leading arm gas and Milky Way gas is large.
-However it formed, the discovery of a young stellar cluster in the Milky Way halo presents an interesting opportunity for study.
-This cluster was discovered with \gaia\ astrometry and photometry alone, but folow-up \decam\ photometry was crucial for measuring its properties.
+Most details of this idea remain a puzzle: the Magellanic stream has low column density, the MW disk at large radii has low gas density, and the relative velocity of the leading arm and MW gas is large.
+However it formed, the discovery of a young stellar cluster in the MW halo presents an interesting opportunity for study.
+This cluster was discovered with \gaia\ astrometry and photometry alone, but follow-up \decam\ photometry was crucial for measuring its properties.
 \end{abstract}

### 2019-06-25 ms.tex
prep for round two

@@
 % Edits
-\newcommand{\changes}[1]{{\ \color{black}{\textbf{#1}\ }}}
+\newcommand{\changes}[1]{#1}
+\newcommand{\changestwo}[1]{{\ \color{black}{\textbf{#1}\ }}}
 \newcommand{\yumi}[1]{{\ \color{purple}{\textbf{Yumi: #1}\ }}}
@@
 At its present Galactocentric position $(R, z) \sim (23, 15)~\textrm{kpc}$, the association is (on the sky) near the leading arm of the gas stream emanating from the Magellanic cloud system, but is located $\approx 60^\circ$ from the Large Magellanic Cloud (LMC) center on the other side of the Milky Way (MW) disk.
-If we assume that the cluster is co-located with \hi gas in the stream, we directly measure the distance to the leading arm of the Magellanic stream.
+If the cluster is co-located with \hi gas in the stream, we directly measure the distance to the leading arm of the Magellanic stream.
 The measured distance is inconsistent with Magellanic stream model predictions that do not account for ram pressure and gas interaction with the MW disk.
@@
 We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{emcee, Goodman:2010} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
-We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps, after which the chains appear converged.
+We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps, after which the chains appear converged: \changestwo{We compute the Gelman-Rubin \citep{Gelman:1992} convergence diagnostic and find that all chains have $R < 1.1$.}
 We then downsample the resulting chains by taking every 16th sample to preserve closer-to-independent samples, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
@@
 \figurename~\ref{fig:decam-cmd} shows the \decam\ g- and i-band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
-We use the g- and i-band photometry \changes{(and u-band, though only the brightest $\sim$15 cluster field members are robustly detected)} for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
+We use the g- and i-band photometry---\changestwo{and u-band, though only the brightest $\sim$15 cluster field members are robustly detected, however for those sources, the u-band significantly helps to constrain the extinction for the cluster}---for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
 To summarize our methodology, we first generate independent posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture model of the cluster and a background population.
@@
 Here we use 64 walkers and run for an initial 128 steps to burn-in the sampler before running for a final 1024 steps.
+\changestwo{We again compute the Gelman-Rubin \citep{Gelman:1992} convergence diagnostic and find that all chains have $R < 1.1$ and are thus likely converged.}
 \figurename~\ref{fig:hierarch-corner} shows a corner plot with all 1D and 2D marginal posterior probability distributions estimated from the samples.
@@
 
+\subsection{Other possible formation scenarios}
+\label{sec:otherformation}
+
+While the spatial proximity of \clustername\ to LA gas in the Magellanic Stream suggests a tentative connection, radial velocity data for the stars is required to confirm that the velocity of the cluster is consistent with the gas and thereby confirm the connection (Nidever et al., in prep.).
+However, even if the cluster can be confidently, kinematically associated with the LA gas, a number of mysteries would remain.
+First, it is not clear what could have triggered this star formation event, or why this appears to be the only young cluster associated with the LA gas.
+Second, the origin of the LA gas itself is not well understood, and some studies have questioned its connection to the Magellanic Clouds \citep{Tepper:2019}.
+
+Other possible formation scenarios for \clustername\ do not help to resolve these issues.
+One possible alternative scenario is that the \clustername\ birth cloud was unassociated with the MS and instead a lone HVC.
+However, this still raises questions about what triggered the star formation, given that other HVCs in the Milky Way are observed to be devoid of stars (e.g., \citalt{Stark:2015}).
+Another possible origin for \clustername\ is that it formed from gas stripped from a fully-destroyed dwarf galaxy (an unknown satellite of the Magellanic Clouds).
+However, the cluster appears to have a single, very young stellar population, and other, comoving, older stars have not been found associated with the LA in this region.
+
 \section{Summary} \label{sec:conclusion}

### 2019-06-25 ms.tex
cite naomi

@@
-% TODO: before submission
-
 % TODO: after submission?
@@
 % - With the PM model, go back and apply it to all stars, not just the blue cut. Gets to Sergey / others request to search for evolved stars
-% - Is the cluster elongated along its orbit?
 % - Describe the strength of the hierarchical cluster params methodology
 % - Sergey's comment about the distance prior: to summarize, uniform space density could be very bad if the contaminants are field BHB / WDs.
-% - https://ui.adsabs.harvard.edu/#abs/2008ApJ...673L.143M/abstract
 
@@
 The similar filamentary structure in the high and lower velocity gas therefore raises the question: Did the low velocity filaments originate in the MS, but were decelerated through interactions with Milky Way gas?
-This presents a possible formation scenario for \clustername.
+\changestwo{This scenario has been suggested (i.e., that the LA material has interacted with gas in the Galactic disk) based on the kinematics and morphology of a LA HVC \citep{McClure-Griffiths:2008}} and presents a possible formation scenario for \clustername.
 If the cluster formed from the LA gas, and some of the gas interacted with the Milky Way disk, the dynamics of the stars and the gas that interacted would have decoupled as soon as the stars formed.

### 2019-06-25 ms.tex
boom

@@
 % - With the PM model, go back and apply it to all stars, not just the blue cut. Gets to Sergey / others request to search for evolved stars
-% - Describe the strength of the hierarchical cluster params methodology
 % - Sergey's comment about the distance prior: to summarize, uniform space density could be very bad if the contaminants are field BHB / WDs.
@@
 To summarize our methodology, we first generate independent posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture model of the cluster and a background population.
+\changestwo{This methodology is more robust than conventional isochrone-fitting methods that require by-hand fitting of stellar population parameters and naturally propagates uncertainties in the photometry and cluster membership.}
 If you prefer to skip the details, the results of this modeling are presented in \sectionname~\ref{sec:popchars}.

### 2019-06-25 ms.tex
typo

@@
 One possible alternative scenario is that the \clustername\ birth cloud was unassociated with the MS and instead a lone HVC.
-However, this still raises questions about what triggered the star formation, given that other HVCs in the Milky Way are observed to be devoid of stars (e.g., \citalt{Stark:2015}).
+However, this still raises questions about what triggered the star formation, given that other HVCs in the Milky Way are observed to be devoid of stars (e.g., \citealt{Stark:2015}).
 Another possible origin for \clustername\ is that it formed from gas stripped from a fully-destroyed dwarf galaxy (an unknown satellite of the Magellanic Clouds).

### 2019-08-26 ms.tex
round 3

@@
 \newcommand{\changes}[1]{#1}
-\newcommand{\changestwo}[1]{{\ \color{black}{\textbf{#1}\ }}}
+\newcommand{\changestwo}[1]{#1}
+\newcommand{\changesthr}[1]{{\ \color{black}{\textbf{#1}\ }}}
 \newcommand{\yumi}[1]{{\ \color{purple}{\textbf{Yumi: #1}\ }}}
@@
 
-The \changes{distant stellar} halo of the Milky Way is typically characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
-\changes{While there is some evidence that the inner stellar halo (within $\lesssim 5~\kpc$ of the sun) could contain young, embedded clusters at high Galactic latitude (e.g., \cite{Camargo:2015, Camargo:2016}; however, these may not be real \cite{Turner:2017}), the typical old age of the stellar halo} is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted early on in the formation of the Galaxy \citep[massive dwarf galaxies][]{Deason:2015, Fiorentino:2015}.
+The \changes{distant stellar} halo of the Milky Way (i.e.
+far from the disk midplane, $|z| \gtrsim 5~\kpc$) is typically characterized by its old ($\gtrsim 10~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
+% \changes{While there is some evidence that the inner stellar halo (within $\lesssim 5~\kpc$ of the sun) could contain young, embedded clusters at high Galactic latitude (e.g., \cite{Camargo:2015, Camargo:2016}; however, these may not be real \cite{Turner:2017}), t
+The typical old age of the stellar halo is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted early on in the formation of the Galaxy \citep[massive dwarf galaxies][]{Deason:2015, Fiorentino:2015}.
 It is thought that these systems came in with significant gas reservoirs, but were quenched and stripped through collisional processes that heated and dispersed the gas \citep[e.g.,][]{Mayer:2006}, thus preventing immediate star formation in the deposited gas.
@@
 The control fields are designed to, together, have the same total area as the cluster field, and were chosen to have similar latitudes as the cluster field in the Magellanic stream coordinate system \citep{Nidever:2008}.
-We assume that the background density in the cluster field is equivalent to the average background density of the joint control fields.
+We assume that the background density in the cluster field is equivalent to the average background density of the joint control fields: \changesthr{We do not see any gradients or significant differences in the proper motion distribution between these two control fields.}
 From visual inspection of the CMDs of the control fields, we do not see any significant clustered over-density and therefore assume that these fields are dominated by the background stellar density.
@@
 For the young cluster, we find $\bs{x} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
-The proper-motion dispersion is consistent with zero, and is likely unmeasured, because of the proper motion uncertainties; 95\% of the posterior samples have $s < 0.09~\masyr$.
+\changesthr{The proper-motion dispersion is consistent with zero, but is unmeasured: 95\% of the posterior samples have $s < 0.09~\masyr$, indicating that the observed proper motion dispersion is consistent with the proper motion \gaia\ uncertainties, which have minimum and median values of $\sim 0.09~\masyr$ and $\sim 0.4~\masyr$, respectively.}
 \tablename~\ref{tbl:gaiadata} contains a subset of the \gaia\ \DR{2} data for stars in the cluster field, with kinematic membership probabilities determined from this modeling procedure.
@@
 In the hierarchical model, we assume that the stellar parameters of each primary star in the selected region are either drawn from the cluster, or a background (stellar halo) population.
-For the cluster, we assume that the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\bs{\alpha} = (\tau^*, \feh^*, D^*, A_V^*)$ as hyperparameters of the hierarchical inference.
+For the cluster, we assume that the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\bs{\alpha} = (\tau^*, \feh^*, D^*, A_V^*)$ as hyperparameters of the hierarchical inference---\changesthr{that is, we assume that the cluster is a single stellar population (SSP).
+We note that we have run the same hierarchical model allowing for Gaussian spreads in age, metallicity, and distance where we simultaneously infer the variances in each cluster parameter, but we have found that the variances are unconstrained, and we therefore instead treat the cluster as an SSP.}
+
 For the background model, we assume the same priors as specified in \tablename~\ref{tbl:priors}.
@@
 Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
-\changes{We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values and standard deviations of age $\tau = \clageerr$, distance $D = \cldisterr$, and metallicity $\feh = \clfeherr$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
-We find that the inferred extinction, $A_V = \claverr$, is consistent with the value $A_{V, {\rm SFD}} \approx 0.2$ from the (recalibrated) SFD dust map \citep{Schlegel:1998, Schlafly:2011}.}
+\changesthr{Under the assumption that \clustername\ has a single stellar population,} we find that \clustername\ is indeed young, distant, and metal poor, with median posterior values and standard deviations of age $\tau = \clageerr$, distance $D = \cldisterr$, and metallicity $\feh = \clfeherr$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
+We find that the inferred extinction, $A_V = \claverr$, is consistent with the value $A_{V, {\rm SFD}} \approx 0.2$ from the (recalibrated) SFD dust map \citep{Schlegel:1998, Schlafly:2011}.
 We note again that, with the \decam\ photometry, we are limited to studying the subcomponent a of \clustername\ --- follow-up imaging of component b (see \figurename~\ref{fig:cmds}) would enable a similar analysis for the full cluster.
@@
 Another possible origin for \clustername\ is that it formed from gas stripped from a fully-destroyed dwarf galaxy (an unknown satellite of the Magellanic Clouds).
-However, the cluster appears to have a single, very young stellar population, and other, comoving, older stars have not been found associated with the LA in this region.
+\changesthr{However, we have not found a significant over-density of comoving older stars associated with the LA in this region.}
+% However, the cluster appears to have a single, very young stellar population, and other, comoving, older stars have not been found associated with the LA in this region.
+
+\changesthr{One final possibility is that these stars were formed in or associated with the Galactic disk.
+While there have been some claimed discoveries of young, embedded clusters at high Galactic latitude (within $\lesssim 5~\kpc$ of the sun, e.g., \citealt{Camargo:2015, Camargo:2016}, these may not be real \citep{Turner:2017}.
+Still, stars formed in the Galactic disk have been observed far from the disk midplane with heights up to $|z| \sim 10~\kpc$ \citep[e.g., the TriAnd over-density;][]{Price-Whelan:2015, Bergemann:2018}).
+However, TriAnd has an old stellar population, and no young disk stars have been since found associated with this or other features in the outer Galactic disk \citep{Deason:2018, Laporte:2019}.}
 
